### 2016-01-31 paper/ms.tex
added manuscript, obs: version after first ref report

%                                                                 aa.dem
% AA vers. 8.2, LaTeX class for Astronomy & Astrophysics
% demonstration file
%                                                       (c) EDP Sciences
%-----------------------------------------------------------------------
%
%\documentclass[referee]{aa} % for a referee version
%\documentclass[onecolumn]{aa} % for a paper on 1 column  
%\documentclass[longauth]{aa} % for the long lists of affiliations 
%\documentclass[rnote]{aa} % for the research notes
%\documentclass[letter]{aa} % for the letters 
%\documentclass[bibyear]{aa} % if the references are not structured 
% according to the author-year natbib style
%
\documentclass{aa}

%
\usepackage{graphicx}

\usepackage{hyperref}
\hypersetup{
    bookmarks=true,                                  % show bookmarks bar in pdf reader
    pdftitle={A Consistent 10 Myr Age for the Upper Scorpius OB Association},          % set pdf title          
    pdfauthor={Gregory A. Feiden},   % set pdf author
    colorlinks=true,                                 % false = box link, true = colored links
    linkcolor=blue,                                  % color of internal links
    citecolor=blue,                                  % color of citations
    urlcolor=blue                                    % external url color
}

\usepackage{defs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{txfonts}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\citestyle{aa}
\bibliographystyle{aa}

\titlerunning{A Consistent 10 Myr Age for Upper Scorpius}
\authorrunning{G.~A. Feiden}

\begin{document}

   \title{Magnetic Inhibition of Convection and the Fundamental Properties of Low--Mass Stars}
   \subtitle{III. A Consistent 10 Myr Age for the Upper Scorpius OB Association}

   \author{Gregory A.~Feiden}

   \institute{Department of Physics \& Astronomy, Uppsala University, Box 516,
                SE-751 20, Uppsala, Sweden. \\
                \email{gregory.feiden@physics.uu.se}
             }

   \date{Version: \today; Submitted: October 21, 2015; Re-submitted: February DD, 2016.}

  \abstract{
    When determining absolute ages of identifiably young stellar populations, results strongly depend on which stars are studied. Cooler (K, M) stars typically yield ages that are systematically younger than warmer (A, F, G) stars, typically by a factor of two. I explore the possibility that this age discordance is the product of magnetic inhibition of convection in cool young stars. I demonstrate that the adoption of magnetic stellar evolution models yield a median age of {\bf 9 -- 10} Myr for the Upper Scorpius subgroup of the Scorpius-Centaurus OB Association. This age is consistent for stars with spectral types A through M, except for a subset of F-type stars that appear older. Agreement is shown for ages derived from the Hertzsprung-Russell diagram and using an empirical mass-radius relationship from eclipsing multiple-star systems. Surface magnetic field strengths required to produce agreement are {\bf of order 2.5 kG} and are predicted from \emph{a priori} estimates of equipartition values, meaning no fine-tuning of model parameters is necessary. {\bf A gradual convergence of magnetic isochrones with standard model isochrones of an equivalent age is predicted to occur with the thinning of convective envelopes in stars with masses above 1.2~$M_{\odot}$. The predicted convergence at 10 Myr occurs when the mass contained in the convective envelope is approximately equal to 40\% of the total stellar mass. This transition appears to coincide with a noted flattening of the Hertzsprung-Russell diagram morphology of Upper Scorpius.} Furthermore, depletion of lithium predicted from magnetic models appears in better agreement with observed lithium equivalent widths than predictions from non-magnetic models. These results suggest that magnetic inhibition of convection plays an important role in the early evolution of low-mass stars and that it may be responsible for noted age discrepancies in young stellar populations.}

   \keywords{stars: evolution -- stars: low-mass -- stars: magnetic fields -- stars: pre-main-sequence -- open clusters and associations: individual: Upper Scorpius}

   \maketitle
%
%________________________________________________________________

\section{Introduction}
The \object{Upper Scorpius} subgroup of the larger Scorpius-Centaurus OB association is estimated to have a median age {\bf between 5 and 11 Myr.} Prior to 2012, there was a broad consensus that Upper Scorpius is roughly 5 Myr old based on age determinations from stellar evolution models \citep{deGeus1992, Preibisch2002, Slesnick2008}. Crucially, \citet{Preibisch2002} showed that this age was consistent across the entire theoretical Hertzsprung-Russell (HR) diagram. However, it was quickly suggested that early-type stars in Upper Scorpius supported an older 8 -- 10 Myr age \citep{Sartori2003}. This revision was confirmed by \citet{Pecaut2012} who performed a comprehensive re-analysis of the B-, A-, F-, and G-type members of Upper Scorpius and found HR diagram ages of each stellar spectral type are consistent with an overall age of approximately $11\pm3$ Myr for the subgroup. Despite the older median age inferred from high mass members of Upper Scorpius, ages for cooler K- and M-type members remain steadfastly younger at 5 -- 7 Myr \citep[][]{Herczeg2015, Rizzuto2015, Rizzuto2015b}, incompatible with a proposed age of 11 Myr.

This problem is not unique to Upper Scorpius and is characteristic of broader issues endemic to age dating young stellar populations with stellar evolution isochrones \citep[e.g.,][]{Naylor2009, Bell2012, Herczeg2015}. HR diagram analyses by \citet{Malo2014} and \citet{Herczeg2015} show that age estimates of mid- to late-M stars in nearby young stellar moving groups are typically younger by factor of two as compared to early-M and late-K stars. On the other hand, early- to late-K stars appear to have ages that are roughly consistent with each other. However, these ages are another factor of two younger than ages typically inferred from stars with spectral type G or earlier \citep{Hillenbrand2008}.

This picture is consistent with findings from studies of open cluster color-magnitude diagrams. Pre-main-sequence stars typically appear a factor of 2 -- 5 younger than main-sequence stars in the same population \citep{Naylor2009, Bell2012, Bell2013}. Age determinations appear to be a sensitive function of the stellar effective temperature range adopted in the analysis. The question is whether this is intrinsically real or an artifact of observational or modeling errors.

%This paper focuses on the latter following evidence that introduction of magnetic fields in stellar models can slow the contraction of young, low-mass stars \citep[e.g.,][]{MM10, Malo2014}.
%% Add paragraph of background with D'Antona+; Malo+; MM10/15;

While other young stellar populations exhibit an age gradient as a function of effective temperature, Upper Scorpius poses a particularly interesting hurdle. Previous studies of this problem are confined to the theoretical HR diagram and suffer from significant uncertainties in the accuracy of inferred stellar properties. However, observations of Upper Scorpius by \emph{Kepler}/K2 during Campaign 2 provide accurate photometric lightcurves of eclipsing multi-star systems \citep{Kraus2015, Alonso2015, David2015b, Lodieu2015}. This opens up new territory for assessing hypotheses as to the origin of the noted age discordance. Models can now be constrained in the HR diagram with added constraints from the eclipsing binary mass-radius relationship. The empirical mass-radius relationship is more reliable than the HR diagram, as masses and radii can be measured directly \citep[e.g.,][]{Andersen1991,Torres2010}. Compare this to conversions from spectral types and photometric colors to \teff s and luminosities, which are subject to significant uncertainties, especially for stars with gravities intermediate between dwarf and giant scales \citep[see, e.g.,][]{Pecaut2013}. Empirical mass-radius relationships should therefore provide stringent tests of stellar model accuracy.

\citet{Kraus2015} examined stellar model agreement using the properties of a low-mass eclipsing binary, UScoCTIO5, that has two roughly 0.3 \msun\ stars with precisely measured radii. What they found was that \object{UScoCTIO5} has an estimated age of about 5 Myr if inferred from the HR diagram, consistent with the age of other low-mass stars in Upper Scorpius \citep{Preibisch2002, Slesnick2008}. Surprisingly, the age inferred for UScoCTIO5 from the mass-radius relationship implies UScoCTIO5 is about 8 Myr old, more in line with \citet{Pecaut2012}. {\bf There is some disagreement about the precise values for the masses and radii of UScoCTIO5 \citep{David2015b}, but the mass-radius relationship nevertheless suggests an age of 7 -- 8 Myr}. Stellar ages are not only dependent on the effective temperature of stars used in the analysis, but on the specific properties adopted. It appears that stellar evolution models are unable to provide consistent ages on multiple levels.

Unfortunately, a single eclipsing binary system with two near-equal-mass components only gives a narrow view of model reliability. More than one system is needed to draw more definitive conclusions. A second system was supplied by the characterization of the triply eclipsing hierarchical triple \object{HD 144548} \citep{Alonso2015}. HD 144548 provides three additional points that are located in a separate region of the mass-radius and HR diagrams than UScoCTIO5 (two near $1.0$ \msun\ and one near $1.4$ \msun). Characterization of HD 144548 in combination with UScoCTIO5 allows for stricter tests of model consistency, assessing not just the ability of models to reproduce individual binary stars, but the more general slope of the mass-radius relationship concurrently with HR diagram fitting.

Here, I test the hypothesis that magnetic fields may inhibit convection in low-mass pre-main-sequence stars {\bf slowing their contraction along the Hayashi track. Slower contraction times for low-mass stars} would give them larger radii at a given age, pushing inferred ages to older values \citep[e.g.,][]{MM10, Malo2014}.  
In Sect.~\ref{sec:models}, I describe the model setup and method used to predict stellar surface magnetic field strengths \emph{a priori}. Section~\ref{sec:data} presents the data adopted for use in HR and mass-radius diagrams. Results about the performance of standard and magnetic stellar evolution models are given in Sect.~\ref{sec:results}, followed by  a discussion of potential uncertainties and weaknesses, as well as further evidence in support of the conclusions in Sect.~\ref{sec:disc}. Finally, the main conclusions of the paper are summarized in Section~\ref{sec:tellit}.

\section{Stellar Evolution Models}
\label{sec:models}
Models adopted in the analysis are magnetic Dartmouth stellar evolution models \citep{FC12b}. Basic physics used in these models are similar to those included in the original Dartmouth Stellar Evolution Program \citep[DSEP;][]{Dotter2008}. There are noted improvements that allow for a more accurate treatment of young star evolution \citep[see, e.g.,][]{Malo2014}. Key improvements are the explicit treatment of deuterium burning in the nuclear reaction network and the prescription of surface boundary conditions at a location in the stellar envelope where the optical depth $\tau_{5000} = 10$.

Specification of surface boundary conditions requires the determination of the gas pressure $\pgas$ and gas temperature $T_{\rm gas}$ at a given optical depth as a function of \logg, \teff, and [$m$/H]. This is accomplished by extracting relevant quantities from stellar model atmosphere structures that are computed with the same solar abundance distribution and (hopefully) opacity data as the interior structure models. Here, model atmosphere structures are those from a custom PHOENIX AMES-COND grid \citep{Hauschildt1999a, Hauschildt1999b, Dotter2008} that adopts the solar composition of \citet{GS98} and low-temperature opacities of \citet{Ferguson2005}.

Effects related to the interaction of magnetic fields and convection, as well as magnetic fields on the plasma equation of state, are included as described by \citet{FC12b,FC13}. {\bf Radial magnetic field strength profiles are prescribed using a ``Gaussian magnetic field strength profile'' of the form
\begin{equation}
	B(r) = B(R_{\rm src}) \exp\left[-\frac{1}{2}\left(\frac{R_{\rm src} - r}{\sigma_g}\right)^2\right]
\end{equation}
where $R_{\rm src}$ is the location of the inner convection zone boundary in fractional radii and $\sigma_g$ defines the width of the Gaussian \citep{FC13}. The adopted radial magnetic field strength profile has a negligible impact on the results provided the peak magnetic energy density remains small compared to the thermal energy density \citep{FC13,FC14,FC14b}.}
Peak interior magnetic field strengths are defined at $R_{\rm src} = 0.5\ R_{\star}$ for fully convective models and at the maximum of $R_{\rm src} = 0.5\ R_{\star}$ and $R_{\rm src} = R_{\rm bcz}$ (convection zone boundary) for partially convective stars. This latter condition allows magnetic models smoothly transition from a fully convective to partially convective configuration.

{\bf The width of the Gaussian controls the magnitude of the peak magnetic field strength at the inner convection zone boundary. It was defined by \citet{FC13} as
\begin{equation}
	\sigma_g = 0.2264 - 0.1776 \left(R_{\rm src}/R_{\star}\right).
\end{equation}
\citet{FC13} provided this expression for $\sigma_g$ to keep the Gaussian localized (sharply peaked) in stars with thin convective envelopes and to make a more distributed (broadly peaked) magnetic field in fully convective stars. For stars with very thin convective envelopes or in stars where the convection envelope gradually disappears, $\sigma_g$ becomes increasingly small and produces large peak magnetic field strengths at the convection zone boundary. As a result, large magnetic pressures and magnetic energy densities are present in tenuous layers, dominating over the gas pressure in the plasma equation of state and leading to numerical convergence errors. Models with initial masses above about 1.15~\msun\ are prevented from evolving through the final approach to the zero-age-main-sequence because of this problem. To mitigate the problem, a lower limit of $\sigma_g = 0.05$ is enforced.}

\begin{table}[t]
    \centering
    \caption{Equipartition magnetic field strength predictions at 10 Myr.}
    \begin{tabular*}{0.6\linewidth}{@{\extracolsep{\fill}}c c c}
        \hline\hline\noalign{\smallskip}
        Mass (\msun) & \teff (K) & $\langle Bf \rangle_{\rm eq,\,surf}$ (kG) \\
        \noalign{\smallskip}\hline\noalign{\smallskip}
        0.1  & 2920 & 2.58 \\
        0.2  & 3127 & 2.54 \\
        0.3  & 3260 & 2.56 \\
        0.4  & 3371 & 2.57 \\
        0.5  & 3463 & 2.56 \\
        0.6  & 3551 & 2.52 \\
        0.7  & 3640 & 2.47 \\
        0.8  & 3735 & 2.40 \\
        0.9  & 3836 & 2.29 \\
        1.0  & 3962 & 2.12 \\
        1.1  & 4099 & 1.94 \\
        1.2  & 4340 & 1.80 \\
        1.3  & 4617 & 1.69 \\
        1.4  & 4976 & 1.56 \\
        1.5  & 5565 & 1.29 \\
        1.6  & 6281 & 0.94 \\
        1.7  & 7004 & 0.77 \\
        \noalign{\smallskip}\hline
    \end{tabular*}
    \label{tab:equip_values}
\end{table}

% support with evidence from the literature? perhaps in discussion section?
The interior magnetic field strength profile requires a surface boundary condition: the average surface magnetic field strength $\langle{\rm B}f\rangle$. In previous studies, a range of values were explored and values that reproduce a given stellar fundamental property were eventually selected. 
Here, a different approach is used. Instead of adjusting models to find suitable magnetic field strengths, equipartition estimates of the maximum allowed average surface magnetic field strengths are adopted. The aim is to test the predictive abilities of magnetic stellar evolution models. Equipartition between the surface magnetic field pressure and the local gas pressure is assumed, meaning
\begin{equation}
    B_{\rm eq,\, surf} = \left(8\pi P_{\rm gas,\, surf}\right)^{1/2}.
\end{equation}
Surface gas pressures are defined using the same model atmosphere structures used to specify surface boundary conditions. The ``surface'' is defined as the optical photosphere where $\tau_{5000} = 1$. Values of the surface equipartition magnetic field strengths are listed in Table~\ref{tab:equip_values} for stars at an age of 10 Myr. Since surface gas pressures are dependent on \logg\ and \teff, equipartition magnetic field strengths evolve toward greater values for stars undergoing quasi-hydrostatic contraction. This assumption breaks down for stars with masses above 1.55 $M_{\odot}$, whose outer convection zones disappear within {\bf about} 10 Myr.

Magnetic field effects are switched on {\bf between the ages of 0.1 and 0.5 Myr years}, perturbing an initial zero-magnetic-field-strength model. The precise age at which the magnetic field is switched on has no impact on the results \citep{FC12b}, provided there is {\bf a} buffer between the perturbation age and ages under investigation (here, ages greater than 1 Myr). This buffer allows models to relax to a stable configuration after the perturbation. Typical peak magnetic field strengths in the models are of order 50 kG for models with $\langle Bf \rangle_{\rm eq,\,surf} \sim 2.5$~kG. 
{\bf Conversely, magnetic field effects are turned off during a model computation once the outer convective envelope disappears. This eventually occurs for stars with $M \gtrsim 1.15 M_{\odot}$.}

\begin{table}[t]
    \centering
    \caption{Adopted solar calibration properties.}
    \begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}l c c c}
        \hline\hline\noalign{\smallskip}
        Parameter & Adopted & Model & Ref \\
        \noalign{\smallskip}\hline\noalign{\smallskip}
        Age (Gyr)    & $4.567$ & $\cdots$ & 1 \\
        \msun\ (g)  & $1.9891\times 10^{33}$ & $\cdots$ & 2  \\
        \rsun\ (cm) & $6.9598\times 10^{10}$ & $\log(R/R_{\odot}) = -6\times 10^{-5}$ & 3, 1 \\
        \lsun\ (erg s$^{-1}$) & $3.8418\times 10^{33}$ & $\log(L/L_{\odot}) = -1\times 10^{-4}$ & 1 \\
        $R_{\rm bcz}/R_{\odot}$ & $0.713\pm0.001$ & $0.715$ & 4, 5 \\
        $(Z/X)_{\rm surf}$ & $0.0231$ & $0.0231$ & 6 \\
        $Y_{\odot,\, \rm surf}$ & $0.2485\pm0.0034$ & $0.2460$ & 7 \\
        \noalign{\smallskip}\hline
    \end{tabular*}
    \label{tab:solar}
    \tablebib{(1)~\citet{Bahcall2005};
    (2)~IAU 2009 \footnote{http://maia.usno.navy.mil/NSFA/NSFA\_cbe.html}
    (3)~\citet{Neckel1995}; (4)~\citet{Basu1997};~(5) \citet{Basu1998};
    (6)~\citet{GS98}; (7)~\citet{Basu2004}.}
\end{table}

Models for this study are computed using solar metallicity, [$m$/H] = 0. Values of the initial helium and heavy element mass fractions ($Y_0$ and $Z_0$, respectively) are taken from a solar-calibrated model. Similarly, a solar-calibrated mixing length parameter $\amlt$ is adopted for all models. In this way, modifications to convection are only introduced through the addition of magnetic perturbations. Solar-calibrated values are determined by finding a combination of $Y_0$, $Z_0$, and $\amlt$ that reproduce the solar radius, luminosity, and surface $\left(Z/X\right)$ at the solar age for a model of 1.0 \msun\ {\bf without a magnetic perturbation.} Adopted solar quantities are given in Table~\ref{tab:solar}. Final calibration parameters are $Y_0 = 0.2755$, $Z_0 = 0.01876$, and $\amlt = 1.884$.

\section{Properties of Upper Scorpius Members}
\label{sec:data}
Empirical data compared to stellar evolution models are taken from literature sources. Properties of stars with spectral type A, F, and G are drawn from \citet{Pecaut2012}. These data were kinematically selected to be highly probable members of Upper Scorpius \citep{deZeeuw1999}. In addition, data for K and M stars are drawn from the low-mass samples presented by \citet{Preibisch1999} and \citet{Preibisch2002}. Data span logarithmic effective temperatures from about 3.5 (3\,000~K) to 4.0 (10\,000~K). From these data, median empirical stellar loci were defined using a moving median approach.

A moving median of logarithmic luminosities as a function of $\log$(\teff) was performed by subdividing the temperature domain into 85 bins of equal width $\Delta\log$(\teff)$ = 0.025$~dex. {\bf This width ensured at least five stars were in each bin across the full temperature domain.} Bins with fewer than three stars were rejected. A median $\logLsun$\ value was estimated for each bin by finding the 50th percentile from the cumulative distribution of median values computed from a total of 10\,000 bootstrap samples. For each bootstrap sample, {\bf the $\log$(\teff) and $\logLsun$\ value for each data point} was randomly perturbed by drawing values from a normal distribution centered on the measured value with a standard deviation {\bf equal to} the quoted error. {\bf Thus}, points were allowed to scatter in and out of neighboring bins {\bf according} to their measured uncertainty. Points without uncertainties were assigned an {\bf optimistic uncertainty of 0.015~dex} in both $\logLsun$\ and $\log$(\teff). Different values for the number of bins, bin widths, and number of bootstrap samples were tested and found to not significantly impact the resulting median stellar locus. {\bf The resulting median locus and corresponding 99\% confidence interval for the median value are shown in Figure~\ref{fig:empirical}.}

\begin{figure}[t]
    \centering
    \includegraphics[width=0.85\linewidth]{USco_median_HRD.eps}
    \caption{Hertzsprung-Russell (HR) diagram for Upper Scorpius. A-type through M-type members of Upper Scorpius \citep{Preibisch1999,Preibisch2002,Pecaut2012} are shown as gray points. A median empirical locus for the population is shown as black solid line with the 99\% confidence interval for the median value shown as a light-gray shaded region. Errorbars shown for the majority of stars with \teff\ $< 5\,500$~K are prescribed as described in Sect.~\ref{sec:data}.}
    \label{fig:empirical}
\end{figure}

In addition to the photometric samples, properties of two eclipsing multiple-star systems recently observed by \emph{Kepler}/K2 are included. The first of these systems, UScoCTIO5, is a low-mass eclipsing binary (\porb$= 34$ days) with a $M_A = 0.329\pm0.002$\msun\ primary and a $M_B = 0.317\pm0.002$\msun\ secondary \citep{Kraus2015}. Radii were also measured and found to be $R_A = 0.834\pm0.006$\rsun\ and $R_B = 0.810\pm0.006$\rsun\ for the primary and secondary, respectively. Extracting reliable effective temperatures for components of eclipsing binary systems is notoriously difficult. However, the similarity between the two stars in UScoCTIO5 ($F_B/F_A \approx T_B/T_A \approx 1$) allows \citet{Kraus2015} to apply several different techniques for determining component effective temperatures, including directly determining the total system bolometric flux [\fbol$= (2.02\pm0.10)\times10^{-10}\textrm{ erg s}^{-1}$]. Assuming a distance of $145\pm15$~pc \citep{deZeeuw1999}, they estimate that $T_{{\rm eff}, A, B} = 3200\pm75$~K. {\bf Properties determined by \citet{David2015b} will be discussed in Sect.~\ref{sec:results}.}

The second system, HD 144548 (also, HIP 78977), was recently revealed to be a triply eclipsing hierarchical triple comprised of a solar-mass close binary system orbiting an F-type tertiary \citep{Alonso2015}. The inner binary has an orbital period \porb~$= 1.63$ days, compared to \porb~$= 33.9$ days for the orbit of the inner binary with the tertiary. Through a combination of photodynamical, radial velocity, and observed minus calculated ($O-C$) modeling, \citet{Alonso2015} were able to measure masses and radii for all three stars. They find $M_A = 1.44\pm0.04$\msun, $M_{Ba} = 0.984\pm0.007$\msun, and $M_{Bb} = 0.944\pm0.017$\msun\ for the tertiary and two close binary components, respectively. Radii for the stars were measured  to be $R_A = 2.41\pm0.03$\rsun, $R_{Ba} = 1.319\pm0.010$\rsun, and $R_{Bb} = 1.330\pm0.010$\rsun. While they were unable to estimate temperatures for individual stars, they were able to estimate luminosity ratios $L_{Bb}/L_{Ba} = 0.97\pm0.05$ and $L_{Ba + Bb}/L_{A} = 0.0593\pm0.0012$. In addition, they quote an apsidal motion rate $\dot{\omega} = 0.0235 \pm 0.002\textrm{ deg day}^{-1}$, which can potentially be used as an independent age estimator \citep{FD13}.

\citet{Pecaut2012} estimated the temperature and luminosity of HD 144548 as though it were a single star. For consistency, their values of $\log$(\teff) $ = 3.788\pm0.007$ and $\logLsun = 0.83\pm0.08$ are adopted as the temperature and luminosity of HD 144548 A. A 6\% correction was applied to the luminosity estimate to remove contribution from the close binary, as established by the luminosity ratio from photodynamical modeling \citep{Alonso2015}. Complications arising with this assignment of $\log$(\teff) and $\logLsun$ are discussed in Section~\ref{sec:radius}.

{\bf Fundamental properties for the eclipsing binary EPIC 203710387 \citep{David2015b, Lodieu2015} are not included in the main analysis because the component masses are uncertain at the 0.02 \msun\ level. Discussion with respect to model predictions in light the two fundamental property determinations will be presented in Sect.~\ref{sec:disc}.}

\begin{figure*}[t]
    \centering
    \includegraphics[width=0.48\linewidth]{HR_diagram_age_USco.eps} \quad
    \includegraphics[width=0.43\linewidth]{HR_diagram_split_USco.eps}
    \caption{{\bf (a) Hertzsprung-Russell (HR) diagram for Upper Scorpius. The median empirical locus calculated in Section~\ref{sec:data} is shown by the light-gray shaded region. Black points signify HR diagram positions of eclipsing binary members for which masses and radii are known. Over-plotted are predictions from Dartmouth stellar evolution isochrones. Standard (i.e., non-magnetic) isochrones at 5 Myr, 10 Myr, and 15 Myr are shown as short-dashed, dash-dotted, and long-dashed lines, respectively. A single magnetic isochrone at 10 Myr is plotted as a solid yellow line. All models are computed with a solar metallicity. (b) Zoom-in on the high-mass region of the HR diagram. (c) Zoom-in on the low-mass region.}}
    \label{fig:ages}
\end{figure*}

\section{Results}
\label{sec:results}
An HR diagram for Upper Scorpius is shown in Fig.~\ref{fig:ages}a. Empirical data is represented by the median stellar locus ({\bf light-gray shaded region}) and against three standard stellar evolution isochrones with ages of 5, 10, and 15 Myr ({\bf black dashed lines}). Focusing on {\bf temperature regimes corresponding} A-, F-, and G-type stars {\bf ($5\,750 <$ \teff/K $< 10\,000$)}, standard stellar isochrones predict ages between 5 and 15 Myr, with a median age estimate of approximately 10 Myr. %A median age of roughly 10 Myr is confirmed by comparison of the median stellar locus with stellar model isochrones.

Careful analysis of Fig.~\ref{fig:ages}b reveals that the empirical sequence closely matches models predictions at about 9 Myr where \teff~$> 8\,000$~K. Late A-type and early F-type stars with $7\,500 < $ \teff/K $ < 8\,000$ agree better with a 9 -- 10 Myr isochrone, as does the early-G-star sequence around \teff\ $\sim 5\,750$~K. In contrast, F-type stars with $6\,000 <$ \teff/K $< 7\,500$ appear marginally older and are best fit by an isochrone between 10 -- 15 Myr. These same features were noted by \citet{Pecaut2012} in their reanalysis of Upper Scorpius. Nevertheless, a 10 Myr isochrone lies almost entirely within the 99\% confidence interval for the median value across the entire range, suggesting an overall age of 10 Myr is reasonable. One can also see that HD 144548 A lies close to the 10 Myr isochrone suggesting that, at the very least, HD 144548 is approximately 10 Myr old.

However, the median age inferred from low-mass stars is about 4 -- 5 Myr. M-type stars with \teff\ $\lesssim 4\,000$~K suggest an age of 5 Myr is appropriate. The empirical stellar locus plotted in Figs.~\ref{fig:ages}a and \ref{fig:ages}c {\bf encompasses a 5 Myr standard stellar model isochrone in the M-star sequence down to \teff\ $\sim3\,100$ K. Disagreement at the lowest temperatures is likely due to a bias in the computation of the empirical stellar locus caused by a steepening of the HR diagram (see Figure~\ref{fig:empirical}).}

K-type stars with $4\,000 <$ \teff/K $< 5\,250$ suggest a younger age of around 4 Myr. Due to a lack of quoted uncertainties (see Sect.~\ref{sec:data}), it is difficult to rigorously assess the significance of the disagreement between the K- and M-star ages. The position of UScoCTIO5 in the HR diagram suggests an age that is slightly younger than 5 Myr, in line with the result of \citet{Kraus2015}. Both points for UScoCTIO5 lie just above the standard stellar model isochrone at 5 Myr, but within the empirical stellar locus \citep{Preibisch1999,Preibisch2002}. Its age is thus consistent with the 4 -- 5 Myr age inferred from K- and M-type stars.

A mass-radius diagram with the two eclipsing systems is shown in Fig.~\ref{fig:mrd}. Errorbars are plotted, but are generally smaller than the individual data points. It is apparent that ages inferred for the individual binary systems are not consistent with those from an HR diagram analysis. The age of HD 144548 from the Ba/Bb components is suggested to be around 5.5 Myr according to standard stellar evolution isochrones. While an age of 5.5 Myr agrees with quoted ages for the K- and M-type stars, it is in tension with the {\bf 10 Myr} age for component A from the HR diagram. Curiously, HD 144548 A lies significantly above the model mass-radius relation. Although concerning, further discussion of HD 144548 A's radius is deferred until Sect.~\ref{sec:radius}. The mass-radius diagram also suggests that UScoCTIO5 is 7.5 Myr old. This age is intermediate between the median age of the higher mass population and other low-mass stars, but it is important to note that this age is inconsistent with the HR diagram age of 5 Myr for UScoCTIO5.

\begin{figure}[t]
    \centering
    \includegraphics[width=0.85\linewidth]{USCO5_MR.eps}
    \caption{Mass-radius diagram for stars in eclipsing systems (black points). Model predictions for magnetic and non-magnetic isochrones are the same as in Fig.~\ref{fig:ages}.}
    \label{fig:mrd}
\end{figure}

Both eclipsing systems exhibit a disagreement between their HR and mass-radius diagram age. However, the disagreements do not immediately appear to be systematic. HD 144548 appears younger in the mass-radius plane than it does in the HR diagram by roughly a factor of two. In contrast, UScoCTIO5 appears older in the mass-radius plane than it does in the HR diagram---also by {\bf about} a factor of two. Slopes of the theoretical \teff-luminosity and mass-radius relationships must be altered in different directions to produce an overall agreement.

Introducing a magnetic perturbation as described in Sect.~\ref{sec:models}, a 10 Myr isochrone is computed and overlaid in the HR and mass-radius diagrams in Figs.~\ref{fig:ages} and \ref{fig:mrd} (thick yellow solid line). An age of 10 Myr was chosen as a starting point based on the approximate median age of the A-, F-, and G-type stars. Figures~\ref{fig:ages}a and \ref{fig:ages}c (HR diagrams) {\bf show that models}, at an age of 10 Myr with equipartition magnetic fields, are shifted toward cooler temperatures and slightly larger luminosities compared to a non-magnetic 10 Myr isochrone. Inhibition of convection by magnetic fields {\bf cools the stellar surface temperature thereby slowing} the contraction rate of young stars, which leads to stars having a larger radius and a larger luminosity at a given age. The combination of cooler surface temperatures and higher luminosities leads to a situation where a 10 Myr magnetic isochrone looks nearly identical to a non-magnetic isochrone at 5 Myr. In fact, the magnetic stellar model isochrone {\bf lies on top of} the 5 Myr standard model isochrone and {\bf within} the empirical stellar locus. Thus, a 10 Myr magnetic isochrone naturally explains the factor of two age difference observed between high- and low-mass stars, provided the high mass stars are not appreciably affected by non-standard physics (e.g., magnetic fields or rotation).

Furthermore, the mass-radius diagram in Figure~\ref{fig:mrd} shows a 10 Myr magnetic isochrone provides reasonable agreement with the two low-mass eclipsing binary systems. It is apparent that magnetic inhibition of convection leads to more significant radius ``inflation'' at higher masses as compared to lower masses. This effect leads to a change in slope of the model predicted mass-radius relationship that is consistent with observations. Although agreement is good, it is not perfect. {\bf Depending on whether mass and radius estimates are adopted from \citet{Kraus2015} or \citet{David2015b}, at 10 Myr the radii of the primary and secondary of UScoCTIO5 are either 3.2\% and 2.1\% \citeauthor{Kraus2015} larger than model predictions or 5.7\% and 6.6\% larger \citeauthor{David2015b}.} Similarly, models at 10 Myr predict radii that are 1.4\% too large and 1.5\% too small for the Ba and Bb components of HD 144548 at 10 Myr, respectively. An age between 9.0 and 9.5 Myr is preferred for UScoCTIO5, while 10 Myr is the best fit age for HD 144548 Ba/Bb.

This age spread could be indicative of an intrinsic age spread, but it is also possible {\bf to attribute this spread to errors in the mass and radius determinations of the eclipsing binary systems or to the fact} that the low-mass stars in UScoCTIO5 may require marginally stronger magnetic field strengths than are predicted from equipartition arguments. Nevertheless, it is encouraging that models provide this level of agreement with an age and surface magnetic field strengths determined \emph{a priori}.

\section{Discussion}
\label{sec:disc}
An age of {\bf 9 -- 10} Myr gives broad agreement across the HR and mass-radius diagrams. No stellar population in Upper Scorpius {\bf studied here robustly} supports the possibility that the median age of the association is 5 Myr old.\footnote{Ages for B-type members of Upper Scorpius suggest a range of ages from 2 -- 15 Myr depending on whether models account for rotation \citep{Pecaut2012}, providing some support for a younger age.} As noted above, F-type stars appear a few million years older than stars of other spectral types. This is concerning and should be explored further, especially considering that potential missing physics in the models would likely conspire to make F-stars older, not younger. Curiously, most F stars in Upper Scorpius are at a stage of evolution where radii increase and subsequently decrease over a period of roughly 4 Myr, eerily similar to the observed age discrepancy (see Fig.\ \ref{fig:bump} and text below for more details).

%While ages for the F stars remain in doubt, an overall age of 10 Myr provides good agreement with median age for B-type stars near the main-sequence turn-off \citep{Pecaut2012}.

\subsection{Magnetic Sequence Turn-off}
\label{sec:dynamo}
% F --> G type members are bright (V < 10 mag) and could be accessible to ZDI. Perhaps we'd see changes in magnetic strengths or topologies stretching from late-G to late-F.

Given that magnetic inhibition of convection is required to explain the anomalously young age of low-mass K- and M-type stars, it is worth considering at what mass or effective temperature the effects related to magnetism can be identified.
%begins to play a significant role in governing stellar structure. 
Looking at Fig.\ \ref{fig:ages}a, early- to mid-G stars follow a 10 Myr standard stellar model isochrone. Instead of continuing the trend, late-G stars appear to deviate toward a 5 Myr isochrone around \teff\ $\sim 5\,750$ K. %, evidenced by a flattening of the empirical locus. 
This may be an artifact of how the empirical locus was computed. However, it may indicate {\bf a transition} where the influence of magnetic inhibition of convection becomes identifiable.

{\bf Predictions from stellar evolution models suggest a transition should exist. Convective envelopes in stars with masses greater than $\sim1.2$ $M_{\odot}$ gradually recede from the deep interior toward the stellar surface in response to the ignition of the proton-proton ($p$-$p$) chain and continued release of gravitational potential energy as the star contracts. Eventually, the convective envelope in these stars will disappear entirely following ignition of the CN-cycle. As the convective envelope grows thinner, magnetic fields of a given strength will have a larger impact on the thermal structure of the super-adiabatic region. However, a restructuring of the super-adiabatic layers in a star with a thin convective envelope has less of an impact on the thermal structure of the deeper layers, which are assumed to be in radiative equilibrium, than for a star whose interior is largely convective. The thinning of the convective envelope is also accompanied by a drop in surface gas pressure as the star's radius inflates, lowering the permitted equipartition magnetic field strength. The combination of these two effects suggests that the transition from a magnetic sequence to a non-magnetic sequence should coincide with the disappearance of the convective envelope.} % confirm discussion of super-adiabatic layers

{\bf This observed transition is reproduced by the magnetic isochrone at 10 Myr, to some degree. For \teff\ $< 5\,000$~K, the magnetic isochrone closely matches predictions from a 5 Myr standard model isochrone, indicating magnetic inhibition of convection may be playing a role for stars at these temperatures. Compare this to the small segment of the magnetic isochrone above \teff\ $\sim 6\,000$~K, where it is beginning to converge with the 10 Myr standard model isochrone. Although the transition appears to occur over approximately the correct effective temperature domain, Fig.~\ref{fig:ages}a shows a sharp transition from a magnetic to a non-magnetic sequence between $5\,000 <$ \teff/K $< 6\,000$ whereas models predict a more gradual transition. In magnetic model space, this temperature domain corresponds to masses between $1.40$ and $1.56$ \msun. Inspection of Fig.~\ref{fig:mrd} reveals this mass range corresponds precisely to where the rapid thinning of the convection zone occurs, as expected.}

{\bf While this behavior is expected in the magnetic models, it does not need to necessarily correspond to the observed transition. General agreement between the behavior of the magnetic model isochrone and the observed stellar locus provides evidence that magnetic inhibition of convection is the mechanism responsible for the age discrepancy between the high- and low-mass stellar populations. However, it is clear that this statement only holds with respect to the plausible identification of a general mechanism with the models failing to reproduce the precise morphology at the magnetic sequence turn-off.}

If the age difference between warmer and cooler stars in Upper Scorpius is the result of magnetic inhibition of convection, the transition region between $5\,000 <$ \teff/K $< 6\,000$ provides an excellent laboratory for studying magnetic dynamo evolution as a function of convection zone depth and convective core size.

%If this is the case, it may help explain the significant gap between the end of the magnetic stellar evolution isochrone and the location of HD 144548 A in the HR diagram. The mass difference is only $0.16\pm0.04$ \msun, but the temperature difference is nearly 1600~K. By contrast, the expected difference is 500~K from standard models. It's interesting to note that the end of the magnetic 10 Myr isochrone is where stars are expected to begin a brief period of radius inflation prior to ignition of the CN cycle (see below). This is shown in Fig.~\ref{fig:bump}. Radius inflation occurs over a 3 -- 4 Myr timespan and may result in a gradual decrease of the magnetic field strength throughout the stellar envelope due to a roughly 30\% decrease in the envelope's angular velocity. The latter is due to an increase in the envelope's moment of inertia and may weaken magnetic dynamo processes. One might then expect a gradual reduction in the importance of magnetic inhibition of convection, creating a situation where stars in a narrow mass range span a relatively large range in effective temperature, resulting in the gap seen in Fig.~\ref{fig:ages}a.

Presence of magnetic and non-magnetic sequences has implications for the (sub)stellar initial mass function of Upper Scorpius \citep{Ardila2000, Preibisch2002}. Not only will magnetic inhibition of convection shift mass estimates for cool stars toward higher masses, but a gradually declining magnetic field in the regime of 1.4 \msun\ should result in a paucity of stars in the 4500~K -- 5500~K temperature range. Standard stellar initial mass functions \citep[e.g.,][]{Salpeter1955, Kroupa2002} predict a certain number of stars at a given mass relative to other masses. Having a range of magnetic field strengths in stars over such a narrow mass range (0.16 \msun) will spread stars of similar mass across a wider range in temperature. It's not clear from \citet{Preibisch2002} whether this paucity is observed. However, they do note a possible excess of low-mass stars compared to field initial mass functions \citep{Scalo1998, Kroupa2002} that appears consistent with predictions from magnetic models. The impact of magnetic inhibition of convection on the (sub)stellar initial mass function of Upper Scorpius is reserved for future work.

\begin{figure}
    \centering
    \includegraphics[width=0.85\linewidth]{radius_bump.eps}
    \caption{Brief period of radius inflation described in Sect.~\ref{sec:radius} for stars with masses of 1.60\msun\ (blue solid), 1.55\msun\ (green short-dashed), 1.50\msun\ (blue dash-dotted), 1.45\msun\ (yellow long-dashed). Mass tracks are computed without a magnetic field (i.e., non-magnetic configuration). Effective temperatures at these masses are characteristic of F stars at 10 Myr.}
    \label{fig:bump}
\end{figure}

\subsection{Radius of HD 144548 A}
\label{sec:radius}
Figure~\ref{fig:mrd} reveals that the radius of HD 144548 A is significantly larger than is expected from standard stellar evolutionary predictions. This poses a problem to claims of consistent ages across stellar populations in Upper Scorpius. However, it is not immediately clear that the observed radius error is a true astrophysical problem. For instance, adopting the effective temperature and luminosity estimate from \citet{Pecaut2012}, one derives a radius of $R = 2.2 \pm 0.2 R_{\odot}$. This is formally consistent with the radius derived by \citep{Alonso2015}, but the mean value is more consistent with estimates from stellar evolution isochrones around 10 Myr. Stellar models show an increase in stellar radius for stars with masses in the vicinity of $M = 1.5$\msun, illustrated {\bf as a function of stellar mass and age} in Fig.\ \ref{fig:bump}. As described in {\bf Sect.\ \ref{sec:dynamo}}, this radius increase is due to the convective envelope responding to increased energy generation from the $p$--$p$ chain and gravitational contraction of the core.

Assessing in detail whether the larger radius of HD 144548 A is real is beyond the scope of this work. However, if it requires revision, the result is unlikely to affect the inferred masses and radii derived for the close binary. Those largely depend on photodynamical modeling of the \emph{Kepler}/K2 lightcurve during events where Ba and Bb eclipse one another, not where the pair eclipse the tertiary component. Results in Sect.~\ref{sec:results} should be robust. Still, confirmation of the star's radius would be beneficial for future investigations to ensure there are no adverse effects on the radii of the B components.

{\bf HD 144548 appears to be in a fairly rapid phase of evolution given either the radius estimate from \cite{Pecaut2012} or \citet{Alonso2015}. This phase of evolution is sensitive to radiative opacities and nuclear reaction cross sections. Radiative opacities and the initial $p$-$p$ reaction cross section determine when radius inflation begins while CN-cycle reactions largely control when radius inflation ends.} It may be possible to use HD 144548 A to constrain these physics, notably nuclear reaction cross-sections for CN-cycle reactions, if the properties of HD 144548 A can be accurately constrained. CN-cycle reactions eventually generate enough energy to oppose core contraction and reverse the radius increase {\bf shown in Figs.\ \ref{fig:mrd} and \ref{fig:bump} \citep[also see][]{Stassun2014}}. Therefore, the maximum radius reached by a star during this phase of evolution is sensitive to the adopted CN-cycle cross sections.

Perhaps there are other physics missing for HD 144548 A that result in the radius discrepancy. Magnetic inhibition of convection {\bf does not appear to play a significant role in governing the radius at this phase of evolution. Convective envelopes contain very little mass ($M_{cz} < 10^{-3} M_{\odot}$) and models indicate that, during the brief period radius inflation, magnetic and non-magnetic mass tracks tend to converge (see Fig.~\ref{fig:mrd}).} However, the exact role that magnetic fields may {\bf play} in governing the pre-main-sequence contraction of young A-, F-, and G-type stars remains relatively unexplored. Attempts were made to include effects from magnetic fields on these stars, but numerical issues prevented models from evolving through CN-cycle ignition. A kink in the magnetic stellar model isochrone can be seen in Fig.\ \ref{fig:mrd} around 1.53 \msun\ highlighting where magnetic perturbations were switched off. This occurs before CN-cycle ignition is reached.

The numerical issue is related to the thinning of the convection zone and the method used to specify surface boundary conditions. 
Extrapolating from the impact of magnetic fields on lower-mass stars during the development of radiative cores, it is expected that there will be little change in the derived ages for higher mass stars, but confirmation is needed.

Effects of strong magnetic fields on convection in stellar cores are also neglected. Strong magnetic fields may be generated by the interaction of a fossil field and vigorous dynamo action \citep[e.g.,][]{Featherstone2009}. Core magnetic fields in present models are below 1 G, which is insufficient to influence core convection. The impact of significantly stronger magnetic fields on core convection and the subsequent effect on the properties of higher mass stars is reserved for a future investigation.

\subsection{On Starspots}
Starspots have been suggested as an alternative mechanism to slow the contraction of young low-mass stars \citep{Jackson2009, MM10, Jackson2014a, Somers2015b}. The primary difference between starspots and a more general magnetic inhibition of convection is that spots are assumed to be strong localizations covering some fraction of the stellar surface whereas magnetic inhibition of convection is assumed (for simplicity) to be globally pervasive. Starspots have qualitatively and quantitatively similar effects on stellar fundamental properties \citep[radius, \teff, luminosity;][]{Spruit1982a,Spruit1986,Somers2015b}, but differ in their impact on photometric properties. Colors of spotted stars are the result of a superposition of surface regions of different effective temperatures \citep{Spruit1986}, whereas a global inhibition of convection still assumes a single temperature optical photosphere \citep{Jackson2014a}.

Assuming starspots are analogous to sunspots, {\bf spots} can be understood to be local manifestations of convective inhibition near the optical photosphere \citep{Biermann1941,Deinzer1965}. The agreement between ages and stellar fundamental properties predicted by magnetic stellar evolution isochrones presented in this work with ages of higher mass stars in Upper Scorpius may indicate that a global inhibition of convection accurately captures relevant physics involved in halting contraction of low-mass stars. If starspots are also to be considered, one should find that young stars in Upper Scorpius have a high coverage fraction of spots ($f \sim 1$). In this limit, a global inhibition of convection and spotted models \citep[e.g.,][]{Somers2015b} should provide equivalent explanations for observed HR and mass-radius diagram discrepancies.

Photometric brightness modulation is observed in lightcurves of UScoCTIO5 and HD 144548, suggesting spots are present on their optical photospheres. However, it may be that a large fraction of the surface is covered by a non-zero magnetic field of near-equipartition value, accompanied by smaller regions of strong local magnetic flux concentration, such as observed on the young star \object{AD Leo} \citep{Shulyak2014}. The latter can lead to the appearance of cooler spots, although only covering a small fraction of the stellar surface. If spots have a small areal coverage, it is more likely that they will have a negligible impact on stellar structure as compared to global inhibition of convection from the more ubiquitous non-zero background magnetic field.

\begin{figure}[t]
    \includegraphics[width=0.85\linewidth]{Li7_USco_Beq.eps}
    \caption{Lithium abundance  as a function of effective temperature at 10 Myr. Predictions are shown from standard (light-blue dashed line) and magnetic (yellow solid line) stellar evolution isochrones. Models were computed using the setup described in Sect.~\ref{sec:models}. Lithium abundance is defined as $A(\,^7{\rm Li}) = \log_{10}(N_{\rm Li}/N_{\rm H}) + 12$.}
    \label{fig:lithium}
\end{figure}

\subsection{Lithium Depletion}
An approach to validating magnetic stellar models is the determination of lithium abundances {\bf \citep{MacDonald2015},} or observation of lithium equivalent widths. {\bf Magnetic inhibition of convection produces a cooler temperature structure in fully convective pre-main-sequence stars, thereby delaying lithium burning and preserving lithium to older ages \citep{Ventura1998, DAntona2000, MM10, FC13, Malo2014, MacDonald2015}. Starspots have a similar affect on lithium burning timescales \citep{Jackson2014b, Somers2015b}, which is perhaps not surprising given the deep connection between starspots and magnetic inhibition of convection \citep{Biermann1941, Deinzer1965}. Nevertheless, if magnetic fields are directly influencing the structure of young stars, they should leave an imprint on the observed lithium abundance distribution in young stellar populations.}

Figure \ref{fig:lithium} demonstrates the impact that magnetic inhibition of convection has on predicted lithium abundances for stars in Upper Scorpius at 10 Myr. The lithium depletion boundary at cooler temperatures remains largely unchanged. However, lithium depletion is not expected to occur in warmer stars with effective temperatures exceeding about 4500~K, assuming they possess a strong magnetic field. Therefore, K-stars are not expected to exhibit signatures of lithium depletion, in contrast to standard model predictions, which suggest stars with spectral types later than G are expected to show signatures of lithium depletion.

Stars with effective temperatures around 3550~K are predicted to exhibit the greatest amount of lithium depletion, as compared to a prediction of 3750~K for standard models. Some depletion is also expected to occur for stars with $3300 <$ \teff/K $< 3500$, which standard models suggest should not be observed. This prediction shows a strong similarity to trends in lithium equivalent widths for M-stars in Upper Scorpius \citep{Rizzuto2015}. The observed lithium equivalent width minimum is located between \teff\ = 3300 -- 3400~K \citep{Rizzuto2015}. While comparing lithium equivalent widths and predictions of lithium abundances is not completely correct, within the narrow range of temperatures surrounding the lithium abundance minimum, equivalent widths should accurately reflect trends in overall lithium abundances. Accounting for uncertainties in the SpT-\teff\ conversion, observed lithium equivalent widths support the validity of magnetic models and an inferred age of 10 Myr for the low-mass stars in Upper Scorpius.

\section{Summary \& Conclusions}
\label{sec:tellit}
Stellar evolution models and literature data are used to derive ages for stars with spectral types A through M in Upper Scorpius. I find a revised median HR diagram age of {\bf 9 -- 10} Myr for A-, F-, and G-type stars, with the exception of a population of F-type stars that appear 5 Myr older. These results agree with the revised $11\pm3$ Myr of \citet{Pecaut2012}. At the same time, I confirm the HR diagram age of 4 -- 5 Myr for K- and M-type stars using standard stellar evolution isochrones \citep{Preibisch2012, Slesnick2008, Herczeg2015}. However, isochrone ages of K- and M-type stars in eclipsing multiple-star systems observed by \emph{Kepler}/K2 \citep{Kraus2015, Alonso2015} disagree with the HR diagram analysis and suggest ages between 6 and 8 Myr for the same stars.

Application of stellar evolution models accounting for magnetic inhibition of convection \citep{FC12b, FC13} yields an age of {\bf 9 -- 10} Myr for K- and M-type stars in Upper Scorpius. Magnetic models provide a consistent explanation for the age discrepancy between high- and low-mass stars, as well as differences observed between HR diagram and mass-radius relationship ages. Magnetic models also reproduce the slope of the low-mass star mass-radius relationship. Critically, average surface magnetic field strengths are determined \emph{a priori} via equipartition arguments, highlighting the potential predictive power of magnetic stellar models of young stars. Furthermore, magnetic models around 10 Myr exhibit a lithium depletion pattern that is in agreement with inferences from observed lithium equivalent widths \citep{Rizzuto2015}.

Results from this work and \citet{Pecaut2012} strongly support adoption of an approximately 10 Myr median age for the Upper Scorpius subgroup of the Scorpius-Centaurus OB association. There is no population of stars in the Upper Scorpius that unambiguously support an age of 5 Myr. Still, additional eclipsing binary systems are needed to further populate the mass-radius relationship and solidify Upper Scorpius as a 10 Myr old stellar association.

Further work is needed to explore the impact of magnetic inhibition of convection on the (sub)stellar initial mass function for Upper Scorpius and other young stellar populations \citep[e.g.,][]{Ardila2000, Preibisch2002}. More work is also needed to explore whether magnetic inhibition of convection serves as a robust solution for noted age gradients as a function of \teff\ \citep{Naylor2009, Herczeg2015}. However, given the ease with which magnetic models appear to reconcile discrepancies in Upper Scorpius, the wider application of magnetic stellar models as a component of isochrone analyses is recommended. A small grid of magnetic stellar isochrones is under construction as is a web interface to request custom magnetic models.

\begin{acknowledgements}
The magnetic Dartmouth stellar evolution code was originally developed with support of National Science Foundation (NSF) grant AST-0908345. This work made use of NASA's Astrophysics Data System (ADS) and the VizieR catalogue access tool by CDS in Strasbourg, France. Figures in this manuscript were produced with Gnuplot 5 \citep{Gnuplot5.0}.
\end{acknowledgements}

\bibliography{papers}

\end{document}

### 2016-01-31 models/quick_iso.py
standard model isochrones + revised magnetic isochrones

@@ -5,10 +5,10 @@ import fileinput as fi
 from scipy.interpolate import Akima1DInterpolator as AkimaSpline
 from scipy.interpolate import interp1d
 
-files = [x.rstrip() for x in fi.input('files.txt')]
+files = [x.rstrip() for x in fi.input(sys.argv[1])]
 fi.close()
 
-ages = np.arange(5.0, 15.0, 0.5)*1.0e6
+ages = np.arange(5.0, 15.1, 0.5)*1.0e6
 masses = []
 
 for age in ages:
@@ -43,5 +43,5 @@ for age in ages:
     header  = 'Dartmouth Stellar Evolution Model: Quick Isochrone \n\n'
     header += 'Age = {:7.1f} Myr   [Fe/H] = {:+5.2f}   [a/Fe] = {:+5.2f} \n\n'.format(age/1.e6, 0.0, 0.0)
     header += '{:^14} {:^14} {:^14} {:^14} {:^14} {:^14}'.format('Mass', 'log(Teff)', 'log(g)', 'log(L/Lo)', 'log(R/Ro)', 'A(Li)')
-    np.savetxt('./dmestar_{:07.1f}myr_z+0.00_a+0.00_marcs_magBeq.iso'.format(age/1.e6), all_props, fmt='%14.7f', header=header)
+    np.savetxt('./dmestar_{:07.1f}myr_z+0.00_a+0.00_phx.iso'.format(age/1.e6), all_props, fmt='%14.7f', header=header)
     del all_props

### 2016-01-31 models/trk/dtrk.py
reprocessed detailed tracks

@@ -1,0 +1,50 @@
+#
+import sys
+import fileinput as fi
+import numpy as np
+
+files = [f.rstrip('\n') for f in fi.input(sys.argv[1])]
+
+for f in files:
+    data = [line for line in fi.input(f)]
+    
+    head = data[:14] 
+    data = data[14:]
+
+    file_out = open(f[:-4] + 'ntrk', 'w')
+    print f[:-4] + 'ntrk'
+    for line in head:
+        file_out.write('# ' + line)
+
+    for i in range(0, len(data) - 6, 6):
+        time_step = ''
+        for j in range(6):
+            time_step += data[i + j].rstrip('\n')
+        dtrk = ''.join(time_step)
+        dtrk.replace('\\n', '')
+        
+        file_out.write(dtrk + '\n')
+    file_out.close()
+
+#    cols = [x for x in range(30)]
+#
+#    new_data = np.genfromtxt(f[:-4] + 'ntrk', skiprows=14, usecols=tuple(cols))
+#    new_iso  = np.empty((len(new_data), 12))
+#    for i, time_step in enumerate(new_data):
+#        new_iso[i, 0] = time_step[2]*1.0e9
+#        new_iso[i, 1] = time_step[6]
+#        new_iso[i, 2] = time_step[5]
+#        new_iso[i, 3] = time_step[3]
+#        new_iso[i, 4] = time_step[4]
+#        new_iso[i, 5] = 1.0 - time_step[28] - time_step[29]
+#        new_iso[i, 6] = time_step[29]
+#        new_iso[i, 7] = time_step[12]/time_step[11]
+#        new_iso[i, 8] = sum(time_step[13:17])/(3.846e33)
+#        new_iso[i, 9] = time_step[17]/(3.846e33)
+#        new_iso[i,10] = time_step[10]
+#        new_iso[i,11] = 0.0
+#
+#    header_file = [line[2:] for line in fi.input(f[:-4] + 'trk') if line[0] == '#']
+#    head = header_file[2] + header_file[3].rstrip('\n')
+#    
+#    np.savetxt(f[:-4] + 'niso', new_iso, fmt='%14.7e', header=head)

### 2016-02-09 src/mvavg.py
plotting scripts, plots, and data

@@ -1,0 +1,56 @@
+#
+#
+import numpy as np
+
+w = 1.0
+N = 20.0
+M = 4.0
+N_Samples = 10000
+
+#data = np.genfromtxt('usco_AFG.txt')
+data = np.genfromtxt('tmp.txt')
+
+end0 = min(data[:,2])
+end1 = max(data[:,2])
+
+# grid up
+distance = end1 - end0
+division = distance/N
+
+centers = np.arange(end0, end1 + division, division/M)
+
+print "Total Points: ", len(data)
+
+fout = open('usco_emp_hrd.txt', 'w')
+
+print len(centers), division, w*division
+np.random.seed()
+for center in centers:
+    logL_pdf = np.empty((N_Samples))
+    for i in range(N_Samples):
+        # collapse data array
+        in_bin = [(center - w*division) <= np.random.normal(x[2], x[3]) < (center + w*division) for x in data]
+        data_in_bin = np.compress(in_bin, data, axis=0)
+        
+        if len(data_in_bin) < 3:
+            continue
+        
+        # bootstrap resample
+        selection = np.random.randint(0, len(data_in_bin), size=len(data_in_bin))
+        new_sample = np.array([data_in_bin[x] for x in selection])
+        
+        # bootstrap with uncertainties
+        logL = np.array([np.random.normal(x[4], x[5]) for x in new_sample])
+        logL_pdf[i] = np.median(logL)
+    
+    if len(data_in_bin) < 3:
+        continue
+    else:
+        print center, "N_bin =", len(data_in_bin)
+    logL = np.percentile(logL_pdf, 50.0)
+    logL_minus = np.percentile(logL_pdf, 0.5)
+    logL_plus  = np.percentile(logL_pdf, 99.5)    
+
+    fout.write("{:12.6f} {:12.6f} {:12.6f} {:12.6f}\n".format(center, logL, logL_minus, logL_plus))
+
+fout.close()

### 2016-02-09 paper/ms.tex
Updated HR Diagram Figure with Rad Core Masses

@@
     \includegraphics[width=0.43\linewidth]{HR_diagram_split_USco.eps}
-    \caption{{\bf (a) Hertzsprung-Russell (HR) diagram for Upper Scorpius.
-The median empirical locus calculated in Section~\ref{sec:data} is shown by the light-gray shaded region.
+    \caption{{\bf (a) Comparison of theoretical Hertzsprung-Russell (HR) diagram predictions to the observational locus of Upper Scorpius.
+The median empirical locus calculated in Section~\ref{sec:data} is shown by the light gray shaded region.
 Black points signify HR diagram positions of eclipsing binary members for which masses and radii are known.
@@
 A single magnetic isochrone at 10 Myr is plotted as a solid yellow line.
+Values in parentheses along the magnetic isochrone are predicted radiative core mass fractions ($M_{\rm rad.\ core}/M_{\star}$) at the circled points.
 All models are computed with a solar metallicity.
@@
     \includegraphics[width=0.85\linewidth]{USCO5_MR.eps}
-    \caption{Mass-radius diagram for stars in eclipsing systems (black points). Model predictions for magnetic and non-magnetic isochrones are the same as in Fig.~\ref{fig:ages}.}
+    \caption{Mass-radius diagram for stars in eclipsing systems.
+{\bf Black points are from \citet{Kraus2015} and \citet{Alonso2015}, while gray points are taken from \citet{Lodieu2015} and \citet{David2015b}.} Model predictions for magnetic and non-magnetic isochrones are the same as in Fig.~\ref{fig:ages}.}
     \label{fig:mrd}
@@
 An age of {\bf 9 -- 10} Myr gives broad agreement across the HR and mass-radius diagrams.
-No stellar population in Upper Scorpius {\bf studied here robustly} supports the possibility that the median age of the association is 5 Myr old.\footnote{Ages for B-type members of Upper Scorpius suggest a range of ages from 2 -- 15 Myr depending on whether models account for rotation \citep{Pecaut2012}, providing some support for a younger age.} As noted above, F-type stars appear a few million years older than stars of other spectral types.
-This is concerning and should be explored further, especially considering that potential missing physics in the models would likely conspire to make F-stars older, not younger.
-Curiously, most F stars in Upper Scorpius are at a stage of evolution where radii increase and subsequently decrease over a period of roughly 4 Myr, eerily similar to the observed age discrepancy (see Fig.\ \ref{fig:bump} and text below for more details).
+No stellar population in Upper Scorpius {\bf studied here robustly} supports the possibility that the median age of the association is 5 Myr old.
+As noted above, the median age for F-type stars appears to be a few million years older than stars of other spectral types.
+This {\bf discrepancy} is {\bf perplexing} and should be explored further, especially considering that potential missing physics in the models would likely conspire to make F-stars older, not younger.
+Curiously, most F stars in Upper Scorpius are at a stage of evolution where radii increase and subsequently decrease over a period of roughly 4 Myr {\bf (e.g., HD 144548 A).
+The timescale for this process is} similar to the observed age discrepancy (see Fig.\ \ref{fig:bump} and text below for more details) and may be indicative of potential shortcomings in model physics.
 
-%While ages for the F stars remain in doubt, an overall age of 10 Myr provides good agreement with median age for B-type stars near the main-sequence turn-off \citep{Pecaut2012}.
+{\bf Age discrepancies also exist with two B-type members of Upper Scorpius: \object{$\tau$ Sco} and \object{$\omega$ Sco}.
+They exhibit ages between 2 and 5 Myr depending on whether rotation is accounted for in stellar evolution models \citep{Pecaut2012}.
+Those authors show that there are four other B-type stars that have inferred ages consistent with the 10 Myr median age proposed here, if rotation is taken into account.
+Notably the four stars that appear older are known binary systems while the two seemingly younger stars do not have a detected companion \citep{Pecaut2012}.
+The presence of two seemingly young B-type stars may be leveraged to suggest there exists a young population of stars with ages around 5 Myr thus supporting the younger age for the low-mass stellar population and thereby doing away with the need for a magnetic field explanation.
+However, that scenario requires that the low-mass stars form almost exclusively in a later star formation episode than the higher mass population.
+Although we cannot definitively rule out this scenario, we find it unlikely and maintain that the {\bf median} age for the low-mass stars is too young compared to the rest of the stellar population in the absence of magnetic inhibition of convection.}
 
@@
 \begin{acknowledgements}
+Thank you to Alexis Lavail, Eric Mamajek, James Silvester, and Eric Stempels for reading and commenting on an early version of this manuscript.
 The magnetic Dartmouth stellar evolution code was originally developed with support of National Science Foundation (NSF) grant AST-0908345.

### 2016-02-09 models/quick_iso.py

@@ -15,16 +15,24 @@ for age in ages:
     print "Processing Age: {:07.1f} Myr".format(age/1.0e6)
     for f in files:
         try:
-            trk = np.genfromtxt(f, skiprows=100, usecols=(0, 1, 2, 3, 4, 8))
+            # import age, log(Teff), log(g), log(L/Lo), log(R/Ro), N(Li), Mconv,env
+            trk = np.genfromtxt(f, skiprows=100, usecols=(2, 6, 5, 3, 4, 56, 8))
         except (IOError, StopIteration):
             print "FAIL: {0}".format(f)
-            continue
-    
+            continue        
+        
+        # convert ages to yr
+        trk[:, 0] = trk[:, 0]*1.0e9
+
+        # convert Li to A(Li)
+        trk[:, 5] = np.log10(trk[:, 5]) + 12.0
+        
+        # interpolate to get properties at desired age 
         mass_index = f.rfind('/') + 2
         mass = float(f[mass_index:mass_index + 4])/1000.
         masses.append(mass)
         try:
-            icurve = AkimaSpline(trk[:, 0], trk[:, 1:])
+            icurve = interp1d(trk[:, 0], trk[:, 1:], kind='linear', axis=0)
         except:
             continue
     
@@ -42,6 +50,7 @@ for age in ages:
 
     header  = 'Dartmouth Stellar Evolution Model: Quick Isochrone \n\n'
     header += 'Age = {:7.1f} Myr   [Fe/H] = {:+5.2f}   [a/Fe] = {:+5.2f} \n\n'.format(age/1.e6, 0.0, 0.0)
-    header += '{:^14} {:^14} {:^14} {:^14} {:^14} {:^14}'.format('Mass', 'log(Teff)', 'log(g)', 'log(L/Lo)', 'log(R/Ro)', 'A(Li)')
-    np.savetxt('./dmestar_{:07.1f}myr_z+0.00_a+0.00_phx.iso'.format(age/1.e6), all_props, fmt='%14.7f', header=header)
+    header += '{:^14} {:^14} {:^14} {:^14} {:^14} {:^14} {:^14}'.format('Mass', 'log(Teff)', 'log(g)', 'log(L/Lo)', 
+                                                                        'log(R/Ro)', 'A(Li)', 'Mconv,env')
+    np.savetxt('./dmestar_{:07.1f}myr_z+0.00_a+0.00_phx_magBeq.iso'.format(age/1.e6), all_props, fmt='%14.7f', header=header)
     del all_props

### 2016-02-11 paper/ms.tex
radiative core mass comparision, shifted text in paper

@@
 
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=0.85\linewidth]{USCO5_MR.eps}
-    \caption{Mass-radius diagram for stars in eclipsing systems.
-{\bf Black points are from \citet{Kraus2015} and \citet{Alonso2015}, while gray points are taken from \citet{Lodieu2015} and \citet{David2015b}.} Model predictions for magnetic and non-magnetic isochrones are the same as in Fig.~\ref{fig:ages}.}
-    \label{fig:mrd}
-\end{figure}
-
 Both eclipsing systems exhibit a disagreement between their HR and mass-radius diagram age.
@@
 Introducing a magnetic perturbation as described in Sect.~\ref{sec:models}, a 10 Myr isochrone is computed and overlaid in the HR and mass-radius diagrams in Figs.~\ref{fig:ages} and \ref{fig:mrd} (thick yellow solid line).
-An age of 10 Myr was chosen as a starting point based on the approximate median age of the A-, F-, and G-type stars.
-Figures~\ref{fig:ages}a and \ref{fig:ages}c (HR diagrams) {\bf show that models}, at an age of 10 Myr with equipartition magnetic fields, are shifted toward cooler temperatures and slightly larger luminosities compared to a non-magnetic 10 Myr isochrone.
-Inhibition of convection by magnetic fields {\bf cools the stellar surface temperature thereby slowing} the contraction rate of young stars, which leads to stars having a larger radius and a larger luminosity at a given age.
-The combination of cooler surface temperatures and higher luminosities leads to a situation where a 10 Myr magnetic isochrone looks nearly identical to a non-magnetic isochrone at 5 Myr.
-In fact, the magnetic stellar model isochrone {\bf lies on top of} the 5 Myr standard model isochrone and {\bf within} the empirical stellar locus.
+An age of 10 Myr was chosen as a starting point based on the approximate median age of the A-, F-, and G-type stars determined from standard stellar evolution models.
+
+\begin{figure}[!b]
+    \centering
+    \includegraphics[width=0.90\linewidth]{USCO5_MR.eps}
+    \caption{Mass-radius diagram for stars in eclipsing systems.
+{\bf Black points are from \citet{Kraus2015} and \citet{Alonso2015}, while gray points are taken from \citet{Lodieu2015} and \citet{David2015b}.} Model predictions for magnetic and non-magnetic isochrones are the same as in Fig.~\ref{fig:ages}.}
+    \label{fig:mrd}
+\end{figure}
+
+Figures~\ref{fig:ages}a and \ref{fig:ages}c (HR diagrams) {\bf show that a 10 Myr isochrone computed with equipartition magnetic fields} is shifted toward cooler temperatures and higher luminosities compared to a 10 Myr non-magnetic isochrone.
+Inhibition of convection by magnetic fields {\bf cools the stellar surface temperature thereby slowing} the contraction rate of young stars, leading to stars having a larger radius and a larger luminosity at a given age.
+The combination of cooler surface temperatures and higher luminosities {\bf makes} a 10 Myr magnetic isochrone look nearly identical to a 5 Myr non-magnetic isochrone for effective temperatures {\bf below about 5\,000~K.
+The magnetic stellar model isochrone lies on top of the 5 Myr standard model isochrone in Figs.~\ref{fig:ages}a and \ref{fig:ages}c.
+It also lies entirely within} the empirical stellar locus for low-mass stars in Upper Scorpius.
+
+{\bf The magnetic model isochrone converges with the 10 Myr standard model isochrone at warmer effective temperatures reproducing, to some degree, an observed transition in the HR diagram from a 5 Myr to a 10 Myr standard model isochrone.
+For \teff\ $< 4\,500$~K, the magnetic isochrone closely matches predictions from a 5 Myr standard model isochrone.
+Compare this to the small segment of the magnetic isochrone above \teff\ $\sim 6\,000$~K, where the magnetic isochrone closely follows the 10 Myr standard model isochrone.
+Although the model predicted transition appears to occur over approximately the correct effective temperature domain, Fig.~\ref{fig:ages}a shows a sharper transition from a magnetic to a non-magnetic sequence between $4\,500 <$ \teff/K $< 6\,000$ compared to model predictions.
+This can be more clearly seen in Fig.~\ref{fig:empirical}, where the empirical median stellar locus exhibits a knee around \teff $\sim 4\,500$~K that roughly corresponds to the beginning of the transition region in Fig.~\ref{fig:ages}a.
+However, a distinct knee feature is absent from the magnetic model isochrone.
+
+In magnetic model space, this temperature domain corresponds to masses between $1.40$ and $1.56$ \msun.
+Inspection of Fig.~\ref{fig:mrd} reveals this mass range corresponds precisely to where the rapid thinning of the convection zone occurs, as expected.}
+
 Thus, a 10 Myr magnetic isochrone naturally explains the factor of two age difference observed between high- and low-mass stars, provided the high mass stars are not appreciably affected by non-standard physics (e.g., magnetic fields or rotation).
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.95\linewidth]{radiative_core_masses.eps}
+    \caption{Mass fraction of the stellar radiative core as a function of (a) total stellar mass and (b) effective temperature. }
+    \label{fig:rad_core}
+\end{figure}
 
@@
 The combination of these two effects suggests that the transition from a magnetic sequence to a non-magnetic sequence should coincide with the disappearance of the convective envelope.} % confirm discussion of super-adiabatic layers
-
-{\bf This observed transition is reproduced by the magnetic isochrone at 10 Myr, to some degree.
-For \teff\ $< 5\,000$~K, the magnetic isochrone closely matches predictions from a 5 Myr standard model isochrone, indicating magnetic inhibition of convection may be playing a role for stars at these temperatures.
-Compare this to the small segment of the magnetic isochrone above \teff\ $\sim 6\,000$~K, where it is beginning to converge with the 10 Myr standard model isochrone.
-Although the transition appears to occur over approximately the correct effective temperature domain, Fig.~\ref{fig:ages}a shows a sharp transition from a magnetic to a non-magnetic sequence between $5\,000 <$ \teff/K $< 6\,000$ whereas models predict a more gradual transition.
-In magnetic model space, this temperature domain corresponds to masses between $1.40$ and $1.56$ \msun.
-Inspection of Fig.~\ref{fig:mrd} reveals this mass range corresponds precisely to where the rapid thinning of the convection zone occurs, as expected.}
 

### 2016-02-18 paper/ms.tex
interpolation curve used to compute mass tracks
analysis of observational errors and the knee feature

@@
 \hypersetup{
-    bookmarks=true,                                  % show bookmarks bar in pdf reader
+	bookmarks=true,
     pdftitle={A Consistent 10 Myr Age for the Upper Scorpius OB Association},          % set pdf title          
@@
     \caption{Equipartition magnetic field strength predictions at 10 Myr.}
-    \begin{tabular*}{0.6\linewidth}{@{\extracolsep{\fill}}c c c}
+    \begin{tabular*}{0.7\linewidth}{@{\extracolsep{\fill}}c c c c}
         \hline\hline\noalign{\smallskip}
-        Mass (\msun) & \teff (K) & $\langle Bf \rangle_{\rm eq,\,surf}$ (kG) \\
+        Mass    & \teff & \logg  & $\langle Bf \rangle_{\rm eq,\,surf}$ \\
+        \noalign{\smallskip}
+        (\msun) &   (K) & (dex)  &   (kG) \\
         \noalign{\smallskip}\hline\noalign{\smallskip}
-        0.1  & 2920 & 2.58 \\
-        0.2  & 3127 & 2.54 \\
-        0.3  & 3260 & 2.56 \\
-        0.4  & 3371 & 2.57 \\
-        0.5  & 3463 & 2.56 \\
-        0.6  & 3551 & 2.52 \\
-        0.7  & 3640 & 2.47 \\
-        0.8  & 3735 & 2.40 \\
-        0.9  & 3836 & 2.29 \\
-        1.0  & 3962 & 2.12 \\
-        1.1  & 4099 & 1.94 \\
-        1.2  & 4340 & 1.80 \\
-        1.3  & 4617 & 1.69 \\
-        1.4  & 4976 & 1.56 \\
-        1.5  & 5565 & 1.29 \\
-        1.6  & 6281 & 0.94 \\
-        1.7  & 7004 & 0.77 \\
+        0.1 &   3060 &   4.16 &   2.64 \\
+  		0.2 &   3261 &   4.19 &   2.51 \\
+  		0.3 &   3396 &   4.20 &   2.44 \\
+  		0.4 &   3517 &   4.22 &   2.41 \\
+  		0.5 &   3639 &   4.24 &   2.38 \\
+  		0.6 &   3760 &   4.26 &   2.34 \\
+  		0.7 &   3888 &   4.28 &   2.29 \\
+  		0.8 &   4031 &   4.29 &   2.22 \\
+  		0.9 &   4195 &   4.30 &   2.14 \\
+  		1.0 &   4397 &   4.30 &   2.04 \\
+  		1.1 &   4641 &   4.30 &   1.92 \\
+  		1.2 &   4910 &   4.28 &   1.83 \\
+  		1.3 &   5214 &   4.25 &   1.73 \\
+  		1.4 &   5569 &   4.19 &   1.58 \\
+  		1.5 &   5995 &   4.06 &   1.29 \\
+  		1.6 &   6618 &   3.96 &   0.94 \\
+  		1.7 &   7403 &   4.15 &   0.76 \\
         \noalign{\smallskip}\hline
@@
 \begin{equation}
-    B_{\rm eq,\, surf} = \left(8\pi P_{\rm gas,\, surf}\right)^{1/2}.
+    B_{\rm eq,\, surf} = \left(8\pi P_{{\rm gas},\, \tau = 1}\right)^{1/2}.
 \end{equation}
@@
 A median empirical locus for the population is shown as black solid line with the 99\% confidence interval for the median value shown as a light-gray shaded region.
-Errorbars shown for the majority of stars with \teff\ $< 5\,500$~K are prescribed as described in Sect.~\ref{sec:data}.}
+Errorbars shown for the majority of stars with \teff~$< 5\,500$~K are prescribed as described in Sect.~\ref{sec:data}.}
     \label{fig:empirical}
@@
 \label{sec:results}
+
+\subsection{Standard Models}
 An HR diagram for Upper Scorpius is shown in Fig.~\ref{fig:ages}a.
@@
 
+\subsection{Magnetic Models}
 Introducing a magnetic perturbation as described in Sect.~\ref{sec:models}, a 10 Myr isochrone is computed and overlaid in the HR and mass-radius diagrams in Figs.~\ref{fig:ages} and \ref{fig:mrd} (thick yellow solid line).
@@
 
-\begin{figure}[!b]
+A 10 Myr magnetic isochrone naturally explains the factor of two age difference observed between high- and low-mass stars, provided the high-mass stars are not appreciably affected by additional non-standard physics (e.g., rotation).
+Figures~\ref{fig:ages}a and \ref{fig:ages}c (HR diagrams) {\bf show that a 10 Myr isochrone computed with equipartition magnetic fields} is shifted toward cooler temperatures and higher luminosities compared to a 10 Myr non-magnetic isochrone.
+Inhibition of convection by magnetic fields {\bf cools the stellar surface temperature thereby slowing} the contraction rate of young stars.
+Stars have a larger radius and a higher luminosity at a given age, as a result.
+The combination of cooler surface temperatures and higher luminosities {\bf makes} a 10 Myr magnetic isochrone look nearly identical to a 5 Myr non-magnetic isochrone for {\bf stars with} effective temperatures {\bf below about 5\,000~K.
+The magnetic stellar model isochrone lies on top of the 5 Myr standard model isochrone in Figs.~\ref{fig:ages}a and \ref{fig:ages}c and entirely within} the empirical stellar locus for low-mass stars in Upper Scorpius.
+
+{\bf The magnetic model isochrone also correctly converges toward the 10 Myr standard model isochrone at warmer effective temperatures.
+To some degree, this  convergence reproduces an observed transition in the empirical HR diagram where the age inferred from standard model isochrones shifts from 5 Myr to 10 Myr.
+Below \teff~$\sim 5\,000$~K, the magnetic isochrone closely matches predictions from a 5 Myr standard model isochrone.
+Compare this to the small segment of the magnetic isochrone above \teff\ $\sim 6\,000$~K.
+Here, the magnetic isochrone traces the 10 Myr standard model isochrone.
+Although the model predicted transition appears to occur over approximately the correct effective temperature domain, Fig.~\ref{fig:ages}a shows a sharper transition from a magnetic to a non-magnetic sequence between $4\,500 <$ \teff/K $< 6\,000$ compared to model predictions.
+This is more clearly seen in Fig.~\ref{fig:empirical}, where the empirical median stellar locus exhibits a knee around \teff $\sim 4\,500$~K that roughly corresponds to the beginning of the transition region in Fig.~\ref{fig:ages}a.
+A distinct knee feature is absent from the magnetic model isochrone.}
+
+%In magnetic model space, this temperature domain corresponds to masses between $1.40$ and $1.56$ \msun.
+Inspection of Fig.~\ref{fig:mrd} reveals this mass range corresponds precisely to where the rapid thinning of the convection zone occurs, as expected.}
+
+\begin{figure}[t]
     \centering
@@
 
-Figures~\ref{fig:ages}a and \ref{fig:ages}c (HR diagrams) {\bf show that a 10 Myr isochrone computed with equipartition magnetic fields} is shifted toward cooler temperatures and higher luminosities compared to a 10 Myr non-magnetic isochrone.
-Inhibition of convection by magnetic fields {\bf cools the stellar surface temperature thereby slowing} the contraction rate of young stars, leading to stars having a larger radius and a larger luminosity at a given age.
-The combination of cooler surface temperatures and higher luminosities {\bf makes} a 10 Myr magnetic isochrone look nearly identical to a 5 Myr non-magnetic isochrone for effective temperatures {\bf below about 5\,000~K.
-The magnetic stellar model isochrone lies on top of the 5 Myr standard model isochrone in Figs.~\ref{fig:ages}a and \ref{fig:ages}c.
-It also lies entirely within} the empirical stellar locus for low-mass stars in Upper Scorpius.
-
-{\bf The magnetic model isochrone converges with the 10 Myr standard model isochrone at warmer effective temperatures reproducing, to some degree, an observed transition in the HR diagram from a 5 Myr to a 10 Myr standard model isochrone.
-For \teff\ $< 4\,500$~K, the magnetic isochrone closely matches predictions from a 5 Myr standard model isochrone.
-Compare this to the small segment of the magnetic isochrone above \teff\ $\sim 6\,000$~K, where the magnetic isochrone closely follows the 10 Myr standard model isochrone.
-Although the model predicted transition appears to occur over approximately the correct effective temperature domain, Fig.~\ref{fig:ages}a shows a sharper transition from a magnetic to a non-magnetic sequence between $4\,500 <$ \teff/K $< 6\,000$ compared to model predictions.
-This can be more clearly seen in Fig.~\ref{fig:empirical}, where the empirical median stellar locus exhibits a knee around \teff $\sim 4\,500$~K that roughly corresponds to the beginning of the transition region in Fig.~\ref{fig:ages}a.
-However, a distinct knee feature is absent from the magnetic model isochrone.
-
-In magnetic model space, this temperature domain corresponds to masses between $1.40$ and $1.56$ \msun.
-Inspection of Fig.~\ref{fig:mrd} reveals this mass range corresponds precisely to where the rapid thinning of the convection zone occurs, as expected.}
-
-Thus, a 10 Myr magnetic isochrone naturally explains the factor of two age difference observed between high- and low-mass stars, provided the high mass stars are not appreciably affected by non-standard physics (e.g., magnetic fields or rotation).
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=0.95\linewidth]{radiative_core_masses.eps}
-    \caption{Mass fraction of the stellar radiative core as a function of (a) total stellar mass and (b) effective temperature. }
-    \label{fig:rad_core}
-\end{figure}
-
-Furthermore, the mass-radius diagram in Figure~\ref{fig:mrd} shows a 10 Myr magnetic isochrone provides reasonable agreement with the two low-mass eclipsing binary systems.
-It is apparent that magnetic inhibition of convection leads to more significant radius ``inflation'' at higher masses as compared to lower masses.
+Moreover, inspection of the mass-radius diagram in Figure~\ref{fig:mrd} shows a 10 Myr magnetic isochrone provides reasonable agreement with the two low-mass eclipsing binary systems.
+It is apparent that magnetic inhibition of convection leads to more significant radius ``inflation'' at higher masses compared to at lower masses.
 This effect leads to a change in slope of the model predicted mass-radius relationship that is consistent with observations.
 Although agreement is good, it is not perfect.
-{\bf Depending on whether mass and radius estimates are adopted from \citet{Kraus2015} or \citet{David2015b}, at 10 Myr the radii of the primary and secondary of UScoCTIO5 are either 3.2\% and 2.1\% \citeauthor{Kraus2015} larger than model predictions or 5.7\% and 6.6\% larger \citeauthor{David2015b}.} Similarly, models at 10 Myr predict radii that are 1.4\% too large and 1.5\% too small for the Ba and Bb components of HD 144548 at 10 Myr, respectively.
+{\bf Depending on whether mass and radius estimates are adopted from \citet{Kraus2015} or \citet{David2015b}, at 10 Myr the radii of the primary and secondary in UScoCTIO5 are either 3.2\% and 2.1\% (\citeauthor{Kraus2015}) larger than model predictions or 5.7\% and 6.6\% larger (\citeauthor{David2015b}).} Similarly, models at 10 Myr predict radii that are 1.4\% too large and 1.5\% too small for the Ba and Bb components of HD 144548 at 10 Myr, respectively.
 An age between 9.0 and 9.5 Myr is preferred for UScoCTIO5, while 10 Myr is the best fit age for HD 144548 Ba/Bb.
@@
 An age of {\bf 9 -- 10} Myr gives broad agreement across the HR and mass-radius diagrams.
-No stellar population in Upper Scorpius {\bf studied here robustly} supports the possibility that the median age of the association is 5 Myr old.
+No stellar population in Upper Scorpius {\bf studied here robustly} supports the possibility that the median age of the association is 5 Myr.
+There are, however, still age discrepancies that must be addressed.
 As noted above, the median age for F-type stars appears to be a few million years older than stars of other spectral types.
-This {\bf discrepancy} is {\bf perplexing} and should be explored further, especially considering that potential missing physics in the models would likely conspire to make F-stars older, not younger.
-Curiously, most F stars in Upper Scorpius are at a stage of evolution where radii increase and subsequently decrease over a period of roughly 4 Myr {\bf (e.g., HD 144548 A).
-The timescale for this process is} similar to the observed age discrepancy (see Fig.\ \ref{fig:bump} and text below for more details) and may be indicative of potential shortcomings in model physics.
+This {\bf discrepancy} is {\bf perplexing and deserves further investigation}, especially considering that potential missing physics in the models would likely conspire to make F-stars older, not younger.
+It should be noted that most F-type stars in Upper Scorpius are at a stage of evolution where models predict radii increase and subsequently decrease over a period of roughly 4 -- 8 Myr.
+{\bf The timescale for this process is} similar to the observed age discrepancy (see Fig.~\ref{fig:bump} in Sect.~\ref{sec:radius}) and may be indicative of potential shortcomings in existing model physics such as radiative opacities or nuclear reaction cross-sections.
 
@@
 
-Given that magnetic inhibition of convection is required to explain the anomalously young age of low-mass K- and M-type stars, it is worth considering at what mass or effective temperature the effects related to magnetism can be identified.
-%begins to play a significant role in governing stellar structure. 
+Given that magnetic inhibition of convection is required to explain the anomalously young age of low-mass K- and M-type stars, it is worth considering at which mass or effective temperature the effects related to magnetism cease to play an important role in governing stellar structure.
 Looking at Fig.\ \ref{fig:ages}a, early- to mid-G stars follow a 10 Myr standard stellar model isochrone.
-Instead of continuing the trend, late-G stars appear to deviate toward a 5 Myr isochrone around \teff\ $\sim 5\,750$ K.
+Instead of continuing the trend, late-G stars appear to slope toward a 5 Myr isochrone around \teff\ $\sim 5\,750$ K.
+The empirical sequence exhibits a shallower slope than the model isochrone at 10 Myr.
  %, evidenced by a flattening of the empirical locus.
-This may be an artifact of how the empirical locus was computed. However, it may indicate {\bf a transition} where the influence of magnetic inhibition of convection becomes identifiable.
+
+The shallower slope may be an artifact of how the empirical locus was computed, {\bf but this seems unlikely to be a dominant factor as the HR diagram is well-populated at this effective temperature.
+It is somewhat under-populated in the immediate vicinity of \teff~$= 5\,500$~K, but is once again well-populated near 4\,500~K.
+The general trend should therefore be robust against errors in how the empirical locus is computed.}
+
+{\bf Observational errors may also provide a plausible explanation for the shallower slope of the HR diagram in the vicinity of 5\,000~K.
+Below this temperature, stellar atmospheric opacity becomes dominated by molecular species, particularly TiO in the optical and H$_2$O in the infrared.
+It can be argued that the effective temperature scale used to determine the properties of K- and M-dwarfs is too cool by about 200 K.
+\citet{Preibisch1999} constructed an spectral type to effective temperature transformation at a gravity intermediate between dwarf and giant scales using the transformation derived for luminosity class IV objects by \citet{deJager1987}.
+Comparing their results to the 5 -- 30 Myr pre-main-sequence star temperature scale proposed by \citet{Pecaut2013}, one finds that the temperature scale adopted by \citeauthor{Preibisch1999} is about 100~K cooler for early K-type stars.
+However, this trend reverses around spectral type M0, with \citeauthor{Preibisch1999} finding temperatures about 100~K warmer than \citet{Pecaut2013} for early-to-late M-type stars.
+Considering these differences, the sharp knee feature in the HR diagram may be accentuated by the adoption of an erroneous temperature scale, but the general trend that late-K to M-type stars are significantly cooler than theoretical predictions at 10 Myr remains.
+Furthermore, \citet{Herczeg2015} independently find a temperature scale consistent with \citeauthor{Preibisch1999}'s using PHOENIX BT-Settl models \citep{Allard2011} to infer effective temperatures from infrared photometric colors.
+The evidence suggests the adopted temperature scale is not the dominant reason for the observed transition in the HR diagram.}
+
+Instead of being the result of observational errors, the shallower slope in the HR diagram may indicate {\bf a transition} where the influence of magnetic inhibition of convection becomes {\bf a critical component governing a star's structure}.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.95\linewidth]{radiative_core_masses.eps}
+    \caption{Mass fraction of the stellar radiative core as a function of (a) total stellar mass and (b) effective temperature. }
+    \label{fig:rad_core}
+\end{figure}
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.85\linewidth]{radius_bump.eps}
-    \caption{Brief period of radius inflation described in Sect.~\ref{sec:radius} for stars with masses of 1.60\msun\ (blue solid), 1.55\msun\ (green short-dashed), 1.50\msun\ (blue dash-dotted), 1.45\msun\ (yellow long-dashed).
-Mass tracks are computed without a magnetic field (i.e., non-magnetic configuration).
-Effective temperatures at these masses are characteristic of F stars at 10 Myr.}
-    \label{fig:bump}
-\end{figure}
-
 \subsection{Radius of HD 144548 A}
@@
 Still, confirmation of the star's radius would be beneficial for future investigations to ensure there are no adverse effects on the radii of the B components.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.85\linewidth]{radius_bump.eps}
+    \caption{Brief period of radius inflation described in Sect.~\ref{sec:radius} for stars with masses of 1.60\msun\ (blue solid), 1.55\msun\ (green short-dashed), 1.50\msun\ (blue dash-dotted), 1.45\msun\ (yellow long-dashed).
+Mass tracks are computed without a magnetic field (i.e., non-magnetic configuration).
+Effective temperatures at these masses are characteristic of F stars at 10 Myr.}
+    \label{fig:bump}
+\end{figure}
 
@@
 
-\bibliography{papers}
+\bibliography{papers.bib}
 

### 2016-02-20 paper/ms.tex
revised abstract

@@
     When determining absolute ages of identifiably young stellar populations, results strongly depend on which stars are studied.
-Cooler (K, M) stars typically yield ages that are systematically younger than warmer (A, F, G) stars, typically by a factor of two.
-I explore the possibility that this age discordance is the product of magnetic inhibition of convection in cool young stars.
-I demonstrate that the adoption of magnetic stellar evolution models yield a median age of {\bf 9 -- 10} Myr for the Upper Scorpius subgroup of the Scorpius-Centaurus OB Association.
-This age is consistent for stars with spectral types A through M, except for a subset of F-type stars that appear older.
-Agreement is shown for ages derived from the Hertzsprung-Russell diagram and using an empirical mass-radius relationship from eclipsing multiple-star systems.
-Surface magnetic field strengths required to produce agreement are {\bf of order 2.5 kG} and are predicted from \emph{a priori} estimates of equipartition values, meaning no fine-tuning of model parameters is necessary.
-{\bf A gradual convergence of magnetic isochrones with standard model isochrones of an equivalent age is predicted to occur with the thinning of convective envelopes in stars with masses above 1.2~$M_{\odot}$.
-The predicted convergence at 10 Myr occurs when the mass contained in the convective envelope is approximately equal to 40\% of the total stellar mass.
-This transition appears to coincide with a noted flattening of the Hertzsprung-Russell diagram morphology of Upper Scorpius.} Furthermore, depletion of lithium predicted from magnetic models appears in better agreement with observed lithium equivalent widths than predictions from non-magnetic models.
+Cooler (K, M) stars typically yield ages that are systematically younger than warmer (A, F, G) stars by a factor of two.
+I explore the possibility that {\bf these age discrepancies are} the {\bf result} of magnetic inhibition of convection in young cool stars {\bf by using magnetic stellar evolution isochrones to determine the age of the Upper Scorpius subgroup of the Scorpius-Centaurus OB Association.} A median age of 10 Myr consistent across spectral types A through M is found, except for a subset of F-type stars that appear significantly older.
+Agreement is shown for ages derived from the Hertzsprung-Russell diagram and {\bf from} the empirical mass-radius relationship defined by eclipsing multiple-star systems.
+Surface magnetic field strengths required to produce agreement are {\bf of order 2.5 kG} and are predicted from \emph{a priori} estimates of equipartition values.
+{\bf A region in the HR diagram is identified that plausibly connects stars whose structures are weakly influenced by the presence of magnetic fields with those whose structures are strongly influenced by magnetic fields.
+The models suggest this region is characterized by stars with rapidly thinning outer convective envelopes where the radiative core mass is greater than 80\% of the total stellar mass.} Furthermore, depletion of lithium predicted from magnetic models appears in better agreement with observed lithium equivalent widths than predictions from non-magnetic models.
 These results suggest that magnetic inhibition of convection plays an important role in the early evolution of low-mass stars and that it may be responsible for noted age discrepancies in young stellar populations.}

### 2016-02-21 models/quick_iso.py
tracks & isochrones with revised B-field strengths

@@ -14,9 +14,10 @@ masses = []
 for age in ages:
     print "Processing Age: {:07.1f} Myr".format(age/1.0e6)
     for f in files:
+        print "....File {:s}".format(f)
         try:
             # import age, log(Teff), log(g), log(L/Lo), log(R/Ro), N(Li), Mconv,env
-            trk = np.genfromtxt(f, skiprows=100, usecols=(2, 6, 5, 3, 4, 56, 8))
+            trk = np.genfromtxt(f, skiprows=10, usecols=(2, 6, 5, 3, 4, 56, 8))
         except (IOError, StopIteration):
             print "FAIL: {0}".format(f)
             continue        
@@ -36,7 +37,10 @@ for age in ages:
         except:
             continue
     
-        props = icurve(age)
+        try:
+            props = icurve(age)
+        except:
+            continue
         props = np.append(mass, props)
     
         try:

### 2016-02-22 paper/ms.tex
revised and expanded conclusions + acknowledgements

@@
 \label{sec:tellit}
-Stellar evolution models and literature data are used to derive ages for stars with spectral types A through M in Upper Scorpius.
-I find a revised median HR diagram age of {\bf 9 -- 10} Myr for A-, F-, and G-type stars, with the exception of a population of F-type stars that appear 5 Myr older.
-These results agree with the revised $11\pm3$ Myr of \citet{Pecaut2012}.
+Stellar evolution models and literature data are used to {\bf estimate} median ages for stars with spectral types A through M in Upper Scorpius.
+I find a median HR diagram age of {\bf 9 -- 10} Myr for A-, F-, and G-type stars, with the exception of a population of F-type stars that appear 5 Myr older.
+These results agree with the revised $11\pm3$ Myr {\bf proposed by} \citet{Pecaut2012}.
 At the same time, I confirm the HR diagram age of 4 -- 5 Myr for K- and M-type stars using standard stellar evolution isochrones \citep{Preibisch2012, Slesnick2008, Herczeg2015}.
-However, isochrone ages of K- and M-type stars in eclipsing multiple-star systems observed by \emph{Kepler}/K2 \citep{Kraus2015, Alonso2015} disagree with the HR diagram analysis and suggest ages between 6 and 8 Myr for the same stars.
+{\bf Notably}, isochronal ages of K- and M-type stars in eclipsing multiple-star systems observed by \emph{Kepler}/K2 \citep{Kraus2015, Alonso2015, David2015b} disagree with the HR diagram analysis and suggest ages between 6 and 8 Myr for the same stars.
 
-Application of stellar evolution models accounting for magnetic inhibition of convection \citep{FC12b, FC13} yields an age of {\bf 9 -- 10} Myr for K- and M-type stars in Upper Scorpius.
-Magnetic models provide a consistent explanation for the age discrepancy between high- and low-mass stars, as well as differences observed between HR diagram and mass-radius relationship ages.
-Magnetic models also reproduce the slope of the low-mass star mass-radius relationship.
-Critically, average surface magnetic field strengths are determined \emph{a priori} via equipartition arguments, highlighting the potential predictive power of magnetic stellar models of young stars.
-Furthermore, magnetic models around 10 Myr exhibit a lithium depletion pattern that is in agreement with inferences from observed lithium equivalent widths \citep{Rizzuto2015}.
+Using stellar evolution models {\bf that account} for magnetic inhibition of convection \citep{FC12b, FC13}, {\bf I find} an age of {\bf 9 -- 10} Myr for K- and M-type stars in Upper Scorpius.
+Magnetic inhibition of convection consistently explains:
+\begin{enumerate} 
+	\item the age discrepancy between high- and low-mass stars in the HR diagram,
+	\item the observed slope of the low-mass stellar mass-radius relationship,
+	\item stellar age differences observed between HR diagram and mass-radius relationship determinations,
+	\item and the lithium depletion pattern inferred from observed lithium equivalent widths \citep{Rizzuto2015}. 
+\end{enumerate}
+Critically, average surface magnetic field strengths are determined \emph{a priori} via equipartition arguments, highlighting the potential predictive power of magnetic stellar models for young stars.
 
-Results from this work and \citet{Pecaut2012} strongly support adoption of an approximately 10 Myr median age for the Upper Scorpius subgroup of the Scorpius-Centaurus OB association.
-There is no population of stars in the Upper Scorpius that unambiguously support an age of 5 Myr.
-Still, additional eclipsing binary systems are needed to further populate the mass-radius relationship and solidify Upper Scorpius as a 10 Myr old stellar association.
+Results from this work and \citet{Pecaut2012} strongly support the adoption of an approximately 10 Myr median age for the Upper Scorpius subgroup of the Scorpius-Centaurus OB association.
+There is no population of stars in the Upper Scorpius that unambiguously supports an age of 5 Myr.
+{\bf Nevertheless, additional eclipsing binary systems are needed to better populate the mass-radius relationship to solidify Upper Scorpius as a 10 Myr old stellar association and to verify predictions from magnetic stellar evolution models across the full mass spectrum.}
 
-Further work is needed to explore the impact of magnetic inhibition of convection on the (sub)stellar initial mass function for Upper Scorpius and other young stellar populations \citep[e.g.,][]{Ardila2000, Preibisch2002}.
-More work is also needed to explore whether magnetic inhibition of convection serves as a robust solution for noted age gradients as a function of \teff\ \citep{Naylor2009, Herczeg2015}.
-However, given the ease with which magnetic models appear to reconcile discrepancies in Upper Scorpius, the wider application of magnetic stellar models as a component of isochrone analyses is recommended.
-A small grid of magnetic stellar isochrones is under construction as is a web interface to request custom magnetic models.
+{\bf Further work is needed to explore whether magnetic inhibition of convection serves as a robust solution for noted age gradients as a function of stellar spectral type \citep[e.g.,][]{Naylor2009, Herczeg2015}.
+Previous work determining ages for the $\beta$-Pictoris moving group from magnetic stellar models suggests the solution is robust \citep{MM10, Malo2014, Binks2016}, but additional confirmation using stellar populations with a wider variety of ages is required.
+These results also highlight the need to explore how the inclusion of magnetic inhibition of convection affects the (sub)stellar initial mass function young stellar populations.}
+
+In the meantime, the use of magnetic stellar models as a component for isochrone analyses for young low-mass stars is recommended.
+Consistency across the HR and mass-radius diagrams exhibited by magnetic stellar evolution isochrones suggest that magnetic isochrones will provide a more accurate characterization of transiting exoplanet host stars in young stellar populations, especially those observed by \emph{Kepler}/K2 in Upper Scorpius.
+By adopting an incorrect age, a reasonable estimate of stellar radii can be found, but stellar masses will be systematically underestimated by roughly 30\%.
+Similar arguments apply to the characterization of young low-mass star hosting directly imaged giant planets or brown dwarfs.
+Ages inferred from standard model isochrones will be systematically too young by a factor of two resulting in a systematic underestimation of giant planet and brown dwarfs masses by roughly 35\%.
+To facilitate this work, all models used in this study are available online\footnote{\url{https://github.com/gfeiden/MagneticUpperSco/}}.
+In addition, a small grid of solar-metallicity magnetic stellar mass tracks and isochrones is under construction, as is a web-interface to compute custom magnetic models.
 
 \begin{acknowledgements}
-Thank you to Alexis Lavail, Eric Mamajek, James Silvester, and Eric Stempels for reading and commenting on an early version of this manuscript.
+G.A.F.
+thanks Alexis Lavail, Eric Mamajek, James Silvester, and Eric Stempels for reading and commenting on an early version of this manuscript as well as Bengt Gustafsson and Thomas Nordlander for interesting discussions that helped improved the manuscript.
 The magnetic Dartmouth stellar evolution code was originally developed with support of National Science Foundation (NSF) grant AST-0908345.
-This work made use of NASA's Astrophysics Data System (ADS) and the VizieR catalogue access tool by CDS in Strasbourg, France.
-Figures in this manuscript were produced with Gnuplot 5 \citep{Gnuplot5.0}.
+This work made use of NASA's Astrophysics Data System (ADS), the VizieR catalogue access tool by CDS in Strasbourg, France \citep{Ochsenbein2000}, and IPython with Jupyter notebooks \citep{Perez2007}.
+Figures in this manuscript were produced with Gnuplot~5 \citep{Gnuplot5.0}.
 \end{acknowledgements}

### 2016-02-22 paper/ms.tex
radiative core mass difference figure

@@
 
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.95\linewidth]{radiative_core_mass_difference.eps}
+    \caption{Difference in radiative core mass between magnetic and standard stellar evolution models as a function of effective temperature.
+The difference is shown as the radiative core mass of a magnetic model minus the radiative core mass of a standard stellar model at the same effective temperature, ($M_{\rm rad.\ core,\, mag} - M_{\rm rad.\ core,\, std}$).}
+    \label{fig:delta_mass}
+\end{figure}
+
 \subsection{Radius of HD 144548 A}
@@
 Previous work determining ages for the $\beta$-Pictoris moving group from magnetic stellar models suggests the solution is robust \citep{MM10, Malo2014, Binks2016}, but additional confirmation using stellar populations with a wider variety of ages is required.
-These results also highlight the need to explore how the inclusion of magnetic inhibition of convection affects the (sub)stellar initial mass function young stellar populations.}
+These results also highlight the need to explore how the inclusion of magnetic inhibition of convection affects the (sub)stellar initial mass function for young stellar populations.}
 
-In the meantime, the use of magnetic stellar models as a component for isochrone analyses for young low-mass stars is recommended.
+{\bf In the meantime, the use of magnetic stellar models as a component for isochrone analyses for young low-mass stars is recommended.
 Consistency across the HR and mass-radius diagrams exhibited by magnetic stellar evolution isochrones suggest that magnetic isochrones will provide a more accurate characterization of transiting exoplanet host stars in young stellar populations, especially those observed by \emph{Kepler}/K2 in Upper Scorpius.
 By adopting an incorrect age, a reasonable estimate of stellar radii can be found, but stellar masses will be systematically underestimated by roughly 30\%.
-Similar arguments apply to the characterization of young low-mass star hosting directly imaged giant planets or brown dwarfs.
-Ages inferred from standard model isochrones will be systematically too young by a factor of two resulting in a systematic underestimation of giant planet and brown dwarfs masses by roughly 35\%.
-To facilitate this work, all models used in this study are available online\footnote{\url{https://github.com/gfeiden/MagneticUpperSco/}}.
-In addition, a small grid of solar-metallicity magnetic stellar mass tracks and isochrones is under construction, as is a web-interface to compute custom magnetic models.
+Similar arguments apply to the characterization of young low-mass stars hosting directly imaged giant planets or brown dwarfs.
+Ages inferred from standard model isochrones may be systematically too young by a factor of two resulting in a systematic underestimation of giant planet and brown dwarfs masses by roughly 35\% \citep{Baraffe2003}.
+To facilitate their adoption, all models used in this study are available online\footnote{\url{https://github.com/gfeiden/MagneticUpperSco/}}.
+A small grid of solar-metallicity magnetic stellar mass tracks and isochrones is also under construction, as is a web-interface to compute custom magnetic models.}
 

### 2016-02-28 paper/ms.tex
small edits to magnetic turn off section

--- 2016-02-20 paper/ms.tex
@@
 
-{\bf Observational errors may also provide a plausible explanation for the shallower slope of the HR diagram in the vicinity of 5\,000~K.
-Below this temperature, stellar atmospheric opacity becomes dominated by molecular species, particularly TiO in the optical and H$_2$O in the infrared.
-It can be argued that the effective temperature scale used to determine the properties of K- and M-dwarfs is too cool by about 200 K.
+{\bf Errors transforming from photometric colors to effective temperatures may also provide a plausible explanation for the shallower slope of the HR diagram in the vicinity of 5\,000~K.
+Below this temperature, stellar atmospheric opacity becomes increasingly dominated by molecular species, particularly TiO in the optical and H$_2$O in the infrared, which poses problems when attempting to derive a robust effective temperature scale.
+If the effective temperature scale adopted by \citet{Preibisch1999} is too cool by about 200 K, the observed transition might disappear and low-mass K- and M-type stars would fall closer to the 10 Myr standard model isochrone.
+
 \citet{Preibisch1999} constructed an spectral type to effective temperature transformation at a gravity intermediate between dwarf and giant scales using the transformation derived for luminosity class IV objects by \citet{deJager1987}.
-Comparing their results to the 5 -- 30 Myr pre-main-sequence star temperature scale proposed by \citet{Pecaut2013}, one finds that the temperature scale adopted by \citeauthor{Preibisch1999} is about 100~K cooler for early K-type stars.
-However, this trend reverses around spectral type M0, with \citeauthor{Preibisch1999} finding temperatures about 100~K warmer than \citet{Pecaut2013} for early-to-late M-type stars.
-Considering these differences, the sharp knee feature in the HR diagram may be accentuated by the adoption of an erroneous temperature scale, but the general trend that late-K to M-type stars are significantly cooler than theoretical predictions at 10 Myr remains.
-Furthermore, \citet{Herczeg2015} independently find a temperature scale consistent with \citeauthor{Preibisch1999}'s using PHOENIX BT-Settl models \citep{Allard2011} to infer effective temperatures from infrared photometric colors.
-The evidence suggests the adopted temperature scale is not the dominant reason for the observed transition in the HR diagram.}
+This temperature scale is consistent with the more recent scale of \citet{Herczeg2015} who used PHOENIX BT-Settl model atmospheres \citep{Allard2011} to infer effective temperatures from photometric colors.
+Agreement between empirical methods and theoretical predictions is reassuring.
+However,
+comparing these results to the 5 -- 30 Myr pre-main-sequence star temperature scale proposed by \citet{Pecaut2013}, one finds that the temperature scale adopted by \citeauthor{Preibisch1999} is about 100~K cooler for early K-type stars, but the two temperature scales agree around spectral type M0.
+For early-to-late M-type stars, \citeauthor{Preibisch1999} find temperatures about 100~K warmer than \citet{Pecaut2013}, a reversal from the comparison for late-K-type stars.
+Considering these differences, the sharp knee feature in the HR diagram may be accentuated by the adoption of an erroneous temperature scale, but it does not appear sufficient to fully explain the shallower slope observed in the HR diagram.}
 
-Instead of being the result of observational errors, the shallower slope in the HR diagram may indicate {\bf a transition} where the influence of magnetic inhibition of convection becomes {\bf a critical component governing a star's structure}.
+Instead of being the result of errors in the data, the shallower slope in the HR diagram may indicate {\bf a real transition} where the influence of magnetic inhibition of convection becomes {\bf a more critical component governing a star's structure}.
 

### 2016-02-29 paper/ms.tex
additional comp in rad core + revised discussion

@@
 
-Given that magnetic inhibition of convection is required to explain the anomalously young age of low-mass K- and M-type stars, it is worth considering at which mass or effective temperature the effects related to magnetism cease to play an important role in governing stellar structure.
-Looking at Fig.\ \ref{fig:ages}a, early- to mid-G stars follow a 10 Myr standard stellar model isochrone.
-Instead of continuing the trend, late-G stars appear to slope toward a 5 Myr isochrone around \teff\ $\sim 5\,750$ K.
-The empirical sequence exhibits a shallower slope than the model isochrone at 10 Myr.
- %, evidenced by a flattening of the empirical locus.
+{\bf Figure~\ref{fig:ages} shows that a 10 Myr magnetic model isochrones traces a 5 Myr standard model isochrone for effective temperatures below about 5\,000~K, but traces a 10 Myr standard model isochrone above 6\,000~K.
+This suggests that magnetic inhibition plays an important role in dictating the structure of cool low-mass stars, but the structure of warmer high-mass stars are relatively insensitive to the influence of magnetic fields.
+In between these two regimes, the models predict a that a transition occurs in which stars appear to exhibit an increasing sensitivity to magnetic inhibition of convection as effective temperature decreases.
 
-The shallower slope may be an artifact of how the empirical locus was computed, {\bf but this seems unlikely to be a dominant factor as the HR diagram is well-populated at this effective temperature.
-It is somewhat under-populated in the immediate vicinity of \teff~$= 5\,500$~K, but is once again well-populated near 4\,500~K.
-The general trend should therefore be robust against errors in how the empirical locus is computed.}
+As was noted in Sect.~\ref{sec:results}, Figs.~\ref{fig:empirical} and \ref{fig:ages}a indicate that this transition occurs over a similar effective temperature domain in the HR diagram of Upper Scorpius.
+Early- to mid-G stars in Upper Scorpius (\teff$ \sim 6000$~K) are best described by a 10 Myr standard stellar model isochrone.
+Instead of continuing to follow a 10 Myr isochrone, late-G stars appear to be better represented by an isochrone intermediate between 5 and 10 Myr causing the empirical sequence to exhibit a shallower slope than standard model predictions between $5750 > T_{\rm eff} / {\rm K} > 5000$~K.
+Agreement between the transition region observed in the empirical data and the one predicted by magnetic stellar models suggests there is a physical explanation for the observed transition, but might there be an alternative explanation?
+}
 
-{\bf Errors transforming from photometric colors to effective temperatures may also provide a plausible explanation for the shallower slope of the HR diagram in the vicinity of 5\,000~K.
+{\bf The shallower slope may be an artifact of how the empirical locus was computed.
+The empirical HR diagram is somewhat under-populated in the immediate vicinity of \teff~$= 5\,500$~K, raising the possibility that the running median has artificially created a smooth transition between warmer and cooler stars.
+However, the HR diagram is well-populated at slightly warmer and slightly cooler temperatures, suggesting the two regions must be somehow connected.
+While the precise morphology of the HR diagram in this region may be subject to alteration with additional data, the general trend of should be robust against errors in how the empirical locus is computed.}
+
+{\bf Errors transforming from photometric colors or spectral types to effective temperatures may provide a plausible explanation for the shallower slope of the HR diagram in the vicinity of 5\,000~K.
 Below this temperature, stellar atmospheric opacity becomes increasingly dominated by molecular species, particularly TiO in the optical and H$_2$O in the infrared, which poses problems when attempting to derive a robust effective temperature scale.
-If the effective temperature scale adopted by \citet{Preibisch1999} is too cool by about 200 K, the observed transition might disappear and low-mass K- and M-type stars would fall closer to the 10 Myr standard model isochrone.
+This is particularly problematic for the HR diagram shown in Fig.~\ref{fig:empirical} because stars above \teff$ \sim 5\,000$~K were transformed from the observational to theoretical plane by different authors (\citealt{Pecaut2012} at warmer temperatures and \citealt{Preibisch1999} at cooler temperatures).
+If the effective temperature scale adopted by \citet{Preibisch1999} for cool stars is too cool by about 200 K, the observed transition might disappear and low-mass K- and M-type stars would fall closer to the 10 Myr standard model isochrone.
 
@@
 For early-to-late M-type stars, \citeauthor{Preibisch1999} find temperatures about 100~K warmer than \citet{Pecaut2013}, a reversal from the comparison for late-K-type stars.
-Considering these differences, the sharp knee feature in the HR diagram may be accentuated by the adoption of an erroneous temperature scale, but it does not appear sufficient to fully explain the shallower slope observed in the HR diagram.}
+Considering these differences, the sharp knee feature in the HR diagram may be accentuated by the adoption of an erroneous temperature scale, but it does not appear sufficient to fully explain the shallower slope observed in the HR diagram.
+}
 
-Instead of being the result of errors in the data, the shallower slope in the HR diagram may indicate {\bf a real transition} where the influence of magnetic inhibition of convection becomes {\bf a more critical component governing a star's structure}.
+{\bf The transition region observed in the HR diagram appears to be the result of a real transition in which the structure of stars becomes increasingly insensitive to magnetic inhibition of convection toward higher temperatures.
+Comparison of the empirical HR diagram to magnetic stellar models suggests that the transition's effective temperature domain begins somewhere between 4\,500~K and 5\,000~K, consistent with the knee observed in the empirical data at \teff$\sim 4\,500$~K.
+According to magnetic stellar models, these effective temperatures correspond to stars with masses between 1.26 \msun\ and 1.40 \msun.
+This is significant because stars in this mass regime are expected to have relatively thin convective envelopes that eventually disappear entirely.
+}
 
-\begin{figure}[t]
+{\bf % Not only for stars with M ~ 1.2... all intermediate mass stars above 0.28 Msun. 
+Convective envelopes in stars with masses greater than $\sim1.2$ $M_{\odot}$ gradually recede from the deep interior toward the stellar surface in response to the ignition of the proton-proton ($p$-$p$) chain, continued release of gravitational potential energy as the star contracts, and a decreasing radiative opacity due to rising gas temperatures \citep{Henyey1955}.
+During this time, the star's radius is predicted to increase.
+Eventually, the radius expansion is halted and the convective envelope disappears entirely following ignition of the CN-cycle.
+Prior to ignition of the CN-cycle, a thinning of the convective envelope means magnetic fields of a given strength will have a larger impact on the thermal structure of the super-adiabatic region.
+However, a restructuring of the super-adiabatic layers in a star with a thin convective envelope has less of an impact on the thermal structure of the deeper underlying layers, which are assumed to be in radiative equilibrium, than for a star whose interior is largely convective.
+The thinning of the convective envelope is also accompanied by a drop in the surface gas pressure as the star's radius inflates thereby lowering the permitted equipartition magnetic field strength.
+The combination of these two effects suggests that the transition from a magnetic sequence to a non-magnetic sequence should coincide with the disappearance of the convective envelope.} % confirm discussion of super-adiabatic layers
+
+\begin{figure*}[!ht]
     \centering
-    \includegraphics[width=0.95\linewidth]{radiative_core_masses.eps}
-    \caption{Mass fraction of the stellar radiative core as a function of (a) total stellar mass and (b) effective temperature. }
+    \includegraphics[width=0.42\linewidth]{radiative_core_masses.eps} \qquad
+    \includegraphics[width=0.48\linewidth]{radiative_core_mass_difference.eps}
+    \caption{Mass fraction of the stellar radiative core as a function of (a) total stellar mass and (b) effective temperature.
+(c) Difference in radiative core mass between magnetic and standard stellar evolution models as a function of effective temperature.
+The difference is shown as the radiative core mass of a magnetic model minus the radiative core mass of a standard stellar model at the same effective temperature, ($M_{\rm rad.\ core,\, mag} - M_{\rm rad.\ core,\, std}$), shown for two ages of standard models (5 Myr, 10 Myr).}
     \label{fig:rad_core}
-\end{figure}
-
-{\bf Predictions from stellar evolution models suggest a transition should exist.
-Convective envelopes in stars with masses greater than $\sim1.2$ $M_{\odot}$ gradually recede from the deep interior toward the stellar surface in response to the ignition of the proton-proton ($p$-$p$) chain and continued release of gravitational potential energy as the star contracts.
-Eventually, the convective envelope in these stars will disappear entirely following ignition of the CN-cycle.
-As the convective envelope grows thinner, magnetic fields of a given strength will have a larger impact on the thermal structure of the super-adiabatic region.
-However, a restructuring of the super-adiabatic layers in a star with a thin convective envelope has less of an impact on the thermal structure of the deeper layers, which are assumed to be in radiative equilibrium, than for a star whose interior is largely convective.
-The thinning of the convective envelope is also accompanied by a drop in surface gas pressure as the star's radius inflates, lowering the permitted equipartition magnetic field strength.
-The combination of these two effects suggests that the transition from a magnetic sequence to a non-magnetic sequence should coincide with the disappearance of the convective envelope.} % confirm discussion of super-adiabatic layers
+\end{figure*}
 
@@
 
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=0.95\linewidth]{radiative_core_mass_difference.eps}
-    \caption{Difference in radiative core mass between magnetic and standard stellar evolution models as a function of effective temperature.
+%\begin{figure}[t]
+%    \centering
+%    \includegraphics[width=0.95\linewidth]{radiative_core_mass_difference.eps}
+%    \caption{Difference in radiative core mass between magnetic and standard stellar evolution models as a function of effective temperature.
 The difference is shown as the radiative core mass of a magnetic model minus the radiative core mass of a standard stellar model at the same effective temperature, ($M_{\rm rad.\ core,\, mag} - M_{\rm rad.\ core,\, std}$).}
-    \label{fig:delta_mass}
-\end{figure}
+%    \label{fig:delta_mass}
+%\end{figure}
 
@@
 Still, confirmation of the star's radius would be beneficial for future investigations to ensure there are no adverse effects on the radii of the B components.
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=0.85\linewidth]{radius_bump.eps}
-    \caption{Brief period of radius inflation described in Sect.~\ref{sec:radius} for stars with masses of 1.60\msun\ (blue solid), 1.55\msun\ (green short-dashed), 1.50\msun\ (blue dash-dotted), 1.45\msun\ (yellow long-dashed).
-Mass tracks are computed without a magnetic field (i.e., non-magnetic configuration).
-Effective temperatures at these masses are characteristic of F stars at 10 Myr.}
-    \label{fig:bump}
-\end{figure}
 
@@
 The impact of significantly stronger magnetic fields on core convection and the subsequent effect on the properties of higher mass stars is reserved for a future investigation.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.85\linewidth]{radius_bump.eps}
+    \caption{Brief period of radius inflation described in Sect.~\ref{sec:radius} for stars with masses of 1.60\msun\ (blue solid), 1.55\msun\ (green short-dashed), 1.50\msun\ (blue dash-dotted), 1.45\msun\ (yellow long-dashed).
+Mass tracks are computed without a magnetic field (i.e., non-magnetic configuration).
+Effective temperatures at these masses are characteristic of F stars at 10 Myr.}
+    \label{fig:bump}
+\end{figure}
 

### 2016-03-02 paper/ms.tex
revising discussion

@@
 In between these two regimes, the models predict a that a transition occurs in which stars appear to exhibit an increasing sensitivity to magnetic inhibition of convection as effective temperature decreases.
+}
 
-As was noted in Sect.~\ref{sec:results}, Figs.~\ref{fig:empirical} and \ref{fig:ages}a indicate that this transition occurs over a similar effective temperature domain in the HR diagram of Upper Scorpius.
-Early- to mid-G stars in Upper Scorpius (\teff$ \sim 6000$~K) are best described by a 10 Myr standard stellar model isochrone.
-Instead of continuing to follow a 10 Myr isochrone, late-G stars appear to be better represented by an isochrone intermediate between 5 and 10 Myr causing the empirical sequence to exhibit a shallower slope than standard model predictions between $5750 > T_{\rm eff} / {\rm K} > 5000$~K.
-Agreement between the transition region observed in the empirical data and the one predicted by magnetic stellar models suggests there is a physical explanation for the observed transition, but might there be an alternative explanation?
+{\bf As was noted in Sect.~\ref{sec:results}, Figs.~\ref{fig:empirical} and \ref{fig:ages}a indicate that a similar transition occurs over roughly the same effective temperature domain in the empirical HR diagram of Upper Scorpius.
+Early- to mid-G stars in Upper Scorpius (\teff$ \sim 6\,000$~K) are best described by a 10 Myr standard stellar model isochrone.
+Instead of continuing to follow a 10 Myr standard model isochrone, late-G stars appear to be better represented by an isochrone intermediate between 5 and 10 Myr causing the empirical sequence to exhibit a shallower slope than standard model predictions between $5\,750 > T_{\rm eff} / {\rm K} > 4\,500$~K.
+That the shallower slope in the empirical HR diagram and the transition predicted by magnetic stellar models are coincident, suggests that the two phenomena may be connected.
 }
+
+\begin{figure*}[!ht]
+    \centering
+    \includegraphics[width=0.42\linewidth]{radiative_core_masses.eps} \qquad
+    \includegraphics[width=0.48\linewidth]{radiative_core_mass_difference.eps}
+    \caption{Mass fraction of the stellar radiative core as a function of (a) total stellar mass and (b) effective temperature.
+(c) Difference in radiative core mass between magnetic and standard stellar evolution models as a function of effective temperature.
+The difference is shown as the radiative core mass of a magnetic model minus the radiative core mass of a standard stellar model at the same effective temperature, ($M_{\rm rad.\ core,\, mag} - M_{\rm rad.\ core,\, std}$), shown for two ages of standard models (5 Myr, 10 Myr).}
+    \label{fig:rad_core}
+\end{figure*}
+
+{\bf The transition exhibited by theoretical magnetic models can be explained by the rapid thinning of outer convective envelopes in stars with masses above about 1.2 $M_{\odot}$.
+Once a star reaches an effective temperature of 6\,000 K, it has either a very small or non-existent convective envelope.
+This provides a natural explanation the convergence of the 10 Myr magnetic isochrone with the 10 Myr standard model isochrone that occurs near this effective temperature in Fig.~\ref{fig:ages}(b).
+
+Assuming that a change in slope of the empirical HR diagram is observed at 4\,500 K, 
+Comparison of the empirical HR diagram to magnetic stellar models suggests that the transition's effective temperature domain begins somewhere between 4\,500~K and 5\,000~K, consistent with the knee observed in the empirical data at \teff$\sim 4\,500$~K.
+According to magnetic stellar models, these effective temperatures correspond to stars with masses between 1.26 \msun\ and 1.40 \msun.
+This is significant because stars in this mass regime are expected to have relatively thin convective envelopes that eventually disappear entirely.
+}
+
+{\bf % Not only for stars with M ~ 1.2... all intermediate mass stars above 0.28 Msun. 
+Convective envelopes in stars with masses greater than $\sim1.2$ $M_{\odot}$ gradually recede from the deep interior toward the stellar surface in response to the ignition of the proton-proton ($p$-$p$) chain, continued release of gravitational potential energy as the star contracts, and a decreasing radiative opacity due to rising gas temperatures \citep{Henyey1955}.
+During this time, the star's radius is predicted to increase.
+Eventually, the radius expansion is halted and the convective envelope disappears entirely following ignition of the CN-cycle.
+Prior to ignition of the CN-cycle, a thinning of the convective envelope means magnetic fields of a given strength will have a larger impact on the thermal structure of the super-adiabatic region.
+However, a restructuring of the super-adiabatic layers in a star with a thin convective envelope has less of an impact on the thermal structure of the deeper underlying layers, which are assumed to be in radiative equilibrium, than for a star whose interior is largely convective.
+The thinning of the convective envelope is also accompanied by a drop in the surface gas pressure as the star's radius inflates thereby lowering the permitted equipartition magnetic field strength.
+The combination of these two effects suggests that the transition from a magnetic sequence to a non-magnetic sequence should coincide with the disappearance of the convective envelope.} % confirm discussion of super-adiabatic layers
+
+{\bf While this behavior is expected in the magnetic models, it does not need to necessarily correspond to the observed transition.
+General agreement between the behavior of the magnetic model isochrone and the observed stellar locus provides evidence that magnetic inhibition of convection is the mechanism responsible for the age discrepancy between the high- and low-mass stellar populations.
+However, it is clear that this statement only holds with respect to the plausible identification of a general mechanism with the models failing to reproduce the precise morphology at the magnetic sequence turn-off.}
 
@@
 }
-
-{\bf The transition region observed in the HR diagram appears to be the result of a real transition in which the structure of stars becomes increasingly insensitive to magnetic inhibition of convection toward higher temperatures.
-Comparison of the empirical HR diagram to magnetic stellar models suggests that the transition's effective temperature domain begins somewhere between 4\,500~K and 5\,000~K, consistent with the knee observed in the empirical data at \teff$\sim 4\,500$~K.
-According to magnetic stellar models, these effective temperatures correspond to stars with masses between 1.26 \msun\ and 1.40 \msun.
-This is significant because stars in this mass regime are expected to have relatively thin convective envelopes that eventually disappear entirely.
-}
-
-{\bf % Not only for stars with M ~ 1.2... all intermediate mass stars above 0.28 Msun. 
-Convective envelopes in stars with masses greater than $\sim1.2$ $M_{\odot}$ gradually recede from the deep interior toward the stellar surface in response to the ignition of the proton-proton ($p$-$p$) chain, continued release of gravitational potential energy as the star contracts, and a decreasing radiative opacity due to rising gas temperatures \citep{Henyey1955}.
-During this time, the star's radius is predicted to increase.
-Eventually, the radius expansion is halted and the convective envelope disappears entirely following ignition of the CN-cycle.
-Prior to ignition of the CN-cycle, a thinning of the convective envelope means magnetic fields of a given strength will have a larger impact on the thermal structure of the super-adiabatic region.
-However, a restructuring of the super-adiabatic layers in a star with a thin convective envelope has less of an impact on the thermal structure of the deeper underlying layers, which are assumed to be in radiative equilibrium, than for a star whose interior is largely convective.
-The thinning of the convective envelope is also accompanied by a drop in the surface gas pressure as the star's radius inflates thereby lowering the permitted equipartition magnetic field strength.
-The combination of these two effects suggests that the transition from a magnetic sequence to a non-magnetic sequence should coincide with the disappearance of the convective envelope.} % confirm discussion of super-adiabatic layers
-
-\begin{figure*}[!ht]
-    \centering
-    \includegraphics[width=0.42\linewidth]{radiative_core_masses.eps} \qquad
-    \includegraphics[width=0.48\linewidth]{radiative_core_mass_difference.eps}
-    \caption{Mass fraction of the stellar radiative core as a function of (a) total stellar mass and (b) effective temperature.
-(c) Difference in radiative core mass between magnetic and standard stellar evolution models as a function of effective temperature.
-The difference is shown as the radiative core mass of a magnetic model minus the radiative core mass of a standard stellar model at the same effective temperature, ($M_{\rm rad.\ core,\, mag} - M_{\rm rad.\ core,\, std}$), shown for two ages of standard models (5 Myr, 10 Myr).}
-    \label{fig:rad_core}
-\end{figure*}
-
-{\bf While this behavior is expected in the magnetic models, it does not need to necessarily correspond to the observed transition.
-General agreement between the behavior of the magnetic model isochrone and the observed stellar locus provides evidence that magnetic inhibition of convection is the mechanism responsible for the age discrepancy between the high- and low-mass stellar populations.
-However, it is clear that this statement only holds with respect to the plausible identification of a general mechanism with the models failing to reproduce the precise morphology at the magnetic sequence turn-off.}
 

### 2016-03-04 paper/ms.tex
revised discussion, added refs to Iben & Bodenheimer

@@
 
-\subsection{Magnetic Sequence Turn-off}
+\subsection{Magnetic Field Evolution \& Radiative Core Growth}
 \label{sec:dynamo}
@@
 {\bf Figure~\ref{fig:ages} shows that a 10 Myr magnetic model isochrones traces a 5 Myr standard model isochrone for effective temperatures below about 5\,000~K, but traces a 10 Myr standard model isochrone above 6\,000~K.
-This suggests that magnetic inhibition plays an important role in dictating the structure of cool low-mass stars, but the structure of warmer high-mass stars are relatively insensitive to the influence of magnetic fields.
-In between these two regimes, the models predict a that a transition occurs in which stars appear to exhibit an increasing sensitivity to magnetic inhibition of convection as effective temperature decreases.
+This suggests that magnetic inhibition plays an important role in dictating the structure of cool low-mass stars, but the structure of warmer high-mass stars is relatively insensitive to the influence of magnetic fields.
+In between these two regimes, the models predict a transition in which stars appear to exhibit an increasing sensitivity to magnetic inhibition of convection as effective temperature decreases.
 }
@@
 Early- to mid-G stars in Upper Scorpius (\teff$ \sim 6\,000$~K) are best described by a 10 Myr standard stellar model isochrone.
-Instead of continuing to follow a 10 Myr standard model isochrone, late-G stars appear to be better represented by an isochrone intermediate between 5 and 10 Myr causing the empirical sequence to exhibit a shallower slope than standard model predictions between $5\,750 > T_{\rm eff} / {\rm K} > 4\,500$~K.
+Instead of continuing to follow a 10 Myr standard model isochrone, late-G stars appear to be better represented by an isochrone intermediate between 5 and 10 Myr causing the empirical sequence to exhibit a shallower slope than standard model predictions between $5\,750 > T_{\rm eff} / {\rm K} > 4\,500$.
 That the shallower slope in the empirical HR diagram and the transition predicted by magnetic stellar models are coincident, suggests that the two phenomena may be connected.
@@
 
-{\bf The transition exhibited by theoretical magnetic models can be explained by the rapid thinning of outer convective envelopes in stars with masses above about 1.2 $M_{\odot}$.
-Once a star reaches an effective temperature of 6\,000 K, it has either a very small or non-existent convective envelope.
-This provides a natural explanation the convergence of the 10 Myr magnetic isochrone with the 10 Myr standard model isochrone that occurs near this effective temperature in Fig.~\ref{fig:ages}(b).
+{\bf The transition exhibited by theoretical magnetic models can be explained by a rapid thinning of outer convective envelopes in stars with masses above about 1.2 $M_{\odot}$.
+Once a star reaches an effective temperature of 6\,000 K, it has a very small or non-existent convective envelope.
+In the absence of a convective envelope, magnetic inhibition of convection is irrelevant.
+Therefore, any differences observed between magnetic and standard stellar model isochrones at this effective temperature are the result of the magnetic field's influence on stellar structure at earlier evolutionary phases.
+This provides a natural explanation for the convergence of the 10 Myr magnetic isochrone with the 10 Myr standard model isochrone that occurs near this effective temperature in Fig.~\ref{fig:ages}(b).
+It then seems reasonable to posit that the shallow slope of the empirical HR diagram and the observed transition in the magnetic models trace the demise of outer convective envelopes and the growth of radiative cores in young, pre-main-sequence stars.}
 
-Assuming that a change in slope of the empirical HR diagram is observed at 4\,500 K, 
+{\bf % Not only for stars with M ~ 1.2... all intermediate mass stars above 0.28 Msun. 
+Stars with masses above about $0.28\ M_{\odot}$ are predicted to, at least temporarily, form a small radiative core during their pre-main-sequence contraction.
+Release of gravitational potential energy as stars contract heats the gas causing radiative opacities to decrease and igniting fusion from the proton-proton ($p$-$p$) chain \citep{Henyey1955}.
+Stars with masses below about $1.2\ M_{\odot}$ continue to contract until energy production from the $p$-$p$ chain is sufficient to stabilize the core (and thus the star) against further contraction.
+However, above $1.2\ M_{\odot}$, core temperatures become sufficiently hot enough to produce hydrogen burning via the CN-cycle at an appreciable level.
+Increased energy production from the CN-cycle, while initially insufficient to support the core against gravitational contraction, causes the radiative core to continue growing and the convective envelope to continue shrinking.
+Increasing energy production from the CN-cycle and $p$-$p$ chain causes a star's outer layers are predicted to expand while the core's contraction slows.
+Eventually, the CN-cycle reaches equilibrium, a convective core develops, the radius expansion is reversed, and the convective envelope disappears entirely \citep{Iben1965,Bodenheimer1965}.
+}
+
+{\bf 
+To fully understand the model-predicted transition in Fig.~\ref{fig:ages}(a) and the reasons why magnetic models do not entirely reproduce the morphology of the empirical transition, it is important to consider how the magnetic field evolves as a star's convective envelope shrinks.
+Prior to ignition of the CN-cycle, a thinning of the convective envelope means magnetic fields of a given strength will have a larger impact on the thermal structure of the super-adiabatic region.
+However, a restructuring of the super-adiabatic layers in a star with a thin convective envelope has less of an impact on the thermal structure of the deeper underlying layers, which are assumed to be in radiative equilibrium, than for a star whose interior is largely convective.
+The thinning of the convective envelope is also accompanied by a drop in the surface gas pressure as the star's radius inflates thereby lowering the permitted equipartition magnetic field strength.
+The combination of these two effects suggests that the transition from a magnetic sequence to a non-magnetic sequence should coincide with the disappearance of the convective envelope.} % confirm discussion of super-adiabatic layers
+
+{\bf Assuming that a change in slope of the empirical HR diagram is observed at 4\,500 K, 
 Comparison of the empirical HR diagram to magnetic stellar models suggests that the transition's effective temperature domain begins somewhere between 4\,500~K and 5\,000~K, consistent with the knee observed in the empirical data at \teff$\sim 4\,500$~K.
@@
 }
-
-{\bf % Not only for stars with M ~ 1.2... all intermediate mass stars above 0.28 Msun. 
-Convective envelopes in stars with masses greater than $\sim1.2$ $M_{\odot}$ gradually recede from the deep interior toward the stellar surface in response to the ignition of the proton-proton ($p$-$p$) chain, continued release of gravitational potential energy as the star contracts, and a decreasing radiative opacity due to rising gas temperatures \citep{Henyey1955}.
-During this time, the star's radius is predicted to increase.
-Eventually, the radius expansion is halted and the convective envelope disappears entirely following ignition of the CN-cycle.
-Prior to ignition of the CN-cycle, a thinning of the convective envelope means magnetic fields of a given strength will have a larger impact on the thermal structure of the super-adiabatic region.
-However, a restructuring of the super-adiabatic layers in a star with a thin convective envelope has less of an impact on the thermal structure of the deeper underlying layers, which are assumed to be in radiative equilibrium, than for a star whose interior is largely convective.
-The thinning of the convective envelope is also accompanied by a drop in the surface gas pressure as the star's radius inflates thereby lowering the permitted equipartition magnetic field strength.
-The combination of these two effects suggests that the transition from a magnetic sequence to a non-magnetic sequence should coincide with the disappearance of the convective envelope.} % confirm discussion of super-adiabatic layers
 

### 2016-03-08 paper/ms.tex
continuing the discussion

@@
 
-{\bf Figure~\ref{fig:ages} shows that a 10 Myr magnetic model isochrones traces a 5 Myr standard model isochrone for effective temperatures below about 5\,000~K, but traces a 10 Myr standard model isochrone above 6\,000~K.
-This suggests that magnetic inhibition plays an important role in dictating the structure of cool low-mass stars, but the structure of warmer high-mass stars is relatively insensitive to the influence of magnetic fields.
-In between these two regimes, the models predict a transition in which stars appear to exhibit an increasing sensitivity to magnetic inhibition of convection as effective temperature decreases.
+{\bf Figure~\ref{fig:ages} shows that a 10 Myr magnetic model isochrone agrees with predictions from a 5 Myr standard model isochrone for effective temperatures below about 5\,000~K, but traces a 10 Myr standard model isochrone above 6\,000~K.
+This suggests that magnetic inhibition of convection plays an important role in dictating the structure of cool low-mass stars, but the structure of warmer high-mass stars is relatively insensitive to the influence of magnetic fields.
+In between these two regimes, models predict a transition in which stars appear to exhibit a decreasing sensitivity to magnetic inhibition of convection as effective temperature increases.
 }
@@
 Early- to mid-G stars in Upper Scorpius (\teff$ \sim 6\,000$~K) are best described by a 10 Myr standard stellar model isochrone.
-Instead of continuing to follow a 10 Myr standard model isochrone, late-G stars appear to be better represented by an isochrone intermediate between 5 and 10 Myr causing the empirical sequence to exhibit a shallower slope than standard model predictions between $5\,750 > T_{\rm eff} / {\rm K} > 4\,500$.
+Instead of continuing to follow a 10 Myr standard model isochrone, late-G stars appear to be better represented by an isochrone intermediate between 5 and 10 Myr.
+This causes the empirical sequence to exhibit a shallower slope than standard model predictions between $5\,750 > T_{\rm eff} / {\rm K} > 4\,500$.
 That the shallower slope in the empirical HR diagram and the transition predicted by magnetic stellar models are coincident, suggests that the two phenomena may be connected.
@@
 
-{\bf The transition exhibited by theoretical magnetic models can be explained by a rapid thinning of outer convective envelopes in stars with masses above about 1.2 $M_{\odot}$.
-Once a star reaches an effective temperature of 6\,000 K, it has a very small or non-existent convective envelope.
+{\bf The transition exhibited by theoretical magnetic models can be explained by a rapid thinning of outer convective envelopes in stars with masses above about 1.2 $M_{\odot}$ \citep[e.g.,][]{Iben1965}.
+Once a star reaches an effective temperature of 6\,000 K, it has a very small or non-existent convective envelope, independent of whether or not magnetic inhibition of convection is considered.
 In the absence of a convective envelope, magnetic inhibition of convection is irrelevant.
-Therefore, any differences observed between magnetic and standard stellar model isochrones at this effective temperature are the result of the magnetic field's influence on stellar structure at earlier evolutionary phases.
-This provides a natural explanation for the convergence of the 10 Myr magnetic isochrone with the 10 Myr standard model isochrone that occurs near this effective temperature in Fig.~\ref{fig:ages}(b).
-It then seems reasonable to posit that the shallow slope of the empirical HR diagram and the observed transition in the magnetic models trace the demise of outer convective envelopes and the growth of radiative cores in young, pre-main-sequence stars.}
+Therefore, any differences between magnetic and standard stellar model isochrones above this effective temperature are the result of the magnetic field's influence on stellar structure at earlier evolutionary phases (i.e., delayed contraction).
+This naturally explains the convergence of the 10 Myr magnetic isochrone with the 10 Myr standard model isochrone, which occurs near $6\,000$~K in Fig.~\ref{fig:ages}(b).
+It then seems reasonable to posit that the shallow slope of the empirical HR diagram traces the demise of surface convection zones, the weakening of surface magnetic dynamo action, and the growth of radiative cores in young, pre-main-sequence stars.}
 
@@
 General agreement between the behavior of the magnetic model isochrone and the observed stellar locus provides evidence that magnetic inhibition of convection is the mechanism responsible for the age discrepancy between the high- and low-mass stellar populations.
-However, it is clear that this statement only holds with respect to the plausible identification of a general mechanism with the models failing to reproduce the precise morphology at the magnetic sequence turn-off.}
+However, it is clear that this statement only holds with respect to the plausible identification of a general mechanism as the models fail to reproduce the precise morphology at the magnetic sequence turn-off.}
 

### 2016-03-26 paper/ms.tex
continuing to work on the discussion

@@
 Therefore, any differences between magnetic and standard stellar model isochrones above this effective temperature are the result of the magnetic field's influence on stellar structure at earlier evolutionary phases (i.e., delayed contraction).
-This naturally explains the convergence of the 10 Myr magnetic isochrone with the 10 Myr standard model isochrone, which occurs near $6\,000$~K in Fig.~\ref{fig:ages}(b).
-It then seems reasonable to posit that the shallow slope of the empirical HR diagram traces the demise of surface convection zones, the weakening of surface magnetic dynamo action, and the growth of radiative cores in young, pre-main-sequence stars.}
+This naturally explains the convergence of the 10 Myr magnetic isochrone with the 10 Myr standard model isochrone near $6\,000$~K in Fig.~\ref{fig:ages}(b).
+It then seems reasonable to posit that the slope of the empirical HR diagram in this temperature domain contains information about the demise of surface convection zones, the growth of radiative cores, and the weakening of surface magnetic dynamo action in young, pre-main-sequence stars.}
+
+{\bf The beginning of the transition between 4\,500 and 5\,000 K corresponds to magnetic models masses of 1.26 $M_{\odot}$ and 1.40 $M_{\odot}$.
+Magnetic models predict that these stars have radiative core masses between 75\% and 88\% of their total stellar mass, respectively (see Figure~\ref{fig:rad_core}a).
+The 1.40 $M_{\odot}$ model is of particular note, as Figure~\ref{fig:mrd} predicts that 1.40 $M_{\odot}$ stars are beginning to enter a brief period of radius inflation that accompanies the ignition of CN-cycle burning \citep{Iben1965}.
+Photospheric gas pressures rapidly drop during this phase of evolution.
+A rapid drop in photospheric gas pressure will bring about a rapid drop in surface equipartition magnetic field strengths.
+As expected, a rapid decrease in equipartition magnetic field strengths is observed among the data in Table~\ref{fig:equip_values} beginning around 1.40 $M_{\odot}$.
+Stars above 1.40 $M_{\odot}$ then become less sensitive to magnetic inhibition of convection because the magnetic fields are intrinsically weaker.}
+
+{\bf However, disagreement between model predictions and the properties observed for F-type stars raises concerns that }
+
+{\bf
+Figure~\ref{fig:rad_core} compares predictions of radiative core masses as a function of stellar mass and effective temperature from standard models at 5 and 10 Myr (characteristic ages for cool and warm stars) and from magnetic models at 10 Myr.
+As a function of mass, magnetic models predict stars to have small radiative cores at 10 Myr, a result of delayed contraction.
+Stars of a given mass take longer to contract down the Hayashi track when magnetic inhibition of convection is included.
+Core temperatures required to initiate the formation of a radiative core are thus delayed.
+}
+
+{\bf However, when comparing radiative core masses as a function of effective temperature, stars of a given effective temperature have significantly larger radiative core masses when magnetic fields are included.
+}
 

### 2016-03-29 paper/ms.tex
headway on magnetic topology

--- 2016-03-08 paper/ms.tex
@@
 {\bf The transition exhibited by theoretical magnetic models can be explained by a rapid thinning of outer convective envelopes in stars with masses above about 1.2 $M_{\odot}$ \citep[e.g.,][]{Iben1965}.
-Once a star reaches an effective temperature of 6\,000 K, it has a very small or non-existent convective envelope, independent of whether or not magnetic inhibition of convection is considered.
+Once a star reaches an effective temperature of 6\,000 K, it has a very small or non-existent convective envelope, as shown in Fig.~\ref{fig:rad_core}(b).
+Figures~\ref{fig:rad_core}(a) and (b) show this is independent of age and mass, a fact arising as a result of the hydrogen ionization zone becoming increasingly localized near the optical photosphere with increasing effective temperature.
 In the absence of a convective envelope, magnetic inhibition of convection is irrelevant.
-Therefore, any differences between magnetic and standard stellar model isochrones above this effective temperature are the result of the magnetic field's influence on stellar structure at earlier evolutionary phases (i.e., delayed contraction).
-This naturally explains the convergence of the 10 Myr magnetic isochrone with the 10 Myr standard model isochrone, which occurs near $6\,000$~K in Fig.~\ref{fig:ages}(b).
-It then seems reasonable to posit that the shallow slope of the empirical HR diagram traces the demise of surface convection zones, the weakening of surface magnetic dynamo action, and the growth of radiative cores in young, pre-main-sequence stars.}
+Therefore, any differences observed between magnetic and standard stellar model isochrones at this effective temperature are the result of the magnetic field's influence on stellar structure at earlier evolutionary phases (i.e., delayed contraction).
+This provides a natural explanation for the convergence of the 10 Myr magnetic and standard model isochrones that occurs near this effective temperature in Fig.~\ref{fig:ages}(b).
+It then seems reasonable to posit that the shallow slope of the empirical HR diagram and the observed transition in the magnetic models trace the demise of outer convective envelopes and the growth of radiative cores in young, pre-main-sequence stars.}
 
-{\bf % Not only for stars with M ~ 1.2... all intermediate mass stars above 0.28 Msun. 
-Stars with masses above about $0.28\ M_{\odot}$ are predicted to, at least temporarily, form a small radiative core during their pre-main-sequence contraction.
-Release of gravitational potential energy as stars contract heats the gas causing radiative opacities to decrease and igniting fusion from the proton-proton ($p$-$p$) chain \citep{Henyey1955}.
-Stars with masses below about $1.2\ M_{\odot}$ continue to contract until energy production from the $p$-$p$ chain is sufficient to stabilize the core (and thus the star) against further contraction.
-However, above $1.2\ M_{\odot}$, core temperatures become sufficiently hot enough to produce hydrogen burning via the CN-cycle at an appreciable level.
-Increased energy production from the CN-cycle, while initially insufficient to support the core against gravitational contraction, causes the radiative core to continue growing and the convective envelope to continue shrinking.
-Increasing energy production from the CN-cycle and $p$-$p$ chain causes a star's outer layers are predicted to expand while the core's contraction slows.
-Eventually, the CN-cycle reaches equilibrium, a convective core develops, the radius expansion is reversed, and the convective envelope disappears entirely \citep{Iben1965,Bodenheimer1965}.
-}
+{\bf While the demise of outer convection zones explains the final convergence of magnetic and standard models, it doesn't necessarily explain the beginning of the transition between  4\,500~K and 5\,000~K.
+Figures~\ref{fig:ages}(a) and \ref{fig:rad_core}(b) indicate that stars with \teff~<~4\,500~K can possess radiative cores that comprise up to about 75\% of the star, by mass.}
 
-{\bf 
-To fully understand the model-predicted transition in Fig.~\ref{fig:ages}(a) and the reasons why magnetic models do not entirely reproduce the morphology of the empirical transition, it is important to consider how the magnetic field evolves as a star's convective envelope shrinks.
-Prior to ignition of the CN-cycle, a thinning of the convective envelope means magnetic fields of a given strength will have a larger impact on the thermal structure of the super-adiabatic region.
-However, a restructuring of the super-adiabatic layers in a star with a thin convective envelope has less of an impact on the thermal structure of the deeper underlying layers, which are assumed to be in radiative equilibrium, than for a star whose interior is largely convective.
-The thinning of the convective envelope is also accompanied by a drop in the surface gas pressure as the star's radius inflates thereby lowering the permitted equipartition magnetic field strength.
-The combination of these two effects suggests that the transition from a magnetic sequence to a non-magnetic sequence should coincide with the disappearance of the convective envelope.} % confirm discussion of super-adiabatic layers
+{\bf In the transition region, magnetic models have masses between 1.26 $M_{\odot}$ and 1.40 $M_{\odot}$.
+Magnetic models predict that these stars have radiative core masses between 76\% and 88\% of their total stellar mass, respectively (see Figure~\ref{fig:rad_core}a).
+The 1.40 $M_{\odot}$ model is of particular note, as Figure~\ref{fig:mrd} suggests that 1.40 $M_{\odot}$ stars are beginning to enter a brief period of radius inflation that accompanies the ignition of CN-cycle burning \citep{Iben1965}.
+Photospheric gas pressures rapidly drop during this phase of evolution bringing about a rapid drop in surface equipartition magnetic field strengths.
+As expected, a rapid decrease in equipartition magnetic field strengths is observed among the data in Table~\ref{tab:equip_values} beginning around 1.40 $M_{\odot}$.
+Stars above 1.40 $M_{\odot}$ then become less sensitive to magnetic inhibition of convection because their magnetic fields are intrinsically weaker.}
 
-{\bf Assuming that a change in slope of the empirical HR diagram is observed at 4\,500 K, 
-Comparison of the empirical HR diagram to magnetic stellar models suggests that the transition's effective temperature domain begins somewhere between 4\,500~K and 5\,000~K, consistent with the knee observed in the empirical data at \teff$\sim 4\,500$~K.
-According to magnetic stellar models, these effective temperatures correspond to stars with masses between 1.26 \msun\ and 1.40 \msun.
-This is significant because stars in this mass regime are expected to have relatively thin convective envelopes that eventually disappear entirely.
-}
+%{\bf Disagreement between model predictions and the properties observed for F-type stars raises concerns about the validity of model predictions during this brief radius inflation phase.
+Possible reasons for these errors are discussed in Sect.~\ref{sec:radius}.
+If it }
 
-{\bf While this behavior is expected in the magnetic models, it does not need to necessarily correspond to the observed transition.
-General agreement between the behavior of the magnetic model isochrone and the observed stellar locus provides evidence that magnetic inhibition of convection is the mechanism responsible for the age discrepancy between the high- and low-mass stellar populations.
-However, it is clear that this statement only holds with respect to the plausible identification of a general mechanism as the models fail to reproduce the precise morphology at the magnetic sequence turn-off.}
+{\bf If the transition region begins around 4\,500~K, as one might expect from the knee in the empirical HR diagram (Fig.~\ref{fig:empirical}), a rapid decrease in surface magnetic field strengths cannot fully explain the start of the transition.
+Another mechanism must be responsible and the failure of magnetic models to reproduce the sharp transition suggests the mechanism is not accounted for in the models.}
 
-{\bf The shallower slope may be an artifact of how the empirical locus was computed.
+{\bf The sharp knee at \teff~=~4\,500~K in Fig.~\ref{fig:empirical} may be the result of a global change in magnetic field topology.
+Evidence for this comes from \citet{Gregory2012}, who noted that large-scale magnetic field topologies observed on pre-main-sequence stars appear to correlate with their predicted radiative core mass.
+Specifically, they noted a shift from predominantly dipolar axisymmetric magnetic field topologies to multi-polar non-axisymmetric field topologies when the estimated radiative core mass $M_{\rm rad.\ core} > 0.4 \star$.
+It was noted above that at \teff~=~4\,500~K, magnetic models predict a star with $M_{\star} = 1.26 M_{\odot}$ and $M_{\rm rad.\ core} \approx 0.76 M_{\star}$, well above the predicted radiative core mass where stars are expected to shift toward multi-polar non-axisymmetric field topologies.}
+
+{\bf However, \citet{Gregory2012} used non-magnetic models \citep{Siess2000} to establish a relationship between magnetic field topology and stellar interior structure.
+Hypothetically, if they were to observe a star in Upper Scorpius with \teff~=~4\,500~K, their HR diagram analysis would suggest that the star is approximately 5 Myr old.
+Figures~\ref{fig:rad_core}(a) and (b) reveal that a star with \teff~=~4\,500~K at 5 Myr is expected to have a mass of $M_{\star} = 1.10 M_{\odot}$ with $M_{\rm rad.\ core} \approx 0.43 M_{\star}$.
+This radiative core mass corresponds to 39\% of the total stellar mass and is consistent with the boundary identified by \citet{Gregory2012}.}
+
+{\bf There are several implications of this result.
+First, the sudden knee observed in Fig.~\ref{fig:empirical} may be the result of a change in magnetic field topology.
+Second, the shift in magnetic field topology from predominantly axisymmetric to non-axisymmetric may when the radiative core mass is much larger than initially suggested, $M_{\rm rad.\ core} / M_{\star} \approx 0.75$ compared to $M_{\rm rad.\ core} / M_{\star} \approx 0.40$, respectively.
+Third, pushing the transition in magnetic field topology to higher radiative core masses may provide an explanation for anomalous rotation periods observed among old main-sequence field stars \citep{vanSaders2016}.}
+
+{\bf If the large-scale magnetic field topology of pre-main-sequence stars shifts from predominantly axisymmetric to non-axisymmetric as the radiative core grows beyond 75\% of the total stellar mass, it is conceivable that the reverse is also true.
+That is, as convective envelopes grow along the sub-giant branch, large-scale magnetic fields may shift from predominantly multi-polar non-axisymmetric toward dipolar axisymmetric topologies.
+The shift in magnetic field topology may affect magnetic wind breaking mechanisms causing stars to exhibit anomalous rotation periods at older ages \citep{vanSaders2016}.
+This hypothesis may be at odds with the dependence of magnetic wind breaking mechanisms on large-scale magnetic field topologies, which suggest dipolar magnetic fields exert a greater torque on a star than multi-polar fields \citep[e.g.,][]{Reville2015}.
+However, it is unclear how the transition from a non-axisymmetric to axisymmetric magnetic field topologies affects this picture.}
+
+{\bf This discussion is premised on the reality of the apparent transition at \teff~=~4\,500~K and the demise of convective envelopes producing the shallower slope in the empirical HR diagram.
+The shallower slope may be an artifact of how the empirical locus was computed.
 The empirical HR diagram is somewhat under-populated in the immediate vicinity of \teff~$= 5\,500$~K, raising the possibility that the running median has artificially created a smooth transition between warmer and cooler stars.
@@
 
+{\bf The observed knee and shallower slope in Fig.~\ref{fig:empirical} appear to be real features.
+General agreement between the behavior of the magnetic model isochrone and the observed stellar locus provides evidence that magnetic inhibition of convection is the mechanism that is producing these effects.
+This means that magnetic fields may be responsible for the age discrepancy between the high- and low-mass stellar populations in young associations.
+However, it is clear that this statement only holds with respect to the plausible identification of a general mechanism as the models fail to reproduce the precise morphology at the magnetic sequence turn-off, perhaps because magnetic models do not account for shifts in global magnetic field topology.}
 If the age difference between warmer and cooler stars in Upper Scorpius is the result of magnetic inhibition of convection, the transition region between $5\,000 <$ \teff/K $< 6\,000$ provides an excellent laboratory for studying magnetic dynamo evolution as a function of convection zone depth and convective core size.

### 2016-04-27 paper/ref/20160427_referee_response_01.txt
Resubmitted version

Dear Editor Bertout,

I have read and given considerable thought to the comments and questions posed by the reviewer. Much time has passed since the reviewer submitted the review, a fact that reflects the attention I gave to their comments and how much their comments influenced the further development of the magnetic models. Their emphasis that the intermediate mass star population was of importance was accurate, so I felt it wise to devote significant time and energy to ensuring that this region was well modeled. I believe I achieved this aim. Ultimately, I am very grateful for their excellent review.

The reviewers reading of the manuscript and comments concerning model convergence issues prompted a more extensive study regarding the effects of magnetic fields on the properties of the intermediate mass star population. During this study, I was able to uncover the source of the model's convergence issues, allowing a larger grid of magnetic stellar evolution models to be computed. This led to some interesting results. In particular, a significant amount of time was devoted to addressing disagreements between the morphology of the HR diagram in the region where surface convective envelopes are disappearing. This more extensive investigation led to significant revisions of the discussion section to address potential physical explanations for the observed disagreements and also physical explanation for notable attributes that are in agreement (convergence of magnetic model isochrones with standard model isochrones).

All changes made to the manuscript are marked with bold text and are summarized below.

Sincerely,

Gregory Feiden

----

Summary of key changes:

- The abstract was revised for clarity and two sentences were added to reflect results from the extension of models to the intermediate mass regime.

- A paragraph in the introduction mentioning lithium depletion was removed as it wasn't necessary for providing background to the problem.

- References to David et al. (2016) were added, including a couple sentence at the end of Section 3. This work appeared after initial submission, but contains data on the same eclipsing binary that was analyzed by Kraus et al. (2015).

- Changes to the stellar evolution made to mitigate convergence issues are discussed in Section 2.

- A log(g) column was added to Table 1.

- All figures were updated to include new models and to improve clarity.

- Section 4.2 now discusses the transition region in the HR diagram that arose from my extension of the magnetic models to higher masses.

- Section 5 includes more extensive discussion of B-type stars.

- Section 5.1 was added to discuss the physics underlying the transition region observed in the HR diagram.

- Section 5.2 was created from the end of the old Section 5.1.

- Section 5.3 is presented without discussion of model convergence issues and mentions carbon/nitrogen abundances, which also play a key role in governing the brief period of radius inflation.

- I've tried to clarify the discussion of starspots vs magnetic inhibition of convection.

- More references were added to the discussion of the lithium depletion boundary.

- The summary and conclusions section was expanded.

====

I would like thank the reviewer for a careful reading of the manuscript and their astute analysis of the convergence problems. Their comments and questions motivated a more detailed study of numerical convergence for the intermediate mass star population; a study that temporarily mitigated the original problem. This resulted in an interesting comparison of the intermediate mass star population in the region of the HR diagram where surface convection zones are expected to disappear. There may be very interesting physics occurring in this region that warrant further study. Section 5 has been extended to address interesting points that arose from this investigation.

>> 1. In the introduction and in the discussion of Li depletion, it is worthwhile to mention the recent paper on the same subject by MacDonald & Mullen (2015, MNRAS, 448, 2019).

Mention of lithium depletion in the introduction has been removed since it was not the primary focus of the paper. However, we did reference MacDonald & Mullan (2015) in the discussion of lithium depletion.

>> 2. **I appreciate that the following may be difficult to accomplish given the current state of the field, so I only ask the author to comment on the following, and discuss possible directions for future study.** The equipartition argument derives the surface gas pressure from atmosphere models that neglect magnetic fields. Whereas a self-consistent treatment would be more appropriate. What is required in order for the atmosphere and interior to be treated on equal footing w.r.t. magnetic field?

It's very true that it's difficult to address this problem given the current state of the field, although there is an effort being made to relieve this uncertainty.

To treat the atmosphere and interior on equal footing with respect to the magnetic field, one must either compute a new grid of atmosphere models with magnetic fields or one must incorporate detailed frequency-dependent radiative transfer in stellar evolution models. The former is intractable, as it would require a number of new atmosphere grids that are calculated with different magnetic field strengths.

It's my opinion that the second option is more viable, although difficult in practice. Incorporating detailed radiative transfer in stellar evolution calculations effectively requires model atmospheres to be computed simultaneously with stellar interior models. This is computationally expensive, but feasible. The difficulty is related to the best way of incorporating the magnetic field, such as how the magnetic field interacts with the plasma in the stellar atmosphere. Nevertheless, if this can be achieved, then it will be possible to calculate accurate surface boundary conditions on the fly including effects due to magnetic fields.

>> 3. In Section 3 we see (Figure 1) that the magnetic isochrone does not extend to such high masses as the standard models. We have to wait until Section 5 to learn why. It would be useful to the reader to have this information up front.

Agreed, information about model limitations should be presented earlier. They are now discussed in Section 2, although in a revised context since we were able to mitigate issues that prevented models from extending to higher masses (see point 5 below).

>> 4. I also note that the different panels of Figure 1 are not labelled although they are referred to as a,b,c in the caption and text.

Panels in Figure 1 are now labeled properly.

>> 5. The issue of what happens to higher mass stars than are modelled with magnetic fields in this paper is extremely important and I would encourage the author to discuss briefly what the issues with convergence are.  This will help the reader to understand the problem and may also help others who wish to work on magnetic models in the future as to what problems they may expect to encounter.  As I read it, it seems that the problem with surface magnetic fields occurs just as we would expect the surface convection zone to disappear above 1 Msol.

An astute analysis by the reviewer. I'll first note that the issue was largely mitigated. The problems and temporary solutions are discussed in Section 2.

The principle problem was, as the reviewer noted, the disappearance of the surface convection zone. Models presented by Feiden & Chaboyer (2013) linearly scaled the width of the Gaussian perturbation with the size of the surface convection zone. This prevented models of lower mass stars from having absurdly strong magnetic fields and allowed the magnetic field to vary more slowly throughout their deep surface convection zones. Model for solar-like stars, however, had a more localized (strongly peaked) magnetic field.

Issues with numerical convergence in the first version of the paper was a consequence of the Gaussian width going to zero, causing enormous magnetic field strengths near the tachocline, which was already situated close the stellar surface. The strong radial magnetic field strength gradient prevented the models from converging. By temporarily fixing the minimum value for the Gaussian width, I've avoided these numerical issues. The precise minimum value had little to no impact on the final results.

>> 6. To quote the estimated age of the system as 9-10 Myr, rather than 9.5 /-0.5 Myr, is perhaps more appropriate to the way the age is treated in the paper. We only see models with ages 5, 10, 15 Myr and no statistical analysis is done.

This is a fair point. The estimated median age is now quoted as 9 - 10 Myr.

>> 7. The stars above which no magnetic models are available are very close to the regime where they will arrive on the main sequence (as noted in the text to begin H-burning in the core), and since such models should have no surface convection zones on the main sequence (M > 1.3 Msol), we might benefit from a more detail about why the models fail to converge. This is certainly of interest to modellers who may try to conduct similar studies.

Agreed, but as mentioned in point 5, this problem has been temporarily relieved.

>> 8. The discussion of magnetic inhibited convection vs. star spots in curious to me because I would expect that they are each a manifestation of the same underlying phenomenon, i.e., magnetic fields in the outer layers of these stars. In this sense I find that the way the two are presented as distinct effects difficult. This also get back to point #2 above in which it would be very interesting to know whether both can be included in the same models.

Yes, this is an overly nuanced discussion. The reviewer is quite correct that starspots are the manifestation of magnetic inhibition of convection. They're discussed separately in Section 5 to highlight that theoretical formulations treat them as distinct phenomena. Magnetic inhibition of convection, in a stellar model sense, has only been treated as a global phenomenon (Mullan & MacDonald; Lydon & Sofia; Feiden & Chaboyer), where as starspots explicitly account for the level of surface coverage (Chabrier et al.; Jackson & Jeffries; Somers & Pinsonneault).

One might naively assume that magnetic inhibition of convection would produce more exaggerated results, since it's a global prescription. However, if magnetic inhibition of convection can reproduce the properties of stars with realistic magnetic field strengths, it suggests that the global description of the magnetic field is not a horrible assumption. Starspots models may then require high surface coverages (approaching 100%) in order to mimic the global prescription of models with magnetic inhibition of convection.

I've tried to make this more clear in Section 5.4.

>> 9. Can the author produce an age estimate from the decay of apsidal motion in HD 144548? If so, how does it compare with the other estimates?

In short, yes, but not reliably. An initial age estimate yielded an age around 15 - 20 Myr. While this is encouraging, it should be approached with caution.

The principle difficulty in deriving an age from the apsidal motion rate for HD 144548 is that the "secondary star" in the system is itself a binary. This poses problems when considering the age dating method proposed by Feiden & Dotter (2013). Namely, defining a suitable average interior structure constant (k2) for the inner binary that adequately describes the resulting gravitational potential, and defining a single "radius" for the inner binary.

>> 10. Finally, I note one reference that may be of interest on the subject of core magnetic fields from Kepler/K2, Fuller et al. 2015 (Science, 350, 423)

Yes, the paper by Fuller et al. on suppression of gravity waves in the cores of red giants is very interesting and quite relevant in terms of providing observational support for dynamo-generated magnetic fields in the cores of intermediate mass stars. The Fuller paper and two subsequent papers by the same group are now cited to motivate future inclusion of magnetic inhibition of convection in core convection descriptions.

### 2016-04-27 paper/ms.tex
Resubmitted version

@@
 
-   \date{Version: \today; Submitted: October 21, 2015; Re-submitted: February DD, 2016.}
+   \date{Version: \today; Submitted: October 21, 2015; Re-submitted: April 27, 2016.}
 
@@
 Previous studies of this problem are confined to the theoretical HR diagram and suffer from significant uncertainties in the accuracy of inferred stellar properties.
-However, observations of Upper Scorpius by \emph{Kepler}/K2 during Campaign 2 provide accurate photometric lightcurves of eclipsing multi-star systems \citep{Kraus2015, Alonso2015, David2015b, Lodieu2015}.
+However, observations of Upper Scorpius by \emph{Kepler}/K2 during Campaign 2 provide accurate photometric lightcurves of eclipsing multi-star systems \citep{Kraus2015, Alonso2015, David2016, Lodieu2015}.
 This opens up new territory for assessing hypotheses as to the origin of the noted age discordance.
@@
 Surprisingly, the age inferred for UScoCTIO5 from the mass-radius relationship implies UScoCTIO5 is about 8 Myr old, more in line with \citet{Pecaut2012}.
-{\bf There is some disagreement about the precise values for the masses and radii of UScoCTIO5 \citep{David2015b}, but the mass-radius relationship nevertheless suggests an age of 7 -- 8 Myr}.
+{\bf There is some disagreement about the precise values for the masses and radii of UScoCTIO5 \citep{David2016}, but the mass-radius relationship nevertheless suggests an age of 7 -- 8 Myr}.
 Stellar ages are not only dependent on the effective temperature of stars used in the analysis, but on the specific properties adopted.
@@
 Assuming a distance of $145\pm15$~pc \citep{deZeeuw1999}, they estimate that $T_{{\rm eff}, A, B} = 3200\pm75$~K.
-{\bf Properties determined by \citet{David2015b} will be discussed in Sect.~\ref{sec:results}.}
+{\bf Properties determined by \citet{David2016} will be discussed in Sect.~\ref{sec:results}.}
 
@@
 
-{\bf Fundamental properties for the eclipsing binary EPIC 203710387 \citep{David2015b, Lodieu2015} are not included in the main analysis because the component masses are uncertain at the 0.02 \msun\ level.
+{\bf Fundamental properties for the eclipsing binary EPIC 203710387 \citep{David2016, Lodieu2015} are not included in the main analysis because the component masses are uncertain at the 0.02 \msun\ level.
 Discussion with respect to model predictions in light the two fundamental property determinations will be presented in Sect.~\ref{sec:disc}.}
@@
     \caption{Mass-radius diagram for stars in eclipsing systems.
-{\bf Black points are from \citet{Kraus2015} and \citet{Alonso2015}, while gray points are taken from \citet{Lodieu2015} and \citet{David2015b}.} Model predictions for magnetic and non-magnetic isochrones are the same as in Fig.~\ref{fig:ages}.}
+{\bf Black points are from \citet{Kraus2015} and \citet{Alonso2015}, while gray points are taken from \citet{Lodieu2015} and \citet{David2016}.} Model predictions for magnetic and non-magnetic isochrones are the same as in Fig.~\ref{fig:ages}.}
     \label{fig:mrd}
@@
 Although agreement is good, it is not perfect.
-{\bf Depending on whether mass and radius estimates are adopted from \citet{Kraus2015} or \citet{David2015b}, at 10 Myr the radii of the primary and secondary in UScoCTIO5 are either 3.2\% and 2.1\% (\citeauthor{Kraus2015}) larger than model predictions or 5.7\% and 6.6\% larger (\citeauthor{David2015b}).} Similarly, models at 10 Myr predict radii that are 1.4\% too large and 1.5\% too small for the Ba and Bb components of HD 144548 at 10 Myr, respectively.
+{\bf Depending on whether mass and radius estimates are adopted from \citet{Kraus2015} or \citet{David2016}, at 10 Myr the radii of the primary and secondary in UScoCTIO5 are either 3.2\% and 2.1\% (\citeauthor{Kraus2015}) larger than model predictions or 5.7\% and 6.6\% larger (\citeauthor{David2016}).} Similarly, models at 10 Myr predict radii that are 1.4\% too large and 1.5\% too small for the Ba and Bb components of HD 144548 at 10 Myr, respectively.
 An age between 9.0 and 9.5 Myr is preferred for UScoCTIO5, while 10 Myr is the best fit age for HD 144548 Ba/Bb.
@@
 Magnetic models predict that these stars have radiative core masses between 76\% and 88\% of their total stellar mass, respectively (see Figure~\ref{fig:rad_core}a).
-The 1.40 $M_{\odot}$ model is of particular note, as Figure~\ref{fig:mrd} suggests that 1.40 $M_{\odot}$ stars are beginning to enter a brief period of radius inflation that accompanies the ignition of CN-cycle burning \citep{Iben1965}.
+The 1.40 $M_{\odot}$ model is of particular note, as Figure~\ref{fig:mrd} suggests that 1.40 $M_{\odot}$ stars are entering a brief period of radius inflation that accompanies the increasing energy generation from the $p$-$p$ chain and CN-cycle burning prior to the onset of core convection \citep[e.g.,][]{Iben1965,Bodenheimer1965}.
 Photospheric gas pressures rapidly drop during this phase of evolution bringing about a rapid drop in surface equipartition magnetic field strengths.
 As expected, a rapid decrease in equipartition magnetic field strengths is observed among the data in Table~\ref{tab:equip_values} beginning around 1.40 $M_{\odot}$.
-Stars above 1.40 $M_{\odot}$ then become less sensitive to magnetic inhibition of convection because their magnetic fields are intrinsically weaker.}
+Stars above 1.40 $M_{\odot}$ become less sensitive to magnetic inhibition of convection because their magnetic fields are intrinsically weaker.}
 
@@
 {\bf If the transition region begins around 4\,500~K, as one might expect from the knee in the empirical HR diagram (Fig.~\ref{fig:empirical}), a rapid decrease in surface magnetic field strengths cannot fully explain the start of the transition.
-Another mechanism must be responsible and the failure of magnetic models to reproduce the sharp transition suggests the mechanism is not accounted for in the models.}
+Note that Fig.~\ref{fig:rad_core}(c) suggests that the difference in size between radiative cores in magnetic and standard stellar models occurs around $T_{\rm eff} \sim 4\,500$~K, suggesting there is something relatively unique occurring at that effective temperature.
+However, Fig.~\ref{fig:ages} shows no noticeable change in morphology at  $T_{\rm eff} \sim 4\,500$~K.
+Another mechanism must be responsible for the failure of magnetic models to reproduce the sharp transition.}
+%suggests the mechanism is not accounted for in the models.}
 
@@
 Evidence for this comes from \citet{Gregory2012}, who noted that large-scale magnetic field topologies observed on pre-main-sequence stars appear to correlate with their predicted radiative core mass.
-Specifically, they noted a shift from predominantly dipolar axisymmetric magnetic field topologies to multi-polar non-axisymmetric field topologies when the estimated radiative core mass $M_{\rm rad.\ core} > 0.4 \star$.
+Specifically, they noted a shift from predominantly dipolar axisymmetric magnetic field topologies to multi-polar non-axisymmetric field topologies when the estimated radiative core mass $M_{\rm rad.\ core} > 0.4 M_\star$.
 It was noted above that at \teff~=~4\,500~K, magnetic models predict a star with $M_{\star} = 1.26 M_{\odot}$ and $M_{\rm rad.\ core} \approx 0.76 M_{\star}$, well above the predicted radiative core mass where stars are expected to shift toward multi-polar non-axisymmetric field topologies.}
@@
 
-{\bf There are several implications of this result.
-First, the sudden knee observed in Fig.~\ref{fig:empirical} may be the result of a change in magnetic field topology.
-Second, the shift in magnetic field topology from predominantly axisymmetric to non-axisymmetric may when the radiative core mass is much larger than initially suggested, $M_{\rm rad.\ core} / M_{\star} \approx 0.75$ compared to $M_{\rm rad.\ core} / M_{\star} \approx 0.40$, respectively.
-Third, pushing the transition in magnetic field topology to higher radiative core masses may provide an explanation for anomalous rotation periods observed among old main-sequence field stars \citep{vanSaders2016}.}
+{\bf The implications of this results are that: (1) the knee observed in Fig.~\ref{fig:empirical} may be the result of a change in magnetic field topology and (2) the shift in magnetic field topology from a predominantly axisymmetric configuration to a non-axisymmetric configuration may occur when the radiative core mass is much larger than initially suggested.
+Magnetic models suggest the shift in global magnetic field topology occurs when $M_{\rm rad.\ core} / M_{\star} \approx 0.75$ as compared to $M_{\rm rad.\ core} / M_{\star} \approx 0.40$ \citep{Gregory2012}.}
 
-{\bf If the large-scale magnetic field topology of pre-main-sequence stars shifts from predominantly axisymmetric to non-axisymmetric as the radiative core grows beyond 75\% of the total stellar mass, it is conceivable that the reverse is also true.
+%Third, pushing the transition in magnetic field topology to higher radiative core masses may provide an explanation for anomalous rotation periods observed among old main-sequence field stars \citep{vanSaders2016}.}
+%{\bf If the large-scale magnetic field topology of pre-main-sequence stars shifts from predominantly axisymmetric to non-axisymmetric as the radiative core grows beyond 75\% of the total stellar mass, it is conceivable that the reverse is also true.
 That is, as convective envelopes grow along the sub-giant branch, large-scale magnetic fields may shift from predominantly multi-polar non-axisymmetric toward dipolar axisymmetric topologies.
@@
 However, the HR diagram is well-populated at slightly warmer and slightly cooler temperatures, suggesting the two regions must be somehow connected.
-While the precise morphology of the HR diagram in this region may be subject to alteration with additional data, the general trend of should be robust against errors in how the empirical locus is computed.}
+While the precise morphology of the HR diagram in this region may be subject to alteration with additional data, the general trend should be robust against errors in how the empirical locus is computed.}
 
@@
 This means that magnetic fields may be responsible for the age discrepancy between the high- and low-mass stellar populations in young associations.
-However, it is clear that this statement only holds with respect to the plausible identification of a general mechanism as the models fail to reproduce the precise morphology at the magnetic sequence turn-off, perhaps because magnetic models do not account for shifts in global magnetic field topology.}
-If the age difference between warmer and cooler stars in Upper Scorpius is the result of magnetic inhibition of convection, the transition region between $5\,000 <$ \teff/K $< 6\,000$ provides an excellent laboratory for studying magnetic dynamo evolution as a function of convection zone depth and convective core size.
+However, it is clear that this statement only holds with respect to the plausible identification of a general mechanism as the models fail to reproduce the precise morphology at the ``magnetic sequence turn-off.'' This is perhaps because magnetic models do not account for shifts in global magnetic field topology.}
+If the age difference between warmer and cooler stars in Upper Scorpius is the result of magnetic inhibition of convection, the transition region between $4\,500 <$ \teff/K $< 6\,000$ provides an excellent laboratory for studying magnetic dynamo evolution as a function of {\bf stellar surface convection zone properties.}
 
@@
 
-Presence of magnetic and non-magnetic sequences has implications for the (sub)stellar initial mass function of Upper Scorpius \citep{Ardila2000, Preibisch2002}.
-Not only will magnetic inhibition of convection shift mass estimates for cool stars toward higher masses, but a gradually declining magnetic field in the regime of 1.4 \msun\ should result in a paucity of stars in the 4500~K -- 5500~K temperature range.
-Standard stellar initial mass functions \citep[e.g.,][]{Salpeter1955, Kroupa2002} predict a certain number of stars at a given mass relative to other masses.
-Having a range of magnetic field strengths in stars over such a narrow mass range (0.16 \msun) will spread stars of similar mass across a wider range in temperature.
-It's not clear from \citet{Preibisch2002} whether this paucity is observed.
-However, they do note a possible excess of low-mass stars compared to field initial mass functions \citep{Scalo1998, Kroupa2002} that appears consistent with predictions from magnetic models.
-The impact of magnetic inhibition of convection on the (sub)stellar initial mass function of Upper Scorpius is reserved for future work.
+\subsection{Initial Mass Function}
+The presence of magnetic and non-magnetic sequences has implications for the (sub)stellar initial mass function of Upper Scorpius \citep{Ardila2000, Preibisch2002}.
+{\bf Section~\ref{sec:results} described how magnetic inhibition of convection predominantly shifts stars of a given mass to cooler temperatures.
+As a result, stars with a given effective temperature and luminosity have a higher mass when magnetic inhibition of convection is considered.
+Furthermore, the presence of a transition region characterized by gradually declining influence of stellar magnetic fields that links the magnetic and non-magnetic sequences will tend spread stars with similar masses across a larger effective temperature domain.
+
+For example, consider the predicted mass difference between a star with $T_{\rm eff} = $ 6\,000~K and one with $T_{\rm eff} = $ 4\,500~K.
+Non-magnetic models predict a mass difference of 0.85 \msun\ and 0.50 \msun\ at 5 Myr and 10 Myr, respectively.
+However, magnetic models suggest that the mass difference is 0.25 \msun\ at 10 Myr.
+This is at least a factor of two smaller than standard model predictions.
+
+Neglecting magnetic inhibition of convection would produce stellar mass distributions that show a paucity of stars at higher masses compared to standard predictions for field and cluster initial mass function \citep[e.g.,][]{Salpeter1955, Kroupa2002, Chabrier2003}.
+\citet{Preibisch2002} note a possible excess of low-mass stars compared to field initial mass functions \citep{Scalo1998, Kroupa2002}, but it's not immediately clear whether this potential excess of low-mass stars is fully consistent with predictions from magnetic model predictions.
+Assessing the impact of magnetic inhibition of convection on the (sub)stellar initial mass function of Upper Scorpius is reserved for future work.}
 
@@
 Stellar models show an increase in stellar radius for stars with masses in the vicinity of $M = 1.5$\msun, illustrated {\bf as a function of stellar mass and age} in Fig.\ \ref{fig:bump}.
-As described in {\bf Sect.\ \ref{sec:dynamo}}, this radius increase is due to the convective envelope responding to increased energy generation from the $p$--$p$ chain and gravitational contraction of the core.
+As described in {\bf Sect.\ \ref{sec:dynamo}}, this radius increase is due to the convective envelope responding to increased energy generation from CN cycle ignition.
 
@@
 
-{\bf HD 144548 appears to be in a fairly rapid phase of evolution given either the radius estimate from \cite{Pecaut2012} or \citet{Alonso2015}.
-This phase of evolution is sensitive to radiative opacities and nuclear reaction cross sections.
-Radiative opacities and the initial $p$-$p$ reaction cross section determine when radius inflation begins while CN-cycle reactions largely control when radius inflation ends.} It may be possible to use HD 144548 A to constrain these physics, notably nuclear reaction cross-sections for CN-cycle reactions, if the properties of HD 144548 A can be accurately constrained.
+HD 144548 appears to be in a fairly rapid phase of evolution given either the radius estimate from \cite{Pecaut2012} or \citet{Alonso2015}.
+This phase of evolution, {\bf described in Section~\ref{sec:dynamo}}, is sensitive to radiative opacities, {\bf individual abundances of carbon and nitrogen,} and nuclear reaction cross sections.
+Radiative opacities and $p$-$p$ chain reaction cross sections determine when radius inflation begins, while CN-cycle reactions largely control when radius inflation ends.
+The maximum radius reached by a star during this phase of evolution is sensitive to the adopted CN-cycle cross sections and individual abundances of carbon and nitrogen.
+Therefore, it may be possible to use HD 144548 A to constrain these physics {\bf or to constrain the C/N ratio in Upper Scorpius.
+This requires that the properties of HD 144548 A, and several other F-type stars, be accurately determined.}
+%Notably nuclear reaction cross-sections for CN-cycle reactions, if the properties of HD 144548 A can be accurately constrained.
 CN-cycle reactions eventually generate enough energy to oppose core contraction and reverse the radius increase {\bf shown in Figs.\ \ref{fig:mrd} and \ref{fig:bump} \citep[also see][]{Stassun2014}}.
-Therefore, the maximum radius reached by a star during this phase of evolution is sensitive to the adopted CN-cycle cross sections.
+Therefore, the maximum radius reached by a star during this phase of evolution is sensitive to the adopted CN-cycle cross sections and individual abundances of carbon and nitrogen.
 
@@
 Convective envelopes contain very little mass ($M_{cz} < 10^{-3} M_{\odot}$) and models indicate that, during the brief period radius inflation, magnetic and non-magnetic mass tracks tend to converge (see Fig.~\ref{fig:mrd}).} However, the exact role that magnetic fields may {\bf play} in governing the pre-main-sequence contraction of young A-, F-, and G-type stars remains relatively unexplored.
-Attempts were made to include effects from magnetic fields on these stars, but numerical issues prevented models from evolving through CN-cycle ignition.
+{\bf While magnetic fields are included in models of these stars, the equipartition magnetic field strength is fixed to the predicted value at 10 Myr.
+Stronger surface magnetic fields may exist at younger ages, which might delay contraction and lead to larger radii at a given age.
+Initial tests suggest this is likely not a significant factor in the observed radius discrepancy between models and HD 144548 A.
+}
+%Attempts were made to include effects from magnetic fields on these stars, but numerical issues prevented models from evolving through CN-cycle ignition.
 A kink in the magnetic stellar model isochrone can be seen in Fig.\ \ref{fig:mrd} around 1.53 \msun\ highlighting where magnetic perturbations were switched off.
@@
 
-The numerical issue is related to the thinning of the convection zone and the method used to specify surface boundary conditions. 
-Extrapolating from the impact of magnetic fields on lower-mass stars during the development of radiative cores, it is expected that there will be little change in the derived ages for higher mass stars, but confirmation is needed.
+%The numerical issue is related to the thinning of the convection zone and the method used to specify surface boundary conditions. 
+%Extrapolating from the impact of magnetic fields on lower-mass stars during the development of radiative cores, it is expected that there will be little change in the derived ages for higher mass stars, but confirmation is needed.
 
 Effects of strong magnetic fields on convection in stellar cores are also neglected.
-Strong magnetic fields may be generated by the interaction of a fossil field and vigorous dynamo action \citep[e.g.,][]{Featherstone2009}.
-Core magnetic fields in present models are below 1 G, which is insufficient to influence core convection.
-The impact of significantly stronger magnetic fields on core convection and the subsequent effect on the properties of higher mass stars is reserved for a future investigation.
+Strong magnetic fields may be generated by the interaction of a fossil field and vigorous dynamo action \citep[e.g.,][]{Featherstone2009}; {\bf a scenario supported by the observation of suppressed asteroseismic dipolar and quadrupolar modes in the cores of a fraction of evolved intermediate mass stars \citep{Fuller2015,Stello2016a,Cantiello2016}.} Core magnetic fields in stellar evolution models used in this work are below 1 G, which is insufficient to influence core convection.
+The impact of significantly stronger magnetic fields on core convection---especially the onset of core convection---and the subsequent effect on the properties of young intermediate mass stars is reserved for a future investigation.
 
@@
 Starspots have been suggested as an alternative mechanism to slow the contraction of young low-mass stars \citep{Jackson2009, MM10, Jackson2014a, Somers2015b}.
-The primary difference between starspots and a more general magnetic inhibition of convection is that spots are assumed to be strong localizations covering some fraction of the stellar surface whereas magnetic inhibition of convection is assumed (for simplicity) to be globally pervasive.
+{\bf Assuming starspots are analogous to sunspots, {\bf spots} can be understood to be local manifestations of convective inhibition near the optical photosphere \citep{Biermann1941,Deinzer1965}.
+In other words, the two phenomena are closely related.
+However, the primary difference between theoretical treatments starspots and a more general magnetic inhibition of convection in stellar evolution models} is that spots are assumed to be strong localizations covering some fraction of the stellar surface whereas magnetic inhibition of convection is assumed (for simplicity) to be globally pervasive.
 Starspots have qualitatively and quantitatively similar effects on stellar fundamental properties \citep[radius, \teff, luminosity;][]{Spruit1982a,Spruit1986,Somers2015b}, but differ in their impact on photometric properties.
@@
 
-Assuming starspots are analogous to sunspots, {\bf spots} can be understood to be local manifestations of convective inhibition near the optical photosphere \citep{Biermann1941,Deinzer1965}.
-The agreement between ages and stellar fundamental properties predicted by magnetic stellar evolution isochrones presented in this work with ages of higher mass stars in Upper Scorpius may indicate that a global inhibition of convection accurately captures relevant physics involved in halting contraction of low-mass stars.
-If starspots are also to be considered, one should find that young stars in Upper Scorpius have a high coverage fraction of spots ($f \sim 1$).
+Agreement between ages and stellar fundamental properties of low-mass stars predicted by magnetic stellar evolution isochrones presented in this work with ages of higher mass stars in Upper Scorpius may indicate that a global inhibition of convection accurately captures relevant physics involved in halting contraction of low-mass stars.
+If starspots are also to be considered, one might expect to find that young stars in Upper Scorpius have a high coverage fraction of spots ($f \sim 1$).
 In this limit, a global inhibition of convection and spotted models \citep[e.g.,][]{Somers2015b} should provide equivalent explanations for observed HR and mass-radius diagram discrepancies.
@@
 If spots have a small areal coverage, it is more likely that they will have a negligible impact on stellar structure as compared to global inhibition of convection from the more ubiquitous non-zero background magnetic field.
-
-\begin{figure}[t]
-    \includegraphics[width=0.85\linewidth]{Li7_USco_Beq.eps}
-    \caption{Lithium abundance  as a function of effective temperature at 10 Myr.
-Predictions are shown from standard (light-blue dashed line) and magnetic (yellow solid line) stellar evolution isochrones.
-Models were computed using the setup described in Sect.~\ref{sec:models}.
-Lithium abundance is defined as $A(\,^7{\rm Li}) = \log_{10}(N_{\rm Li}/N_{\rm H}) + 12$.}
-    \label{fig:lithium}
-\end{figure}
 
@@
 
+\begin{figure}[t]
+    \includegraphics[width=0.85\linewidth]{Li7_USco_Beq.eps}
+    \caption{Lithium abundance  as a function of effective temperature at 10 Myr.
+Predictions are shown from standard (light-blue dashed line) and magnetic (yellow solid line) stellar evolution isochrones.
+Models were computed using the setup described in Sect.~\ref{sec:models}.
+Lithium abundance is defined as $A(\,^7{\rm Li}) = \log_{10}(N_{\rm Li}/N_{\rm H}) + 12$.}
+    \label{fig:lithium}
+\end{figure}
+
 \section{Summary \& Conclusions}
@@
 Stellar evolution models and literature data are used to {\bf estimate} median ages for stars with spectral types A through M in Upper Scorpius.
-I find a median HR diagram age of {\bf 9 -- 10} Myr for A-, F-, and G-type stars, with the exception of a population of F-type stars that appear 5 Myr older.
-These results agree with the revised $11\pm3$ Myr {\bf proposed by} \citet{Pecaut2012}.
-At the same time, I confirm the HR diagram age of 4 -- 5 Myr for K- and M-type stars using standard stellar evolution isochrones \citep{Preibisch2012, Slesnick2008, Herczeg2015}.
-{\bf Notably}, isochronal ages of K- and M-type stars in eclipsing multiple-star systems observed by \emph{Kepler}/K2 \citep{Kraus2015, Alonso2015, David2015b} disagree with the HR diagram analysis and suggest ages between 6 and 8 Myr for the same stars.
+A median HR diagram age of {\bf 9 -- 10} Myr is found for A-, F-, and G-type stars, with the exception of a population of F-type stars that appear roughly 4 -- 5 Myr older.
+These results agree with the revised $11\pm3$ Myr age {\bf proposed by} \citet{Pecaut2012}.
+At the same time, an HR diagram age of 4 -- 5 Myr is confirmed for K- and M-type stars using standard stellar evolution isochrones \citep{Preibisch2012, Slesnick2008, Herczeg2015}.
+{\bf Notably}, isochronal ages of K- and M-type stars in eclipsing multiple-star systems observed by \emph{Kepler}/K2 \citep{Kraus2015, Alonso2015, David2016} disagree with the HR diagram analysis and suggest ages between 6 and 8 Myr for the same stars.
 
-Using stellar evolution models {\bf that account} for magnetic inhibition of convection \citep{FC12b, FC13}, {\bf I find} an age of {\bf 9 -- 10} Myr for K- and M-type stars in Upper Scorpius.
+Using stellar evolution models {\bf that account} for magnetic inhibition of convection \citep{FC12b, FC13}, an age of {\bf 9 -- 10} Myr is found for K- and M-type stars in Upper Scorpius.
 Magnetic inhibition of convection consistently explains:
 \begin{enumerate} 
-	\item the age discrepancy between high- and low-mass stars in the HR diagram,
+	\item the age discrepancy between high- and low-mass stars in the HR diagram \citep{Herczeg2015},
 	\item the observed slope of the low-mass stellar mass-radius relationship,
-	\item stellar age differences observed between HR diagram and mass-radius relationship determinations,
+	\item stellar age differences observed between HR diagram and mass-radius relationship determinations \citep{Kraus2015},
 	\item and the lithium depletion pattern inferred from observed lithium equivalent widths \citep{Rizzuto2015}. 

### 2016-04-27 paper/arXiv/ms.tex
arXiv version (no bf commands)

--- 2016-04-27 paper/ms.tex
@@
 %-----------------------------------------------------------------------
-%
-%\documentclass[referee]{aa} % for a referee version
-%\documentclass[onecolumn]{aa} % for a paper on 1 column  
-%\documentclass[longauth]{aa} % for the long lists of affiliations 
-%\documentclass[rnote]{aa} % for the research notes
-%\documentclass[letter]{aa} % for the letters 
-%\documentclass[bibyear]{aa} % if the references are not structured 
-% according to the author-year natbib style
 %
@@
 \hypersetup{
-	bookmarks=true,
     pdftitle={A Consistent 10 Myr Age for the Upper Scorpius OB Association},          % set pdf title          
@@
 Cooler (K, M) stars typically yield ages that are systematically younger than warmer (A, F, G) stars by a factor of two.
-I explore the possibility that {\bf these age discrepancies are} the {\bf result} of magnetic inhibition of convection in young cool stars {\bf by using magnetic stellar evolution isochrones to determine the age of the Upper Scorpius subgroup of the Scorpius-Centaurus OB Association.} A median age of 10 Myr consistent across spectral types A through M is found, except for a subset of F-type stars that appear significantly older.
-Agreement is shown for ages derived from the Hertzsprung-Russell diagram and {\bf from} the empirical mass-radius relationship defined by eclipsing multiple-star systems.
-Surface magnetic field strengths required to produce agreement are {\bf of order 2.5 kG} and are predicted from \emph{a priori} estimates of equipartition values.
-{\bf A region in the HR diagram is identified that plausibly connects stars whose structures are weakly influenced by the presence of magnetic fields with those whose structures are strongly influenced by magnetic fields.
-The models suggest this region is characterized by stars with rapidly thinning outer convective envelopes where the radiative core mass is greater than 80\% of the total stellar mass.} Furthermore, depletion of lithium predicted from magnetic models appears in better agreement with observed lithium equivalent widths than predictions from non-magnetic models.
+I explore the possibility that these age discrepancies are the result of magnetic inhibition of convection in young cool stars by using magnetic stellar evolution isochrones to determine the age of the Upper Scorpius subgroup of the Scorpius-Centaurus OB Association.
+A median age of 10 Myr consistent across spectral types A through M is found, except for a subset of F-type stars that appear significantly older.
+Agreement is shown for ages derived from the Hertzsprung-Russell diagram and from the empirical mass-radius relationship defined by eclipsing multiple-star systems.
+Surface magnetic field strengths required to produce agreement are of order 2.5 kG and are predicted from \emph{a priori} estimates of equipartition values.
+A region in the HR diagram is identified that plausibly connects stars whose structures are weakly influenced by the presence of magnetic fields with those whose structures are strongly influenced by magnetic fields.
+The models suggest this region is characterized by stars with rapidly thinning outer convective envelopes where the radiative core mass is greater than 80\% of the total stellar mass.
+Furthermore, depletion of lithium predicted from magnetic models appears in better agreement with observed lithium equivalent widths than predictions from non-magnetic models.
 These results suggest that magnetic inhibition of convection plays an important role in the early evolution of low-mass stars and that it may be responsible for noted age discrepancies in young stellar populations.}
@@
 \section{Introduction}
-The \object{Upper Scorpius} subgroup of the larger Scorpius-Centaurus OB association is estimated to have a median age {\bf between 5 and 11 Myr.} Prior to 2012, there was a broad consensus that Upper Scorpius is roughly 5 Myr old based on age determinations from stellar evolution models \citep{deGeus1992, Preibisch2002, Slesnick2008}.
+The \object{Upper Scorpius} subgroup of the larger Scorpius-Centaurus OB association is estimated to have a median age between 5 and 11 Myr.
+Prior to 2012, there was a broad consensus that Upper Scorpius is roughly 5 Myr old based on age determinations from stellar evolution models \citep{deGeus1992, Preibisch2002, Slesnick2008}.
 Crucially, \citet{Preibisch2002} showed that this age was consistent across the entire theoretical Hertzsprung-Russell (HR) diagram.
@@
 
-%This paper focuses on the latter following evidence that introduction of magnetic fields in stellar models can slow the contraction of young, low-mass stars \citep[e.g.,][]{MM10, Malo2014}.
-%% Add paragraph of background with D'Antona+; Malo+; MM10/15;
-
 While other young stellar populations exhibit an age gradient as a function of effective temperature, Upper Scorpius poses a particularly interesting hurdle.
@@
 Surprisingly, the age inferred for UScoCTIO5 from the mass-radius relationship implies UScoCTIO5 is about 8 Myr old, more in line with \citet{Pecaut2012}.
-{\bf There is some disagreement about the precise values for the masses and radii of UScoCTIO5 \citep{David2016}, but the mass-radius relationship nevertheless suggests an age of 7 -- 8 Myr}.
+There is some disagreement about the precise values for the masses and radii of UScoCTIO5 \citep{David2016}, but the mass-radius relationship nevertheless suggests an age of 7 -- 8 Myr.
 Stellar ages are not only dependent on the effective temperature of stars used in the analysis, but on the specific properties adopted.
@@
 
-Here, I test the hypothesis that magnetic fields may inhibit convection in low-mass pre-main-sequence stars {\bf slowing their contraction along the Hayashi track.
-Slower contraction times for low-mass stars} would give them larger radii at a given age, pushing inferred ages to older values \citep[e.g.,][]{MM10, Malo2014}.
+Here, I test the hypothesis that magnetic fields may inhibit convection in low-mass pre-main-sequence stars slowing their contraction along the Hayashi track.
+Slower contraction times for low-mass stars would give them larger radii at a given age, pushing inferred ages to older values \citep[e.g.,][]{MM10, Malo2014}.
 In Sect.~\ref{sec:models}, I describe the model setup and method used to predict stellar surface magnetic field strengths \emph{a priori}.
@@
 Effects related to the interaction of magnetic fields and convection, as well as magnetic fields on the plasma equation of state, are included as described by \citet{FC12b,FC13}.
-{\bf Radial magnetic field strength profiles are prescribed using a ``Gaussian magnetic field strength profile'' of the form
+Radial magnetic field strength profiles are prescribed using a ``Gaussian magnetic field strength profile'' of the form
 \begin{equation}
@@
 where $R_{\rm src}$ is the location of the inner convection zone boundary in fractional radii and $\sigma_g$ defines the width of the Gaussian \citep{FC13}.
-The adopted radial magnetic field strength profile has a negligible impact on the results provided the peak magnetic energy density remains small compared to the thermal energy density \citep{FC13,FC14,FC14b}.}
+The adopted radial magnetic field strength profile has a negligible impact on the results provided the peak magnetic energy density remains small compared to the thermal energy density \citep{FC13,FC14,FC14b}.
 Peak interior magnetic field strengths are defined at $R_{\rm src} = 0.5\ R_{\star}$ for fully convective models and at the maximum of $R_{\rm src} = 0.5\ R_{\star}$ and $R_{\rm src} = R_{\rm bcz}$ (convection zone boundary) for partially convective stars.
@@
 
-{\bf The width of the Gaussian controls the magnitude of the peak magnetic field strength at the inner convection zone boundary. It was defined by \citet{FC13} as
+The width of the Gaussian controls the magnitude of the peak magnetic field strength at the inner convection zone boundary. It was defined by \citet{FC13} as
 \begin{equation}
@@
 Models with initial masses above about 1.15~\msun\ are prevented from evolving through the final approach to the zero-age-main-sequence because of this problem.
-To mitigate the problem, a lower limit of $\sigma_g = 0.05$ is enforced.}
+To mitigate the problem, a lower limit of $\sigma_g = 0.05$ is enforced.
 
@@
 
-% support with evidence from the literature? perhaps in discussion section?
 The interior magnetic field strength profile requires a surface boundary condition: the average surface magnetic field strength $\langle{\rm B}f\rangle$.
@@
 Since surface gas pressures are dependent on \logg\ and \teff, equipartition magnetic field strengths evolve toward greater values for stars undergoing quasi-hydrostatic contraction.
-This assumption breaks down for stars with masses above 1.55 $M_{\odot}$, whose outer convection zones disappear within {\bf about} 10 Myr.
+This assumption breaks down for stars with masses above 1.55 $M_{\odot}$, whose outer convection zones disappear within about 10 Myr.
 
-Magnetic field effects are switched on {\bf between the ages of 0.1 and 0.5 Myr years}, perturbing an initial zero-magnetic-field-strength model.
-The precise age at which the magnetic field is switched on has no impact on the results \citep{FC12b}, provided there is {\bf a} buffer between the perturbation age and ages under investigation (here, ages greater than 1 Myr).
+Magnetic field effects are switched on between the ages of 0.1 and 0.5 Myr years, perturbing an initial zero-magnetic-field-strength model.
+The precise age at which the magnetic field is switched on has no impact on the results \citep{FC12b}, provided there is a buffer between the perturbation age and ages under investigation (here, ages greater than 1 Myr).
 This buffer allows models to relax to a stable configuration after the perturbation.
 Typical peak magnetic field strengths in the models are of order 50 kG for models with $\langle Bf \rangle_{\rm eq,\,surf} \sim 2.5$~kG.
-{\bf Conversely, magnetic field effects are turned off during a model computation once the outer convective envelope disappears. This eventually occurs for stars with $M \gtrsim 1.15 M_{\odot}$.}
+Conversely, magnetic field effects are turned off during a model computation once the outer convective envelope disappears.
+This eventually occurs for stars with $M \gtrsim 1.15 M_{\odot}$.
 
@@
 In this way, modifications to convection are only introduced through the addition of magnetic perturbations.
-Solar-calibrated values are determined by finding a combination of $Y_0$, $Z_0$, and $\amlt$ that reproduce the solar radius, luminosity, and surface $\left(Z/X\right)$ at the solar age for a model of 1.0 \msun\ {\bf without a magnetic perturbation.} Adopted solar quantities are given in Table~\ref{tab:solar}.
+Solar-calibrated values are determined by finding a combination of $Y_0$, $Z_0$, and $\amlt$ that reproduce the solar radius, luminosity, and surface $\left(Z/X\right)$ at the solar age for a model of 1.0 \msun\ without a magnetic perturbation.
+Adopted solar quantities are given in Table~\ref{tab:solar}.
 Final calibration parameters are $Y_0 = 0.2755$, $Z_0 = 0.01876$, and $\amlt = 1.884$.
@@
 A moving median of logarithmic luminosities as a function of $\log$(\teff) was performed by subdividing the temperature domain into 85 bins of equal width $\Delta\log$(\teff)$ = 0.025$~dex.
-{\bf This width ensured at least five stars were in each bin across the full temperature domain.} Bins with fewer than three stars were rejected.
+This width ensured at least five stars were in each bin across the full temperature domain.
+Bins with fewer than three stars were rejected.
 A median $\logLsun$\ value was estimated for each bin by finding the 50th percentile from the cumulative distribution of median values computed from a total of 10\,000 bootstrap samples.
-For each bootstrap sample, {\bf the $\log$(\teff) and $\logLsun$\ value for each data point} was randomly perturbed by drawing values from a normal distribution centered on the measured value with a standard deviation {\bf equal to} the quoted error.
-{\bf Thus}, points were allowed to scatter in and out of neighboring bins {\bf according} to their measured uncertainty.
-Points without uncertainties were assigned an {\bf optimistic uncertainty of 0.015~dex} in both $\logLsun$\ and $\log$(\teff).
+For each bootstrap sample, the $\log$(\teff) and $\logLsun$\ value for each data point was randomly perturbed by drawing values from a normal distribution centered on the measured value with a standard deviation equal to the quoted error.
+Thus, points were allowed to scatter in and out of neighboring bins according to their measured uncertainty.
+Points without uncertainties were assigned an optimistic uncertainty of 0.015~dex in both $\logLsun$\ and $\log$(\teff).
 Different values for the number of bins, bin widths, and number of bootstrap samples were tested and found to not significantly impact the resulting median stellar locus.
-{\bf The resulting median locus and corresponding 99\% confidence interval for the median value are shown in Figure~\ref{fig:empirical}.}
+The resulting median locus and corresponding 99\% confidence interval for the median value are shown in Figure~\ref{fig:empirical}.
 
@@
 Assuming a distance of $145\pm15$~pc \citep{deZeeuw1999}, they estimate that $T_{{\rm eff}, A, B} = 3200\pm75$~K.
-{\bf Properties determined by \citet{David2016} will be discussed in Sect.~\ref{sec:results}.}
+Properties determined by \citet{David2016} will be discussed in Sect.~\ref{sec:results}.
 
@@
 
-{\bf Fundamental properties for the eclipsing binary EPIC 203710387 \citep{David2016, Lodieu2015} are not included in the main analysis because the component masses are uncertain at the 0.02 \msun\ level.
-Discussion with respect to model predictions in light the two fundamental property determinations will be presented in Sect.~\ref{sec:disc}.}
+Fundamental properties for the eclipsing binary EPIC 203710387 \citep{David2016, Lodieu2015} are not included in the main analysis because the component masses are uncertain at the 0.02 \msun\ level.
+Discussion with respect to model predictions in light the two fundamental property determinations will be presented in Sect.~\ref{sec:disc}.
 
@@
     \includegraphics[width=0.43\linewidth]{HR_diagram_split_USco.eps}
-    \caption{{\bf (a) Comparison of theoretical Hertzsprung-Russell (HR) diagram predictions to the observational locus of Upper Scorpius.
+    \caption{(a) Comparison of theoretical Hertzsprung-Russell (HR) diagram predictions to the observational locus of Upper Scorpius.
 The median empirical locus calculated in Section~\ref{sec:data} is shown by the light gray shaded region.
@@
 (b) Zoom-in on the high-mass region of the HR diagram.
-(c) Zoom-in on the low-mass region.}}
+(c) Zoom-in on the low-mass region.}
     \label{fig:ages}
@@
 An HR diagram for Upper Scorpius is shown in Fig.~\ref{fig:ages}a.
-Empirical data is represented by the median stellar locus ({\bf light-gray shaded region}) and against three standard stellar evolution isochrones with ages of 5, 10, and 15 Myr ({\bf black dashed lines}).
-Focusing on {\bf temperature regimes corresponding} A-, F-, and G-type stars {\bf ($5\,750 <$ \teff/K $< 10\,000$)}, standard stellar isochrones predict ages between 5 and 15 Myr, with a median age estimate of approximately 10 Myr.
-%A median age of roughly 10 Myr is confirmed by comparison of the median stellar locus with stellar model isochrones.
+Empirical data is represented by the median stellar locus (light-gray shaded region) and against three standard stellar evolution isochrones with ages of 5, 10, and 15 Myr (black dashed lines).
+Focusing on temperature regimes corresponding A-, F-, and G-type stars ($5\,750 <$ \teff/K $< 10\,000$), standard stellar isochrones predict ages between 5 and 15 Myr, with a median age estimate of approximately 10 Myr.
 
@@
 M-type stars with \teff\ $\lesssim 4\,000$~K suggest an age of 5 Myr is appropriate.
-The empirical stellar locus plotted in Figs.~\ref{fig:ages}a and \ref{fig:ages}c {\bf encompasses a 5 Myr standard stellar model isochrone in the M-star sequence down to \teff\ $\sim3\,100$ K.
-Disagreement at the lowest temperatures is likely due to a bias in the computation of the empirical stellar locus caused by a steepening of the HR diagram (see Figure~\ref{fig:empirical}).}
+The empirical stellar locus plotted in Figs.~\ref{fig:ages}a and \ref{fig:ages}c encompasses a 5 Myr standard stellar model isochrone in the M-star sequence down to \teff\ $\sim3\,100$ K.
+Disagreement at the lowest temperatures is likely due to a bias in the computation of the empirical stellar locus caused by a steepening of the HR diagram (see Figure~\ref{fig:empirical}).
 
@@
 The age of HD 144548 from the Ba/Bb components is suggested to be around 5.5 Myr according to standard stellar evolution isochrones.
-While an age of 5.5 Myr agrees with quoted ages for the K- and M-type stars, it is in tension with the {\bf 10 Myr} age for component A from the HR diagram.
+While an age of 5.5 Myr agrees with quoted ages for the K- and M-type stars, it is in tension with the 10 Myr age for component A from the HR diagram.
 Curiously, HD 144548 A lies significantly above the model mass-radius relation.
@@
 HD 144548 appears younger in the mass-radius plane than it does in the HR diagram by roughly a factor of two.
-In contrast, UScoCTIO5 appears older in the mass-radius plane than it does in the HR diagram---also by {\bf about} a factor of two.
+In contrast, UScoCTIO5 appears older in the mass-radius plane than it does in the HR diagram---also by about a factor of two.
 Slopes of the theoretical \teff-luminosity and mass-radius relationships must be altered in different directions to produce an overall agreement.
@@
 A 10 Myr magnetic isochrone naturally explains the factor of two age difference observed between high- and low-mass stars, provided the high-mass stars are not appreciably affected by additional non-standard physics (e.g., rotation).
-Figures~\ref{fig:ages}a and \ref{fig:ages}c (HR diagrams) {\bf show that a 10 Myr isochrone computed with equipartition magnetic fields} is shifted toward cooler temperatures and higher luminosities compared to a 10 Myr non-magnetic isochrone.
-Inhibition of convection by magnetic fields {\bf cools the stellar surface temperature thereby slowing} the contraction rate of young stars.
+Figures~\ref{fig:ages}a and \ref{fig:ages}c (HR diagrams) show that a 10 Myr isochrone computed with equipartition magnetic fields is shifted toward cooler temperatures and higher luminosities compared to a 10 Myr non-magnetic isochrone.
+Inhibition of convection by magnetic fields cools the stellar surface temperature thereby slowing the contraction rate of young stars.
 Stars have a larger radius and a higher luminosity at a given age, as a result.
-The combination of cooler surface temperatures and higher luminosities {\bf makes} a 10 Myr magnetic isochrone look nearly identical to a 5 Myr non-magnetic isochrone for {\bf stars with} effective temperatures {\bf below about 5\,000~K.
-The magnetic stellar model isochrone lies on top of the 5 Myr standard model isochrone in Figs.~\ref{fig:ages}a and \ref{fig:ages}c and entirely within} the empirical stellar locus for low-mass stars in Upper Scorpius.
+The combination of cooler surface temperatures and higher luminosities makes a 10 Myr magnetic isochrone look nearly identical to a 5 Myr non-magnetic isochrone for stars with effective temperatures below about 5\,000~K.
+The magnetic stellar model isochrone lies on top of the 5 Myr standard model isochrone in Figs.~\ref{fig:ages}a and \ref{fig:ages}c and entirely within the empirical stellar locus for low-mass stars in Upper Scorpius.
 
-{\bf The magnetic model isochrone also correctly converges toward the 10 Myr standard model isochrone at warmer effective temperatures.
+The magnetic model isochrone also correctly converges toward the 10 Myr standard model isochrone at warmer effective temperatures.
 To some degree, this  convergence reproduces an observed transition in the empirical HR diagram where the age inferred from standard model isochrones shifts from 5 Myr to 10 Myr.
@@
 This is more clearly seen in Fig.~\ref{fig:empirical}, where the empirical median stellar locus exhibits a knee around \teff $\sim 4\,500$~K that roughly corresponds to the beginning of the transition region in Fig.~\ref{fig:ages}a.
-A distinct knee feature is absent from the magnetic model isochrone.}
-
-%In magnetic model space, this temperature domain corresponds to masses between $1.40$ and $1.56$ \msun.
-Inspection of Fig.~\ref{fig:mrd} reveals this mass range corresponds precisely to where the rapid thinning of the convection zone occurs, as expected.}
+A distinct knee feature is absent from the magnetic model isochrone.
 
@@
     \caption{Mass-radius diagram for stars in eclipsing systems.
-{\bf Black points are from \citet{Kraus2015} and \citet{Alonso2015}, while gray points are taken from \citet{Lodieu2015} and \citet{David2016}.} Model predictions for magnetic and non-magnetic isochrones are the same as in Fig.~\ref{fig:ages}.}
+Black points are from \citet{Kraus2015} and \citet{Alonso2015}, while gray points are taken from \citet{Lodieu2015} and \citet{David2016}.
+Model predictions for magnetic and non-magnetic isochrones are the same as in Fig.~\ref{fig:ages}.}
     \label{fig:mrd}
@@
 Although agreement is good, it is not perfect.
-{\bf Depending on whether mass and radius estimates are adopted from \citet{Kraus2015} or \citet{David2016}, at 10 Myr the radii of the primary and secondary in UScoCTIO5 are either 3.2\% and 2.1\% (\citeauthor{Kraus2015}) larger than model predictions or 5.7\% and 6.6\% larger (\citeauthor{David2016}).} Similarly, models at 10 Myr predict radii that are 1.4\% too large and 1.5\% too small for the Ba and Bb components of HD 144548 at 10 Myr, respectively.
+Depending on whether mass and radius estimates are adopted from \citet{Kraus2015} or \citet{David2016}, at 10 Myr the radii of the primary and secondary in UScoCTIO5 are either 3.2\% and 2.1\% (\citeauthor{Kraus2015}) larger than model predictions or 5.7\% and 6.6\% larger (\citeauthor{David2016}).
+Similarly, models at 10 Myr predict radii that are 1.4\% too large and 1.5\% too small for the Ba and Bb components of HD 144548 at 10 Myr, respectively.
 An age between 9.0 and 9.5 Myr is preferred for UScoCTIO5, while 10 Myr is the best fit age for HD 144548 Ba/Bb.
 
-This age spread could be indicative of an intrinsic age spread, but it is also possible {\bf to attribute this spread to errors in the mass and radius determinations of the eclipsing binary systems or to the fact} that the low-mass stars in UScoCTIO5 may require marginally stronger magnetic field strengths than are predicted from equipartition arguments.
+This age spread could be indicative of an intrinsic age spread, but it is also possible to attribute this spread to errors in the mass and radius determinations of the eclipsing binary systems or to the fact that the low-mass stars in UScoCTIO5 may require marginally stronger magnetic field strengths than are predicted from equipartition arguments.
 Nevertheless, it is encouraging that models provide this level of agreement with an age and surface magnetic field strengths determined \emph{a priori}.
@@
 \label{sec:disc}
-An age of {\bf 9 -- 10} Myr gives broad agreement across the HR and mass-radius diagrams.
-No stellar population in Upper Scorpius {\bf studied here robustly} supports the possibility that the median age of the association is 5 Myr.
+An age of 9 -- 10 Myr gives broad agreement across the HR and mass-radius diagrams.
+No stellar population in Upper Scorpius studied here robustly supports the possibility that the median age of the association is 5 Myr.
 There are, however, still age discrepancies that must be addressed.
 As noted above, the median age for F-type stars appears to be a few million years older than stars of other spectral types.
-This {\bf discrepancy} is {\bf perplexing and deserves further investigation}, especially considering that potential missing physics in the models would likely conspire to make F-stars older, not younger.
+This discrepancy is perplexing and deserves further investigation, especially considering that potential missing physics in the models would likely conspire to make F-stars older, not younger.
 It should be noted that most F-type stars in Upper Scorpius are at a stage of evolution where models predict radii increase and subsequently decrease over a period of roughly 4 -- 8 Myr.
-{\bf The timescale for this process is} similar to the observed age discrepancy (see Fig.~\ref{fig:bump} in Sect.~\ref{sec:radius}) and may be indicative of potential shortcomings in existing model physics such as radiative opacities or nuclear reaction cross-sections.
+The timescale for this process is similar to the observed age discrepancy (see Fig.~\ref{fig:bump} in Sect.~\ref{sec:radius}) and may be indicative of potential shortcomings in existing model physics such as radiative opacities or nuclear reaction cross-sections.
 
-{\bf Age discrepancies also exist with two B-type members of Upper Scorpius: \object{$\tau$ Sco} and \object{$\omega$ Sco}.
+Age discrepancies also exist with two B-type members of Upper Scorpius: \object{$\tau$ Sco} and \object{$\omega$ Sco}.
 They exhibit ages between 2 and 5 Myr depending on whether rotation is accounted for in stellar evolution models \citep{Pecaut2012}.
@@
 However, that scenario requires that the low-mass stars form almost exclusively in a later star formation episode than the higher mass population.
-Although we cannot definitively rule out this scenario, we find it unlikely and maintain that the {\bf median} age for the low-mass stars is too young compared to the rest of the stellar population in the absence of magnetic inhibition of convection.}
+Although we cannot definitively rule out this scenario, we find it unlikely and maintain that the median age for the low-mass stars is too young compared to the rest of the stellar population in the absence of magnetic inhibition of convection.
 
@@
 \label{sec:dynamo}
-% F --> G type members are bright (V < 10 mag) and could be accessible to ZDI. Perhaps we'd see changes in magnetic strengths or topologies stretching from late-G to late-F.
-
-{\bf Figure~\ref{fig:ages} shows that a 10 Myr magnetic model isochrone agrees with predictions from a 5 Myr standard model isochrone for effective temperatures below about 5\,000~K, but traces a 10 Myr standard model isochrone above 6\,000~K.
+Figure~\ref{fig:ages} shows that a 10 Myr magnetic model isochrone agrees with predictions from a 5 Myr standard model isochrone for effective temperatures below about 5\,000~K, but traces a 10 Myr standard model isochrone above 6\,000~K.
 This suggests that magnetic inhibition of convection plays an important role in dictating the structure of cool low-mass stars, but the structure of warmer high-mass stars is relatively insensitive to the influence of magnetic fields.
 In between these two regimes, models predict a transition in which stars appear to exhibit a decreasing sensitivity to magnetic inhibition of convection as effective temperature increases.
-}
 
-{\bf As was noted in Sect.~\ref{sec:results}, Figs.~\ref{fig:empirical} and \ref{fig:ages}a indicate that a similar transition occurs over roughly the same effective temperature domain in the empirical HR diagram of Upper Scorpius.
+As was noted in Sect.~\ref{sec:results}, Figs.~\ref{fig:empirical} and \ref{fig:ages}a indicate that a similar transition occurs over roughly the same effective temperature domain in the empirical HR diagram of Upper Scorpius.
 Early- to mid-G stars in Upper Scorpius (\teff$ \sim 6\,000$~K) are best described by a 10 Myr standard stellar model isochrone.
@@
 That the shallower slope in the empirical HR diagram and the transition predicted by magnetic stellar models are coincident, suggests that the two phenomena may be connected.
-}
 
@@
 
-{\bf The transition exhibited by theoretical magnetic models can be explained by a rapid thinning of outer convective envelopes in stars with masses above about 1.2 $M_{\odot}$ \citep[e.g.,][]{Iben1965}.
+The transition exhibited by theoretical magnetic models can be explained by a rapid thinning of outer convective envelopes in stars with masses above about 1.2 $M_{\odot}$ \citep[e.g.,][]{Iben1965}.
 Once a star reaches an effective temperature of 6\,000 K, it has a very small or non-existent convective envelope, as shown in Fig.~\ref{fig:rad_core}(b).
@@
 This provides a natural explanation for the convergence of the 10 Myr magnetic and standard model isochrones that occurs near this effective temperature in Fig.~\ref{fig:ages}(b).
-It then seems reasonable to posit that the shallow slope of the empirical HR diagram and the observed transition in the magnetic models trace the demise of outer convective envelopes and the growth of radiative cores in young, pre-main-sequence stars.}
+It then seems reasonable to posit that the shallow slope of the empirical HR diagram and the observed transition in the magnetic models trace the demise of outer convective envelopes and the growth of radiative cores in young, pre-main-sequence stars.
 
-{\bf While the demise of outer convection zones explains the final convergence of magnetic and standard models, it doesn't necessarily explain the beginning of the transition between  4\,500~K and 5\,000~K.
-Figures~\ref{fig:ages}(a) and \ref{fig:rad_core}(b) indicate that stars with \teff~<~4\,500~K can possess radiative cores that comprise up to about 75\% of the star, by mass.}
-
-{\bf In the transition region, magnetic models have masses between 1.26 $M_{\odot}$ and 1.40 $M_{\odot}$.
+While the demise of outer convection zones explains the final convergence of magnetic and standard models, it doesn't necessarily explain the beginning of the transition that occurs between $T_{\rm eff} = $4\,500~K and 5\,000~K.
+In the transition region, magnetic models have masses between 1.26 $M_{\odot}$ ($T_{\rm eff} = $ 4\,500~K) and 1.40 $M_{\odot}$ ($T_{\rm eff} = $5\,000~K).
 Magnetic models predict that these stars have radiative core masses between 76\% and 88\% of their total stellar mass, respectively (see Figure~\ref{fig:rad_core}a).
@@
 As expected, a rapid decrease in equipartition magnetic field strengths is observed among the data in Table~\ref{tab:equip_values} beginning around 1.40 $M_{\odot}$.
-Stars above 1.40 $M_{\odot}$ become less sensitive to magnetic inhibition of convection because their magnetic fields are intrinsically weaker.}
+Stars above 1.40 $M_{\odot}$ become less sensitive to magnetic inhibition of convection because their magnetic fields are intrinsically weaker.
 
-%{\bf Disagreement between model predictions and the properties observed for F-type stars raises concerns about the validity of model predictions during this brief radius inflation phase.
-Possible reasons for these errors are discussed in Sect.~\ref{sec:radius}.
-If it }
-
-{\bf If the transition region begins around 4\,500~K, as one might expect from the knee in the empirical HR diagram (Fig.~\ref{fig:empirical}), a rapid decrease in surface magnetic field strengths cannot fully explain the start of the transition.
+If the transition region begins around 4\,500~K, as one might expect from the knee in the empirical HR diagram (Fig.~\ref{fig:empirical}), a rapid decrease in surface magnetic field strengths cannot fully explain the start of the transition.
 Note that Fig.~\ref{fig:rad_core}(c) suggests that the difference in size between radiative cores in magnetic and standard stellar models occurs around $T_{\rm eff} \sim 4\,500$~K, suggesting there is something relatively unique occurring at that effective temperature.
 However, Fig.~\ref{fig:ages} shows no noticeable change in morphology at  $T_{\rm eff} \sim 4\,500$~K.
-Another mechanism must be responsible for the failure of magnetic models to reproduce the sharp transition.}
-%suggests the mechanism is not accounted for in the models.}
+Another mechanism must be responsible for the failure of magnetic models to reproduce the sharp transition.
 
-{\bf The sharp knee at \teff~=~4\,500~K in Fig.~\ref{fig:empirical} may be the result of a global change in magnetic field topology.
+The sharp knee at \teff~=~4\,500~K in Fig.~\ref{fig:empirical} may be the result of a global change in magnetic field topology.
 Evidence for this comes from \citet{Gregory2012}, who noted that large-scale magnetic field topologies observed on pre-main-sequence stars appear to correlate with their predicted radiative core mass.
 Specifically, they noted a shift from predominantly dipolar axisymmetric magnetic field topologies to multi-polar non-axisymmetric field topologies when the estimated radiative core mass $M_{\rm rad.\ core} > 0.4 M_\star$.
-It was noted above that at \teff~=~4\,500~K, magnetic models predict a star with $M_{\star} = 1.26 M_{\odot}$ and $M_{\rm rad.\ core} \approx 0.76 M_{\star}$, well above the predicted radiative core mass where stars are expected to shift toward multi-polar non-axisymmetric field topologies.}
+It was noted above that at \teff~=~4\,500~K, magnetic models predict a star with $M_{\star} = 1.26 M_{\odot}$ and $M_{\rm rad.\ core} \approx 0.76 M_{\star}$, well above the predicted radiative core mass where stars are expected to shift toward multi-polar non-axisymmetric field topologies.
 
-{\bf However, \citet{Gregory2012} used non-magnetic models \citep{Siess2000} to establish a relationship between magnetic field topology and stellar interior structure.
+However, \citet{Gregory2012} used non-magnetic models \citep{Siess2000} to establish a relationship between magnetic field topology and stellar interior structure.
 Hypothetically, if they were to observe a star in Upper Scorpius with \teff~=~4\,500~K, their HR diagram analysis would suggest that the star is approximately 5 Myr old.
 Figures~\ref{fig:rad_core}(a) and (b) reveal that a star with \teff~=~4\,500~K at 5 Myr is expected to have a mass of $M_{\star} = 1.10 M_{\odot}$ with $M_{\rm rad.\ core} \approx 0.43 M_{\star}$.
-This radiative core mass corresponds to 39\% of the total stellar mass and is consistent with the boundary identified by \citet{Gregory2012}.}
+This radiative core mass corresponds to 39\% of the total stellar mass and is consistent with the boundary identified by \citet{Gregory2012}.
 
-{\bf The implications of this results are that: (1) the knee observed in Fig.~\ref{fig:empirical} may be the result of a change in magnetic field topology and (2) the shift in magnetic field topology from a predominantly axisymmetric configuration to a non-axisymmetric configuration may occur when the radiative core mass is much larger than initially suggested.
-Magnetic models suggest the shift in global magnetic field topology occurs when $M_{\rm rad.\ core} / M_{\star} \approx 0.75$ as compared to $M_{\rm rad.\ core} / M_{\star} \approx 0.40$ \citep{Gregory2012}.}
+The implications of this results are that: (1) the knee observed in Fig.~\ref{fig:empirical} may be the result of a change in magnetic field topology and (2) the shift in magnetic field topology from a predominantly axisymmetric configuration to a non-axisymmetric configuration may occur when the radiative core mass is much larger than initially suggested.
+Magnetic models suggest the shift in global magnetic field topology occurs when $M_{\rm rad.\ core} / M_{\star} \approx 0.75$ as compared to $M_{\rm rad.\ core} / M_{\star} \approx 0.40$ \citep{Gregory2012}.
 
-%Third, pushing the transition in magnetic field topology to higher radiative core masses may provide an explanation for anomalous rotation periods observed among old main-sequence field stars \citep{vanSaders2016}.}
-%{\bf If the large-scale magnetic field topology of pre-main-sequence stars shifts from predominantly axisymmetric to non-axisymmetric as the radiative core grows beyond 75\% of the total stellar mass, it is conceivable that the reverse is also true.
-That is, as convective envelopes grow along the sub-giant branch, large-scale magnetic fields may shift from predominantly multi-polar non-axisymmetric toward dipolar axisymmetric topologies.
-The shift in magnetic field topology may affect magnetic wind breaking mechanisms causing stars to exhibit anomalous rotation periods at older ages \citep{vanSaders2016}.
-This hypothesis may be at odds with the dependence of magnetic wind breaking mechanisms on large-scale magnetic field topologies, which suggest dipolar magnetic fields exert a greater torque on a star than multi-polar fields \citep[e.g.,][]{Reville2015}.
-However, it is unclear how the transition from a non-axisymmetric to axisymmetric magnetic field topologies affects this picture.}
-
-{\bf This discussion is premised on the reality of the apparent transition at \teff~=~4\,500~K and the demise of convective envelopes producing the shallower slope in the empirical HR diagram.
+This discussion is premised on the reality of the apparent transition at \teff~=~4\,500~K and the demise of convective envelopes producing the shallower slope in the empirical HR diagram.
 The shallower slope may be an artifact of how the empirical locus was computed.
@@
 However, the HR diagram is well-populated at slightly warmer and slightly cooler temperatures, suggesting the two regions must be somehow connected.
-While the precise morphology of the HR diagram in this region may be subject to alteration with additional data, the general trend should be robust against errors in how the empirical locus is computed.}
+While the precise morphology of the HR diagram in this region may be subject to alteration with additional data, the general trend should be robust against errors in how the empirical locus is computed.
 
-{\bf Errors transforming from photometric colors or spectral types to effective temperatures may provide a plausible explanation for the shallower slope of the HR diagram in the vicinity of 5\,000~K.
+Errors transforming from photometric colors or spectral types to effective temperatures may provide a plausible explanation for the shallower slope of the HR diagram in the vicinity of 5\,000~K.
 Below this temperature, stellar atmospheric opacity becomes increasingly dominated by molecular species, particularly TiO in the optical and H$_2$O in the infrared, which poses problems when attempting to derive a robust effective temperature scale.
@@
 Agreement between empirical methods and theoretical predictions is reassuring.
-However,
-comparing these results to the 5 -- 30 Myr pre-main-sequence star temperature scale proposed by \citet{Pecaut2013}, one finds that the temperature scale adopted by \citeauthor{Preibisch1999} is about 100~K cooler for early K-type stars, but the two temperature scales agree around spectral type M0.
+However, comparing these results to the 5 -- 30 Myr pre-main-sequence star temperature scale proposed by \citet{Pecaut2013}, one finds that the temperature scale adopted by \citeauthor{Preibisch1999} is about 100~K cooler for early K-type stars, but the two temperature scales agree around spectral type M0.
 For early-to-late M-type stars, \citeauthor{Preibisch1999} find temperatures about 100~K warmer than \citet{Pecaut2013}, a reversal from the comparison for late-K-type stars.
 Considering these differences, the sharp knee feature in the HR diagram may be accentuated by the adoption of an erroneous temperature scale, but it does not appear sufficient to fully explain the shallower slope observed in the HR diagram.
-}
 
-{\bf The observed knee and shallower slope in Fig.~\ref{fig:empirical} appear to be real features.
+The observed knee and shallower slope in Fig.~\ref{fig:empirical} appear to be real features.
 General agreement between the behavior of the magnetic model isochrone and the observed stellar locus provides evidence that magnetic inhibition of convection is the mechanism that is producing these effects.
 This means that magnetic fields may be responsible for the age discrepancy between the high- and low-mass stellar populations in young associations.
-However, it is clear that this statement only holds with respect to the plausible identification of a general mechanism as the models fail to reproduce the precise morphology at the ``magnetic sequence turn-off.'' This is perhaps because magnetic models do not account for shifts in global magnetic field topology.}
-If the age difference between warmer and cooler stars in Upper Scorpius is the result of magnetic inhibition of convection, the transition region between $4\,500 <$ \teff/K $< 6\,000$ provides an excellent laboratory for studying magnetic dynamo evolution as a function of {\bf stellar surface convection zone properties.}
-
-%If this is the case, it may help explain the significant gap between the end of the magnetic stellar evolution isochrone and the location of HD 144548 A in the HR diagram.
-The mass difference is only $0.16\pm0.04$ \msun, but the temperature difference is nearly 1600~K.
-By contrast, the expected difference is 500~K from standard models.
-It's interesting to note that the end of the magnetic 10 Myr isochrone is where stars are expected to begin a brief period of radius inflation prior to ignition of the CN cycle (see below).
-This is shown in Fig.~\ref{fig:bump}.
-Radius inflation occurs over a 3 -- 4 Myr timespan and may result in a gradual decrease of the magnetic field strength throughout the stellar envelope due to a roughly 30\% decrease in the envelope's angular velocity.
-The latter is due to an increase in the envelope's moment of inertia and may weaken magnetic dynamo processes.
-One might then expect a gradual reduction in the importance of magnetic inhibition of convection, creating a situation where stars in a narrow mass range span a relatively large range in effective temperature, resulting in the gap seen in Fig.~\ref{fig:ages}a.
+However, it is clear that this statement only holds with respect to the plausible identification of a general mechanism as the models fail to reproduce the precise morphology at the ``magnetic sequence turn-off.'' This is perhaps because magnetic models do not account for shifts in global magnetic field topology.
+If the age difference between warmer and cooler stars in Upper Scorpius is the result of magnetic inhibition of convection, the transition region between $4\,500 <$ \teff/K $< 6\,000$ provides an excellent laboratory for studying magnetic dynamo evolution as a function of stellar surface convection zone properties.
 
@@
 The presence of magnetic and non-magnetic sequences has implications for the (sub)stellar initial mass function of Upper Scorpius \citep{Ardila2000, Preibisch2002}.
-{\bf Section~\ref{sec:results} described how magnetic inhibition of convection predominantly shifts stars of a given mass to cooler temperatures.
+Section~\ref{sec:results} described how magnetic inhibition of convection predominantly shifts stars of a given mass to cooler temperatures.
 As a result, stars with a given effective temperature and luminosity have a higher mass when magnetic inhibition of convection is considered.
@@
 \citet{Preibisch2002} note a possible excess of low-mass stars compared to field initial mass functions \citep{Scalo1998, Kroupa2002}, but it's not immediately clear whether this potential excess of low-mass stars is fully consistent with predictions from magnetic model predictions.
-Assessing the impact of magnetic inhibition of convection on the (sub)stellar initial mass function of Upper Scorpius is reserved for future work.}
-
-%\begin{figure}[t]
-%    \centering
-%    \includegraphics[width=0.95\linewidth]{radiative_core_mass_difference.eps}
-%    \caption{Difference in radiative core mass between magnetic and standard stellar evolution models as a function of effective temperature.
-The difference is shown as the radiative core mass of a magnetic model minus the radiative core mass of a standard stellar model at the same effective temperature, ($M_{\rm rad.\ core,\, mag} - M_{\rm rad.\ core,\, std}$).}
-%    \label{fig:delta_mass}
-%\end{figure}
+Assessing the impact of magnetic inhibition of convection on the (sub)stellar initial mass function of Upper Scorpius is reserved for future work.
 
@@
 This is formally consistent with the radius derived by \citep{Alonso2015}, but the mean value is more consistent with estimates from stellar evolution isochrones around 10 Myr.
-Stellar models show an increase in stellar radius for stars with masses in the vicinity of $M = 1.5$\msun, illustrated {\bf as a function of stellar mass and age} in Fig.\ \ref{fig:bump}.
-As described in {\bf Sect.\ \ref{sec:dynamo}}, this radius increase is due to the convective envelope responding to increased energy generation from CN cycle ignition.
+Stellar models show an increase in stellar radius for stars with masses in the vicinity of $M = 1.5$\msun, illustrated as a function of stellar mass and age in Fig.\ \ref{fig:bump}.
+As described in Sect.\ \ref{sec:dynamo}, this radius increase is due to the convective envelope responding to increased energy generation from CN cycle ignition.
 
@@
 HD 144548 appears to be in a fairly rapid phase of evolution given either the radius estimate from \cite{Pecaut2012} or \citet{Alonso2015}.
-This phase of evolution, {\bf described in Section~\ref{sec:dynamo}}, is sensitive to radiative opacities, {\bf individual abundances of carbon and nitrogen,} and nuclear reaction cross sections.
+This phase of evolution, described in Section~\ref{sec:dynamo}, is sensitive to radiative opacities, individual abundances of carbon and nitrogen, and nuclear reaction cross sections.
 Radiative opacities and $p$-$p$ chain reaction cross sections determine when radius inflation begins, while CN-cycle reactions largely control when radius inflation ends.
 The maximum radius reached by a star during this phase of evolution is sensitive to the adopted CN-cycle cross sections and individual abundances of carbon and nitrogen.
-Therefore, it may be possible to use HD 144548 A to constrain these physics {\bf or to constrain the C/N ratio in Upper Scorpius.
-This requires that the properties of HD 144548 A, and several other F-type stars, be accurately determined.}
-%Notably nuclear reaction cross-sections for CN-cycle reactions, if the properties of HD 144548 A can be accurately constrained.
-CN-cycle reactions eventually generate enough energy to oppose core contraction and reverse the radius increase {\bf shown in Figs.\ \ref{fig:mrd} and \ref{fig:bump} \citep[also see][]{Stassun2014}}.
-Therefore, the maximum radius reached by a star during this phase of evolution is sensitive to the adopted CN-cycle cross sections and individual abundances of carbon and nitrogen.
+Therefore, it may be possible to use HD 144548 A to constrain these physics or to constrain the C/N ratio in Upper Scorpius.
+This requires that the properties of HD 144548 A, and several other F-type stars, be accurately determined.
 
 Perhaps there are other physics missing for HD 144548 A that result in the radius discrepancy.
-Magnetic inhibition of convection {\bf does not appear to play a significant role in governing the radius at this phase of evolution.
-Convective envelopes contain very little mass ($M_{cz} < 10^{-3} M_{\odot}$) and models indicate that, during the brief period radius inflation, magnetic and non-magnetic mass tracks tend to converge (see Fig.~\ref{fig:mrd}).} However, the exact role that magnetic fields may {\bf play} in governing the pre-main-sequence contraction of young A-, F-, and G-type stars remains relatively unexplored.
-{\bf While magnetic fields are included in models of these stars, the equipartition magnetic field strength is fixed to the predicted value at 10 Myr.
+Magnetic inhibition of convection does not appear to play a significant role in governing the radius at this phase of evolution.
+Convective envelopes contain very little mass ($M_{cz} < 10^{-3} M_{\odot}$) and models indicate that, during the brief period radius inflation, magnetic and non-magnetic mass tracks tend to converge (see Fig.~\ref{fig:mrd}).
+However, the exact role that magnetic fields may play in governing the pre-main-sequence contraction of young A-, F-, and G-type stars remains relatively unexplored.
+While magnetic fields are included in models of these stars, the equipartition magnetic field strength is fixed to the predicted value at 10 Myr.
 Stronger surface magnetic fields may exist at younger ages, which might delay contraction and lead to larger radii at a given age.
 Initial tests suggest this is likely not a significant factor in the observed radius discrepancy between models and HD 144548 A.
-}
-%Attempts were made to include effects from magnetic fields on these stars, but numerical issues prevented models from evolving through CN-cycle ignition.
-A kink in the magnetic stellar model isochrone can be seen in Fig.\ \ref{fig:mrd} around 1.53 \msun\ highlighting where magnetic perturbations were switched off.
-This occurs before CN-cycle ignition is reached.
-
-%The numerical issue is related to the thinning of the convection zone and the method used to specify surface boundary conditions. 
-%Extrapolating from the impact of magnetic fields on lower-mass stars during the development of radiative cores, it is expected that there will be little change in the derived ages for higher mass stars, but confirmation is needed.
 
 Effects of strong magnetic fields on convection in stellar cores are also neglected.
-Strong magnetic fields may be generated by the interaction of a fossil field and vigorous dynamo action \citep[e.g.,][]{Featherstone2009}; {\bf a scenario supported by the observation of suppressed asteroseismic dipolar and quadrupolar modes in the cores of a fraction of evolved intermediate mass stars \citep{Fuller2015,Stello2016a,Cantiello2016}.} Core magnetic fields in stellar evolution models used in this work are below 1 G, which is insufficient to influence core convection.
+Strong magnetic fields may be generated by the interaction of a fossil field and vigorous dynamo action \citep[e.g.,][]{Featherstone2009}; a scenario supported by the observation of suppressed asteroseismic dipolar and quadrupolar modes in the cores of a fraction of evolved intermediate mass stars \citep{Fuller2015,Stello2016a,Cantiello2016}.
+Core magnetic fields in stellar evolution models used in this work are below 1 G, which is insufficient to influence core convection.
 The impact of significantly stronger magnetic fields on core convection---especially the onset of core convection---and the subsequent effect on the properties of young intermediate mass stars is reserved for a future investigation.
@@
 Starspots have been suggested as an alternative mechanism to slow the contraction of young low-mass stars \citep{Jackson2009, MM10, Jackson2014a, Somers2015b}.
-{\bf Assuming starspots are analogous to sunspots, {\bf spots} can be understood to be local manifestations of convective inhibition near the optical photosphere \citep{Biermann1941,Deinzer1965}.
+Assuming starspots are analogous to sunspots, spots can be understood to be local manifestations of convective inhibition near the optical photosphere \citep{Biermann1941,Deinzer1965}.
 In other words, the two phenomena are closely related.
-However, the primary difference between theoretical treatments starspots and a more general magnetic inhibition of convection in stellar evolution models} is that spots are assumed to be strong localizations covering some fraction of the stellar surface whereas magnetic inhibition of convection is assumed (for simplicity) to be globally pervasive.
+However, the primary difference between theoretical treatments starspots and a more general magnetic inhibition of convection in stellar evolution models is that spots are assumed to be strong localizations covering some fraction of the stellar surface whereas magnetic inhibition of convection is assumed (for simplicity) to be globally pervasive.
 Starspots have qualitatively and quantitatively similar effects on stellar fundamental properties \citep[radius, \teff, luminosity;][]{Spruit1982a,Spruit1986,Somers2015b}, but differ in their impact on photometric properties.
@@
 \subsection{Lithium Depletion}
-An approach to validating magnetic stellar models is the determination of lithium abundances {\bf \citep{MacDonald2015},} or observation of lithium equivalent widths.
-{\bf Magnetic inhibition of convection produces a cooler temperature structure in fully convective pre-main-sequence stars, thereby delaying lithium burning and preserving lithium to older ages \citep{Ventura1998, DAntona2000, MM10, FC13, Malo2014, MacDonald2015}.
+An approach to validating magnetic stellar models is the determination of lithium abundances \citep{MacDonald2015}, or observation of lithium equivalent widths.
+Magnetic inhibition of convection produces a cooler temperature structure in fully convective pre-main-sequence stars, thereby delaying lithium burning and preserving lithium to older ages \citep{Ventura1998, DAntona2000, MM10, FC13, Malo2014, MacDonald2015}.
 Starspots have a similar affect on lithium burning timescales \citep{Jackson2014b, Somers2015b}, which is perhaps not surprising given the deep connection between starspots and magnetic inhibition of convection \citep{Biermann1941, Deinzer1965}.
-Nevertheless, if magnetic fields are directly influencing the structure of young stars, they should leave an imprint on the observed lithium abundance distribution in young stellar populations.}
+Nevertheless, if magnetic fields are directly influencing the structure of young stars, they should leave an imprint on the observed lithium abundance distribution in young stellar populations.
 
@@
 \label{sec:tellit}
-Stellar evolution models and literature data are used to {\bf estimate} median ages for stars with spectral types A through M in Upper Scorpius.
-A median HR diagram age of {\bf 9 -- 10} Myr is found for A-, F-, and G-type stars, with the exception of a population of F-type stars that appear roughly 4 -- 5 Myr older.
-These results agree with the revised $11\pm3$ Myr age {\bf proposed by} \citet{Pecaut2012}.
+Stellar evolution models and literature data are used to estimate median ages for stars with spectral types A through M in Upper Scorpius.
+A median HR diagram age of 9 -- 10 Myr is found for A-, F-, and G-type stars, with the exception of a population of F-type stars that appear roughly 4 -- 5 Myr older.
+These results agree with the revised $11\pm3$ Myr age proposed by \citet{Pecaut2012}.
 At the same time, an HR diagram age of 4 -- 5 Myr is confirmed for K- and M-type stars using standard stellar evolution isochrones \citep{Preibisch2012, Slesnick2008, Herczeg2015}.
-{\bf Notably}, isochronal ages of K- and M-type stars in eclipsing multiple-star systems observed by \emph{Kepler}/K2 \citep{Kraus2015, Alonso2015, David2016} disagree with the HR diagram analysis and suggest ages between 6 and 8 Myr for the same stars.
+Notably, isochronal ages of K- and M-type stars in eclipsing multiple-star systems observed by \emph{Kepler}/K2 \citep{Kraus2015, Alonso2015, David2016} disagree with the HR diagram analysis and suggest ages between 6 and 8 Myr for the same stars.
 
-Using stellar evolution models {\bf that account} for magnetic inhibition of convection \citep{FC12b, FC13}, an age of {\bf 9 -- 10} Myr is found for K- and M-type stars in Upper Scorpius.
+Using stellar evolution models that account for magnetic inhibition of convection \citep{FC12b, FC13}, an age of 9 -- 10 Myr is found for K- and M-type stars in Upper Scorpius.
 Magnetic inhibition of convection consistently explains:
@@
 There is no population of stars in the Upper Scorpius that unambiguously supports an age of 5 Myr.
-{\bf Nevertheless, additional eclipsing binary systems are needed to better populate the mass-radius relationship to solidify Upper Scorpius as a 10 Myr old stellar association and to verify predictions from magnetic stellar evolution models across the full mass spectrum.}
+Nevertheless, additional eclipsing binary systems are needed to better populate the mass-radius relationship to solidify Upper Scorpius as a 10 Myr old stellar association and to verify predictions from magnetic stellar evolution models across the full mass spectrum.
 
-{\bf Further work is needed to explore whether magnetic inhibition of convection serves as a robust solution for noted age gradients as a function of stellar spectral type \citep[e.g.,][]{Naylor2009, Herczeg2015}.
+Further work is needed to explore whether magnetic inhibition of convection serves as a robust solution for noted age gradients as a function of stellar spectral type \citep[e.g.,][]{Naylor2009, Herczeg2015}.
 Previous work determining ages for the $\beta$-Pictoris moving group from magnetic stellar models suggests the solution is robust \citep{MM10, Malo2014, Binks2016}, but additional confirmation using stellar populations with a wider variety of ages is required.
-These results also highlight the need to explore how the inclusion of magnetic inhibition of convection affects the (sub)stellar initial mass function for young stellar populations.}
+These results also highlight the need to explore how the inclusion of magnetic inhibition of convection affects the (sub)stellar initial mass function for young stellar populations.
 
-{\bf In the meantime, the use of magnetic stellar models as a component for isochrone analyses for young low-mass stars is recommended.
+In the meantime, the use of magnetic stellar models as a component for isochrone analyses for young low-mass stars is recommended.
 Consistency across the HR and mass-radius diagrams exhibited by magnetic stellar evolution isochrones suggest that magnetic isochrones will provide a more accurate characterization of transiting exoplanet host stars in young stellar populations, especially those observed by \emph{Kepler}/K2 in Upper Scorpius.
@@
 To facilitate their adoption, all models used in this study are available online\footnote{\url{https://github.com/gfeiden/MagneticUpperSco/}}.
-A small grid of solar-metallicity magnetic stellar mass tracks and isochrones is also under construction, as is a web-interface to compute custom magnetic models.}
+A small grid of solar-metallicity magnetic stellar mass tracks and isochrones is also under construction, as is a web-interface to compute custom magnetic models.
 
@@
 
-\bibliography{papers.bib}
+\begin{thebibliography}{71}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Allard} {et~al.}(2011){Allard}, {Homeier}, \&
+  {Freytag}}]{Allard2011}
+{Allard}, F., {Homeier}, D., \& {Freytag}, B. 2011, in Astronomical Society of
+  the Pacific Conference Series, Vol. 448, 16th Cambridge Workshop on Cool
+  Stars, Stellar Systems, and the Sun, ed. C.~{Johns-Krull}, M.~K. {Browning},
+  \& A.~A. {West}, 91
+
+\bibitem[{{Alonso} {et~al.}(2015){Alonso}, {Deeg}, {Hoyer}, {Lodieu}, {Palle},
+  \& {Sanchis-Ojeda}}]{Alonso2015}
+{Alonso}, R., {Deeg}, H.~J., {Hoyer}, S., {et~al.} 2015, \aap, 584, L8
+
+\bibitem[{{Andersen}(1991)}]{Andersen1991}
+{Andersen}, J. 1991, \aapr, 3, 91
+
+\bibitem[{{Ardila} {et~al.}(2000){Ardila}, {Mart{\'{\i}}n}, \&
+  {Basri}}]{Ardila2000}
+{Ardila}, D., {Mart{\'{\i}}n}, E., \& {Basri}, G. 2000, \aj, 120, 479
+
+\bibitem[{{Bahcall} {et~al.}(2005){Bahcall}, {Serenelli}, \&
+  {Basu}}]{Bahcall2005}
+{Bahcall}, J.~N., {Serenelli}, A.~M., \& {Basu}, S. 2005, \apj, 621, L85
+
+\bibitem[{{Baraffe} {et~al.}(2003){Baraffe}, {Chabrier}, {Barman}, {Allard}, \&
+  {Hauschildt}}]{Baraffe2003}
+{Baraffe}, I., {Chabrier}, G., {Barman}, T.~S., {Allard}, F., \& {Hauschildt},
+  P.~H. 2003, \aap, 402, 701
+
+\bibitem[{{Basu}(1998)}]{Basu1998}
+{Basu}, S. 1998, \mnras, 298, 719
+
+\bibitem[{{Basu} \& {Antia}(1997)}]{Basu1997}
+{Basu}, S. \& {Antia}, H.~M. 1997, \mnras, 287, 189
+
+\bibitem[{{Basu} \& {Antia}(2004)}]{Basu2004}
+{Basu}, S. \& {Antia}, H.~M. 2004, \apjl, 606, L85
+
+\bibitem[{{Bell} {et~al.}(2012){Bell}, {Naylor}, {Mayne}, {Jeffries}, \&
+  {Littlefair}}]{Bell2012}
+{Bell}, C.~P.~M., {Naylor}, T., {Mayne}, N.~J., {Jeffries}, R.~D., \&
+  {Littlefair}, S.~P. 2012, \mnras, 424, 3178
+
+\bibitem[{{Bell} {et~al.}(2013){Bell}, {Naylor}, {Mayne}, {Jeffries}, \&
+  {Littlefair}}]{Bell2013}
+{Bell}, C.~P.~M., {Naylor}, T., {Mayne}, N.~J., {Jeffries}, R.~D., \&
+  {Littlefair}, S.~P. 2013, \mnras, 434, 806
+
+\bibitem[{{Biermann}(1941)}]{Biermann1941}
+{Biermann}, L. 1941, Vierteljahresschrift der Astronomischen Gesellschaft, 76,
+  194
+
+\bibitem[{{Binks} \& {Jeffries}(2016)}]{Binks2016}
+{Binks}, A.~S. \& {Jeffries}, R.~D. 2016, \mnras, 455, 3345
+
+\bibitem[{{Bodenheimer} {et~al.}(1965){Bodenheimer}, {Forbes}, {Gould}, \&
+  {Henyey}}]{Bodenheimer1965}
+{Bodenheimer}, P., {Forbes}, J.~E., {Gould}, N.~L., \& {Henyey}, L.~G. 1965,
+  \apj, 141, 1019
+
+\bibitem[{Cantiello {et~al.}(2016)Cantiello, Fuller, \&
+  Bildsten}]{Cantiello2016}
+Cantiello, M., Fuller, J., \& Bildsten, L. 2016, arXiv: 1602.03056
+
+\bibitem[{{Chabrier}(2003)}]{Chabrier2003}
+{Chabrier}, G. 2003, \pasp, 115, 763
+
+\bibitem[{{D'Antona} {et~al.}(2000){D'Antona}, {Ventura}, \&
+  {Mazzitelli}}]{DAntona2000}
+{D'Antona}, F., {Ventura}, P., \& {Mazzitelli}, I. 2000, \apj, 543, L77
+
+\bibitem[{{David} {et~al.}(2016){David}, {Hillenbrand}, {Cody}, {Carpenter}, \&
+  {Howard}}]{David2016}
+{David}, T.~J., {Hillenbrand}, L.~A., {Cody}, A.~M., {Carpenter}, J.~M., \&
+  {Howard}, A.~W. 2016, \apj, 816, 21
+
+\bibitem[{{de Geus}(1992)}]{deGeus1992}
+{de Geus}, E.~J. 1992, \aap, 262, 258
+
+\bibitem[{{de Jager} \& {Nieuwenhuijzen}(1987)}]{deJager1987}
+{de Jager}, C. \& {Nieuwenhuijzen}, H. 1987, \aap, 177, 217
+
+\bibitem[{{de Zeeuw} {et~al.}(1999){de Zeeuw}, {Hoogerwerf}, {de Bruijne},
+  {Brown}, \& {Blaauw}}]{deZeeuw1999}
+{de Zeeuw}, P.~T., {Hoogerwerf}, R., {de Bruijne}, J.~H.~J., {Brown}, A.~G.~A.,
+  \& {Blaauw}, A. 1999, \aj, 117, 354
+
+\bibitem[{{Deinzer}(1965)}]{Deinzer1965}
+{Deinzer}, W. 1965, \apj, 141, 548
+
+\bibitem[{Dotter {et~al.}(2008)Dotter, Chaboyer, Jevremovi\'{c}, Kostov, Baron,
+  \& Ferguson}]{Dotter2008}
+Dotter, A., Chaboyer, B., Jevremovi\'{c}, D., {et~al.} 2008, \apjs, 178, 89
+
+\bibitem[{{Featherstone} {et~al.}(2009){Featherstone}, {Browning}, {Brun}, \&
+  {Toomre}}]{Featherstone2009}
+{Featherstone}, N.~A., {Browning}, M.~K., {Brun}, A.~S., \& {Toomre}, J. 2009,
+  \apj, 705, 1000
+
+\bibitem[{{Feiden} \& {Chaboyer}(2012)}]{FC12b}
+{Feiden}, G.~A. \& {Chaboyer}, B. 2012, \apj, 761, 30
+
+\bibitem[{{Feiden} \& {Chaboyer}(2013)}]{FC13}
+{Feiden}, G.~A. \& {Chaboyer}, B. 2013, \apj, 779, 183
+
+\bibitem[{{Feiden} \& {Chaboyer}(2014{\natexlab{a}})}]{FC14}
+{Feiden}, G.~A. \& {Chaboyer}, B. 2014{\natexlab{a}}, \apj, 786, 53
+
+\bibitem[{{Feiden} \& {Chaboyer}(2014{\natexlab{b}})}]{FC14b}
+{Feiden}, G.~A. \& {Chaboyer}, B. 2014{\natexlab{b}}, \aap, 571, A70
+
+\bibitem[{{Feiden} \& {Dotter}(2013)}]{FD13}
+{Feiden}, G.~A. \& {Dotter}, A. 2013, \apj, 765, 86
+
+\bibitem[{{Ferguson} {et~al.}(2005){Ferguson}, {Alexander}, {Allard}, {Barman},
+  {Bodnarik}, {Hauschildt}, {Heffner-Wong}, \& {Tamanai}}]{Ferguson2005}
+{Ferguson}, J.~W., {Alexander}, D.~R., {Allard}, F., {et~al.} 2005, \apj, 623,
+  585
+
+\bibitem[{Fuller {et~al.}(2015)Fuller, Cantiello, Stello, Garcia, \&
+  Bildsten}]{Fuller2015}
+Fuller, J., Cantiello, M., Stello, D., Garcia, R.~A., \& Bildsten, L. 2015,
+  Science, 350, 423
+
+\bibitem[{{Gregory} {et~al.}(2012){Gregory}, {Donati}, {Morin}, {Hussain},
+  {Mayne}, {Hillenbrand}, \& {Jardine}}]{Gregory2012}
+{Gregory}, S.~G., {Donati}, J.-F., {Morin}, J., {et~al.} 2012, \apj, 755, 97
+
+\bibitem[{{Grevesse} \& {Sauval}(1998)}]{GS98}
+{Grevesse}, N. \& {Sauval}, A.~J. 1998, \ssr, 85, 161
+
+\bibitem[{{Hauschildt} {et~al.}(1999{\natexlab{a}}){Hauschildt}, {Allard}, \&
+  {Baron}}]{Hauschildt1999a}
+{Hauschildt}, P.~H., {Allard}, F., \& {Baron}, E. 1999{\natexlab{a}}, \apj,
+  512, 377
+
+\bibitem[{{Hauschildt} {et~al.}(1999{\natexlab{b}}){Hauschildt}, {Allard},
+  {Ferguson}, {Baron}, \& {Alexander}}]{Hauschildt1999b}
+{Hauschildt}, P.~H., {Allard}, F., {Ferguson}, J., {Baron}, E., \& {Alexander},
+  D.~R. 1999{\natexlab{b}}, \apj, 525, 871
+
+\bibitem[{{Herczeg} \& {Hillenbrand}(2015)}]{Herczeg2015}
+{Herczeg}, G.~J. \& {Hillenbrand}, L.~A. 2015, \apj, 808, 23
+
+\bibitem[{{Hillenbrand} {et~al.}(2008){Hillenbrand}, {Bauermeister}, \&
+  {White}}]{Hillenbrand2008}
+{Hillenbrand}, L.~A., {Bauermeister}, A., \& {White}, R.~J. 2008, in
+  Astronomical Society of the Pacific Conference Series, Vol. 384, 14th
+  Cambridge Workshop on Cool Stars, Stellar Systems, and the Sun, ed. G.~{van
+  Belle}, 200
+
+\bibitem[{{Iben}(1965)}]{Iben1965}
+{Iben}, Jr., I. 1965, \apj, 141, 993
+
+\bibitem[{{Jackson} \& {Jeffries}(2014{\natexlab{a}})}]{Jackson2014b}
+{Jackson}, R.~J. \& {Jeffries}, R.~D. 2014{\natexlab{a}}, \mnras, 445, 4306
+
+\bibitem[{{Jackson} \& {Jeffries}(2014{\natexlab{b}})}]{Jackson2014a}
+{Jackson}, R.~J. \& {Jeffries}, R.~D. 2014{\natexlab{b}}, \mnras, 441, 2111
+
+\bibitem[{{Jackson} {et~al.}(2009){Jackson}, {Jeffries}, \&
+  {Maxted}}]{Jackson2009}
+{Jackson}, R.~J., {Jeffries}, R.~D., \& {Maxted}, P.~F.~L. 2009, \mnras, 339,
+  L89
+
+\bibitem[{{Kraus} {et~al.}(2015){Kraus}, {Cody}, {Covey}, {Rizzuto}, {Mann}, \&
+  {Ireland}}]{Kraus2015}
+{Kraus}, A.~L., {Cody}, A.~M., {Covey}, K.~R., {et~al.} 2015, \apj, 807, 3
+
+\bibitem[{Kroupa(2002)}]{Kroupa2002}
+Kroupa, P. 2002, Science (New York, N.Y.), 295, 82
+
+\bibitem[{{Lodieu} {et~al.}(2015){Lodieu}, {Alonso}, {Gonz{\'a}lez
+  Hern{\'a}ndez}, {Sanchis-Ojeda}, {Narita}, {Kawashima}, {Kawauchi},
+  {Su{\'a}rez Mascare{\~n}o}, {Deeg}, {Prieto Arranz}, {Rebolo}, {Pall{\'e}},
+  {B{\'e}jar}, {Ferragamo}, \& {Rubi{\~n}o-Mart{\'{\i}}n}}]{Lodieu2015}
+{Lodieu}, N., {Alonso}, R., {Gonz{\'a}lez Hern{\'a}ndez}, J.~I., {et~al.} 2015,
+  \aap, 584, A128
+
+\bibitem[{MacDonald \& Mullan(2010)}]{MM10}
+MacDonald, J. \& Mullan, D.~J. 2010, \apj, 723, 1599
+
+\bibitem[{{MacDonald} \& {Mullan}(2015)}]{MacDonald2015}
+{MacDonald}, J. \& {Mullan}, D.~J. 2015, \mnras, 448, 2019
+
+\bibitem[{{Malo} {et~al.}(2014){Malo}, {Doyon}, {Feiden}, {Albert},
+  {Lafreni{\`e}re}, {Artigau}, {Gagn{\'e}}, \& {Riedel}}]{Malo2014}
+{Malo}, L., {Doyon}, R., {Feiden}, G.~A., {et~al.} 2014, \apj, 792, 37
+
+\bibitem[{{Naylor}(2009)}]{Naylor2009}
+{Naylor}, T. 2009, \mnras, 399, 432
+
+\bibitem[{{Neckel}(1995)}]{Neckel1995}
+{Neckel}, H. 1995, \solphys, 156, 7
+
+\bibitem[{{Ochsenbein} {et~al.}(2000){Ochsenbein}, {Bauer}, \&
+  {Marcout}}]{Ochsenbein2000}
+{Ochsenbein}, F., {Bauer}, P., \& {Marcout}, J. 2000, \aaps, 143, 23
+
+\bibitem[{{Pecaut} \& {Mamajek}(2013)}]{Pecaut2013}
+{Pecaut}, M.~J. \& {Mamajek}, E.~E. 2013, \apjs, 208, 9
+
+\bibitem[{{Pecaut} {et~al.}(2012){Pecaut}, {Mamajek}, \& {Bubar}}]{Pecaut2012}
+{Pecaut}, M.~J., {Mamajek}, E.~E., \& {Bubar}, E.~J. 2012, \apj, 746, 154
+
+\bibitem[{P\'erez \& Granger(2007)}]{Perez2007}
+P\'erez, F. \& Granger, B.~E. 2007, Computing in Science and Engineering, 9, 21
+
+\bibitem[{{Preibisch}(2012)}]{Preibisch2012}
+{Preibisch}, T. 2012, Research in Astronomy and Astrophysics, 12, 1
+
+\bibitem[{{Preibisch} {et~al.}(2002){Preibisch}, {Brown}, {Bridges},
+  {Guenther}, \& {Zinnecker}}]{Preibisch2002}
+{Preibisch}, T., {Brown}, A.~G.~A., {Bridges}, T., {Guenther}, E., \&
+  {Zinnecker}, H. 2002, \aj, 124, 404
+
+\bibitem[{{Preibisch} \& {Zinnecker}(1999)}]{Preibisch1999}
+{Preibisch}, T. \& {Zinnecker}, H. 1999, \aj, 117, 2381
+
+\bibitem[{{Rizzuto} {et~al.}(2015{\natexlab{a}}){Rizzuto}, {Ireland}, {Dupuy},
+  \& {Kraus}}]{Rizzuto2015b}
+{Rizzuto}, A.~C., {Ireland}, M.~J., {Dupuy}, T.~J., \& {Kraus}, A.~L.
+  2015{\natexlab{a}}, arXiv: 1512.05371
+
+\bibitem[{{Rizzuto} {et~al.}(2015{\natexlab{b}}){Rizzuto}, {Ireland}, \&
+  {Kraus}}]{Rizzuto2015}
+{Rizzuto}, A.~C., {Ireland}, M.~J., \& {Kraus}, A.~L. 2015{\natexlab{b}},
+  \mnras, 448, 2737
+
+\bibitem[{{Salpeter}(1955)}]{Salpeter1955}
+{Salpeter}, E.~E. 1955, \apj, 121, 161
+
+\bibitem[{{Sartori} {et~al.}(2003){Sartori}, {L{\'e}pine}, \&
+  {Dias}}]{Sartori2003}
+{Sartori}, M.~J., {L{\'e}pine}, J.~R.~D., \& {Dias}, W.~S. 2003, \aap, 404, 913
+
+\bibitem[{{Scalo}(1998)}]{Scalo1998}
+{Scalo}, J. 1998, in Astronomical Society of the Pacific Conference Series,
+  Vol. 142, The Stellar Initial Mass Function (38th Herstmonceux Conference),
+  ed. G.~{Gilmore} \& D.~{Howell}, 201
+
+\bibitem[{{Shulyak} {et~al.}(2014){Shulyak}, {Reiners}, {Seemann}, {Kochukhov},
+  \& {Piskunov}}]{Shulyak2014}
+{Shulyak}, D., {Reiners}, A., {Seemann}, U., {Kochukhov}, O., \& {Piskunov}, N.
+  2014, \aap, 563, A35
+
+\bibitem[{{Siess} {et~al.}(2000){Siess}, {Dufour}, \& {Forestini}}]{Siess2000}
+{Siess}, L., {Dufour}, E., \& {Forestini}, M. 2000, \aap, 358, 593
+
+\bibitem[{{Slesnick} {et~al.}(2008){Slesnick}, {Hillenbrand}, \&
+  {Carpenter}}]{Slesnick2008}
+{Slesnick}, C.~L., {Hillenbrand}, L.~A., \& {Carpenter}, J.~M. 2008, \apj, 688,
+  377
+
+\bibitem[{{Somers} \& {Pinsonneault}(2015)}]{Somers2015b}
+{Somers}, G. \& {Pinsonneault}, M.~H. 2015, \apj, 807, 174
+
+\bibitem[{{Spruit}(1982)}]{Spruit1982a}
+{Spruit}, H.~C. 1982, \aap, 108, 348
+
+\bibitem[{{Spruit} \& {Weiss}(1986)}]{Spruit1986}
+{Spruit}, H.~C. \& {Weiss}, A. 1986, \aap, 166, 167
+
+\bibitem[{Stello {et~al.}(2016)Stello, Cantiello, Fuller, Huber, Garc\'{\i}a,
+  Bedding, Bildsten, \& Aguirre}]{Stello2016a}
+Stello, D., Cantiello, M., Fuller, J., {et~al.} 2016, Nature, 529, 364
+
+\bibitem[{Torres {et~al.}(2010)Torres, Andersen, \& Gim\'{e}nez}]{Torres2010}
+Torres, G., Andersen, J., \& Gim\'{e}nez, A. 2010, \aapr, 18, 67
+
+\bibitem[{{Ventura} {et~al.}(1998){Ventura}, {Zeppieri}, {Mazzitelli}, \&
+  {D'Antona}}]{Ventura1998}
+{Ventura}, P., {Zeppieri}, A., {Mazzitelli}, I., \& {D'Antona}, F. 1998, \aap,
+  331, 1011
+
+\bibitem[{{Williams} {et~al.}(2015){Williams}, {Kelley}, \& {et
+  al.}}]{Gnuplot5.0}
+{Williams}, T., {Kelley}, C., \& {et al.} 2015, Gnuplot 5.0: an interactive
+  plotting program, \url{http://www.gnuplot.info/}
+
+\end{thebibliography}
 

### 2016-05-13 paper/ms.tex
addressed refs first comment

@@
 \label{sec:disc}
-An age of {\bf 9 -- 10} Myr gives broad agreement across the HR and mass-radius diagrams.
-No stellar population in Upper Scorpius {\bf studied here robustly} supports the possibility that the median age of the association is 5 Myr.
+An age of 9 -- 10 Myr gives broad agreement across the HR and mass-radius diagrams.
+No stellar population in Upper Scorpius studied here robustly supports the possibility that the median age of the association is 5 Myr.
 There are, however, still age discrepancies that must be addressed.
-As noted above, the median age for F-type stars appears to be a few million years older than stars of other spectral types.
-This {\bf discrepancy} is {\bf perplexing and deserves further investigation}, especially considering that potential missing physics in the models would likely conspire to make F-stars older, not younger.
+As noted above, the median age {\bf inferred from} F-type stars appears to be a few million years older than {\bf the median age inferred from} stars of other spectral types.
+This discrepancy is perplexing and deserves further investigation, especially considering that {\bf physics potentially missing from the models} would likely conspire to {\bf increase the age inferred from} F-stars.
 It should be noted that most F-type stars in Upper Scorpius are at a stage of evolution where models predict radii increase and subsequently decrease over a period of roughly 4 -- 8 Myr.
-{\bf The timescale for this process is} similar to the observed age discrepancy (see Fig.~\ref{fig:bump} in Sect.~\ref{sec:radius}) and may be indicative of potential shortcomings in existing model physics such as radiative opacities or nuclear reaction cross-sections.
+The timescale for this process is similar to the observed age discrepancy (see Fig.~\ref{fig:bump} in Sect.~\ref{sec:radius}) and may be indicative of potential shortcomings in existing model physics such as radiative opacities or nuclear reaction cross-sections.
 
-{\bf Age discrepancies also exist with two B-type members of Upper Scorpius: \object{$\tau$ Sco} and \object{$\omega$ Sco}.
+Age discrepancies also exist with two B-type members of Upper Scorpius: \object{$\tau$ Sco} and \object{$\omega$ Sco}.
 They exhibit ages between 2 and 5 Myr depending on whether rotation is accounted for in stellar evolution models \citep{Pecaut2012}.
@@
 G.A.F.
-thanks Alexis Lavail, Eric Mamajek, James Silvester, and Eric Stempels for reading and commenting on an early version of this manuscript as well as Bengt Gustafsson and Thomas Nordlander for interesting discussions that helped improved the manuscript.
+thanks Alexis Lavail, Eric Mamajek, James Silvester, and Eric Stempels for reading and commenting on an early version of this manuscript as well as Bengt Gustafsson and Thomas Nordlander for interesting discussions that helped improve the manuscript.
 The magnetic Dartmouth stellar evolution code was originally developed with support of National Science Foundation (NSF) grant AST-0908345.

### 2016-06-23 paper/ref/20160509_referee_response_02.txt
Edits and responses to report 2

> I have reviewed the latest draft of the paper and find it is essentially ready to be accepted. I would encourage the author to consider the following minor comments:

> - Section 5: I find the following two sentences difficult to understand. There is some confusion between real stars and models that needs to be clarified.

> "There are, however, still age discrepancies that must be addressed. As noted above, the median age for F-type stars appears to be a few million years older than stars of other spectral types. This discrepancy is perplexing and deserves further investigation, especially considering that potential missing physics in the models would likely conspire to make F-stars older, not younger."

I have attempted to emphasize a distinction between models and real stars by emphasizing that ages are inferred from models and are not a definite property of F-type stars.

> - Figure 4: It is much more common to discuss the mass of the convective envelope than of the radiative core.

This is true. I adopted the radiative core mass for consistency with Gregory et al. (2012), who used radiative core mass to explain variations in the geometry and complexity of large-scale magnetic fields among young stars. However, as noted by the reviewer, it is not an optimal selection, as convection zone structure is more pertinent for theoretical discussions of stellar structure and 3D magnetic dynamo simulations.

I've recast the discussion and Figure 4 in terms of convective envelope mass and refer to radiative core mass only for comparison with Gregory et al. (2012).

### 2016-06-23 paper/arXiv/ms.tex
Edits and responses to report 2

@@
                 SE-751 20, Uppsala, Sweden. \\
+              Department of Physics, University of North Georgia, 82 College Circle, Dahlonega, GA 30597, USA. \\
                 \email{gregory.feiden@physics.uu.se}
@@
 
-   \date{Version: \today; Submitted: October 21, 2015; Re-submitted: April 27, 2016.}
+   \date{Version: \today; Submitted: October 21, 2015; Re-submitted: June 23, 2016.}
 
@@
 Cooler (K, M) stars typically yield ages that are systematically younger than warmer (A, F, G) stars by a factor of two.
-I explore the possibility that these age discrepancies are the result of magnetic inhibition of convection in young cool stars by using magnetic stellar evolution isochrones to determine the age of the Upper Scorpius subgroup of the Scorpius-Centaurus OB Association.
+I explore the possibility that these age discrepancies are the result of magnetic inhibition of convection in cool young stars by using magnetic stellar evolution isochrones to determine the age of the Upper Scorpius subgroup of the Scorpius-Centaurus OB Association.
 A median age of 10 Myr consistent across spectral types A through M is found, except for a subset of F-type stars that appear significantly older.
@@
 A region in the HR diagram is identified that plausibly connects stars whose structures are weakly influenced by the presence of magnetic fields with those whose structures are strongly influenced by magnetic fields.
-The models suggest this region is characterized by stars with rapidly thinning outer convective envelopes where the radiative core mass is greater than 80\% of the total stellar mass.
+The models suggest this region is characterized by stars with rapidly thinning outer convective envelopes where the radiative core mass is greater than 75\% of the total stellar mass.
 Furthermore, depletion of lithium predicted from magnetic models appears in better agreement with observed lithium equivalent widths than predictions from non-magnetic models.
@@
 There are, however, still age discrepancies that must be addressed.
-As noted above, the median age for F-type stars appears to be a few million years older than stars of other spectral types.
-This discrepancy is perplexing and deserves further investigation, especially considering that potential missing physics in the models would likely conspire to make F-stars older, not younger.
-It should be noted that most F-type stars in Upper Scorpius are at a stage of evolution where models predict radii increase and subsequently decrease over a period of roughly 4 -- 8 Myr.
+As noted above, the median age inferred from models for F-type stars appears to be a few million years older than the age inferred from models for stars of other spectral types.
+This discrepancy is perplexing and deserves further investigation, especially considering that physics potentially missing from the models would likely increase the inferred age for F-stars, widening the age discrepancy.
+It should be noted that most F-type stars in Upper Scorpius appear to be at a stage of evolution where models predict stellar radii increase and subsequently decrease over a period of roughly 4 -- 8 Myr.
 The timescale for this process is similar to the observed age discrepancy (see Fig.~\ref{fig:bump} in Sect.~\ref{sec:radius}) and may be indicative of potential shortcomings in existing model physics such as radiative opacities or nuclear reaction cross-sections.
@@
     \centering
-    \includegraphics[width=0.42\linewidth]{radiative_core_masses.eps} \qquad
-    \includegraphics[width=0.48\linewidth]{radiative_core_mass_difference.eps}
-    \caption{Mass fraction of the stellar radiative core as a function of (a) total stellar mass and (b) effective temperature.
-(c) Difference in radiative core mass between magnetic and standard stellar evolution models as a function of effective temperature.
-The difference is shown as the radiative core mass of a magnetic model minus the radiative core mass of a standard stellar model at the same effective temperature, ($M_{\rm rad.\ core,\, mag} - M_{\rm rad.\ core,\, std}$), shown for two ages of standard models (5 Myr, 10 Myr).}
+    \includegraphics[width=0.42\linewidth]{convective_env_masses.eps} \qquad
+    \includegraphics[width=0.48\linewidth]{convective_env_mass_difference.eps}
+    \caption{Mass fraction of the stellar convective envelopes as a function of (a) total stellar mass and (b) effective temperature.
+(c) Difference in convective envelope mass between magnetic and standard stellar evolution models as a function of effective temperature.
+The difference is shown as the convective envelope mass of a magnetic model minus the convective envelope mass of a standard stellar model at the same effective temperature, ($M_{\rm conv.\ env.,\, mag} - M_{\rm conv.\ env,\, std}$), shown for two ages of standard models (5 Myr, 10 Myr).}
     \label{fig:rad_core}
@@
 
-While the demise of outer convection zones explains the final convergence of magnetic and standard models, it doesn't necessarily explain the beginning of the transition that occurs between $T_{\rm eff} = $4\,500~K and 5\,000~K.
-In the transition region, magnetic models have masses between 1.26 $M_{\odot}$ ($T_{\rm eff} = $ 4\,500~K) and 1.40 $M_{\odot}$ ($T_{\rm eff} = $5\,000~K).
-Magnetic models predict that these stars have radiative core masses between 76\% and 88\% of their total stellar mass, respectively (see Figure~\ref{fig:rad_core}a).
+While the demise of outer convection zones explains the final convergence of magnetic and standard models, it doesn't necessarily explain the beginning of the transition that occurs between $T_{\rm eff} = $ 4\,500~K and 5\,000~K.
+In this transition region, magnetic models have masses between 1.26 $M_{\odot}$ ($T_{\rm eff} = $ 4\,500~K) and 1.40 $M_{\odot}$ ($T_{\rm eff} = $5\,000~K).
+Magnetic models predict that these stars have convective envelope masses between 24\% and 12\% of their total stellar mass, respectively (see Figure~\ref{fig:rad_core}a).
 The 1.40 $M_{\odot}$ model is of particular note, as Figure~\ref{fig:mrd} suggests that 1.40 $M_{\odot}$ stars are entering a brief period of radius inflation that accompanies the increasing energy generation from the $p$-$p$ chain and CN-cycle burning prior to the onset of core convection \citep[e.g.,][]{Iben1965,Bodenheimer1965}.
@@
 If the transition region begins around 4\,500~K, as one might expect from the knee in the empirical HR diagram (Fig.~\ref{fig:empirical}), a rapid decrease in surface magnetic field strengths cannot fully explain the start of the transition.
-Note that Fig.~\ref{fig:rad_core}(c) suggests that the difference in size between radiative cores in magnetic and standard stellar models occurs around $T_{\rm eff} \sim 4\,500$~K, suggesting there is something relatively unique occurring at that effective temperature.
+Note that Fig.~\ref{fig:rad_core}(c) suggests that the mass difference between convective envelopes in magnetic and standard stellar models occurs around $T_{\rm eff} \sim 4\,500$~K,\footnote{The slope in the convective envelope mass difference below $3\,500$~K is due to the fact that models predict stars are fully convective below that temperature, but cooling of the stellar photosphere by magnetic inhibition of convection means magnetic models have a larger mass at a given $T_{\rm eff}$ than standard models.} suggesting there is something relatively unique occurring at that effective temperature.
 However, Fig.~\ref{fig:ages} shows no noticeable change in morphology at  $T_{\rm eff} \sim 4\,500$~K.
@@
 The sharp knee at \teff~=~4\,500~K in Fig.~\ref{fig:empirical} may be the result of a global change in magnetic field topology.
-Evidence for this comes from \citet{Gregory2012}, who noted that large-scale magnetic field topologies observed on pre-main-sequence stars appear to correlate with their predicted radiative core mass.
-Specifically, they noted a shift from predominantly dipolar axisymmetric magnetic field topologies to multi-polar non-axisymmetric field topologies when the estimated radiative core mass $M_{\rm rad.\ core} > 0.4 M_\star$.
-It was noted above that at \teff~=~4\,500~K, magnetic models predict a star with $M_{\star} = 1.26 M_{\odot}$ and $M_{\rm rad.\ core} \approx 0.76 M_{\star}$, well above the predicted radiative core mass where stars are expected to shift toward multi-polar non-axisymmetric field topologies.
+Evidence for this comes from \citet{Gregory2012}, who noted that large-scale magnetic field topologies observed on pre-main-sequence stars appear to correlate with their predicted \emph{radiative core mass}, or alternatively, their convective envelope mass.
+Specifically, \citet{Gregory2012} noted a shift from predominantly dipolar axisymmetric magnetic field topologies to multi-polar non-axisymmetric field topologies when the estimated radiative core mass $M_{\rm rad.\ core} > 0.4\ M_\star$.
+It was noted above that at \teff~=~4\,500~K, magnetic models predict a star with $M_{\star} = 1.26\ M_{\odot}$ and $M_{\rm conv.\ env.} \approx 0.24\ M_{\star}$ ($M_{\rm rad.\ core} \approx 0.76\ M_{\star}$), well below the predicted convective envelope mass where stars are expected to shift toward multi-polar non-axisymmetric field topologies.
 
@@
 Hypothetically, if they were to observe a star in Upper Scorpius with \teff~=~4\,500~K, their HR diagram analysis would suggest that the star is approximately 5 Myr old.
-Figures~\ref{fig:rad_core}(a) and (b) reveal that a star with \teff~=~4\,500~K at 5 Myr is expected to have a mass of $M_{\star} = 1.10 M_{\odot}$ with $M_{\rm rad.\ core} \approx 0.43 M_{\star}$.
+Figures~\ref{fig:rad_core}(a) and (b) reveal that a star with \teff~=~4\,500~K at 5 Myr is expected to have a mass of $M_{\star} = 1.10\ M_{\odot}$ with $M_{\rm conv.\ env.} \approx 0.67\ M_{\odot}$ and thus $M_{\rm rad.\ core} \approx 0.43\ M_{\odot}$ (see Fig.~\ref{fig:rad_core}(a)).
 This radiative core mass corresponds to 39\% of the total stellar mass and is consistent with the boundary identified by \citet{Gregory2012}.
 
-The implications of this results are that: (1) the knee observed in Fig.~\ref{fig:empirical} may be the result of a change in magnetic field topology and (2) the shift in magnetic field topology from a predominantly axisymmetric configuration to a non-axisymmetric configuration may occur when the radiative core mass is much larger than initially suggested.
-Magnetic models suggest the shift in global magnetic field topology occurs when $M_{\rm rad.\ core} / M_{\star} \approx 0.75$ as compared to $M_{\rm rad.\ core} / M_{\star} \approx 0.40$ \citep{Gregory2012}.
+The implications of this results are that: (1) the knee observed in Fig.~\ref{fig:empirical} may be the result of a change in magnetic field topology and (2) the shift in magnetic field topology from a predominantly axisymmetric configuration to a non-axisymmetric configuration may occur when the radiative core mass is much larger---and convective envelope mass much smaller---than initially suggested.
+Magnetic models suggest the shift in global magnetic field topology may occur when $M_{\rm conv.\ env} / M_{\star} \approx 0.25$ ($M_{\rm rad.\ core} / M_{\star} \approx 0.75$) as compared to $M_{\rm conv.\ env.} / M_{\star} \approx 0.60$ \citep[$M_{\rm rad.\ core} / M_{\star} \approx 0.40$;][]{Gregory2012}.
 
@@
 
-The observed knee and shallower slope in Fig.~\ref{fig:empirical} appear to be real features.
+The observed knee and shallower slope in Fig.~\ref{fig:empirical} appear to be genuine features.
 General agreement between the behavior of the magnetic model isochrone and the observed stellar locus provides evidence that magnetic inhibition of convection is the mechanism that is producing these effects.
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=0.85\linewidth]{radius_bump.eps}
+    \caption{Brief period of radius inflation described in Sect.~\ref{sec:radius} for stars with masses of 1.60\msun\ (blue solid), 1.55\msun\ (green short-dashed), 1.50\msun\ (blue dash-dotted), 1.45\msun\ (yellow long-dashed).
+Mass tracks are computed without a magnetic field (i.e., non-magnetic configuration).
+Effective temperatures at these masses are characteristic of F stars at 10 Myr.}
+    \label{fig:bump}
+\end{figure}
+
 Assessing in detail whether the larger radius of HD 144548 A is real is beyond the scope of this work.
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.85\linewidth]{radius_bump.eps}
-    \caption{Brief period of radius inflation described in Sect.~\ref{sec:radius} for stars with masses of 1.60\msun\ (blue solid), 1.55\msun\ (green short-dashed), 1.50\msun\ (blue dash-dotted), 1.45\msun\ (yellow long-dashed).
-Mass tracks are computed without a magnetic field (i.e., non-magnetic configuration).
-Effective temperatures at these masses are characteristic of F stars at 10 Myr.}
-    \label{fig:bump}
-\end{figure}
-
 \subsection{On Starspots}
@@
 \subsection{Lithium Depletion}
+
+\begin{figure}[t]
+    \includegraphics[width=0.85\linewidth]{Li7_USco_Beq.eps}
+    \caption{Lithium abundance  as a function of effective temperature at 10 Myr.
+Predictions are shown from standard (light-blue dashed line) and magnetic (yellow solid line) stellar evolution isochrones.
+Models were computed using the setup described in Sect.~\ref{sec:models}.
+Lithium abundance is defined as $A(\,^7{\rm Li}) = \log_{10}(N_{\rm Li}/N_{\rm H}) + 12$.}
+    \label{fig:lithium}
+\end{figure}
+
 An approach to validating magnetic stellar models is the determination of lithium abundances \citep{MacDonald2015}, or observation of lithium equivalent widths.
@@
 Accounting for uncertainties in the SpT-\teff\ conversion, observed lithium equivalent widths support the validity of magnetic models and an inferred age of 10 Myr for the low-mass stars in Upper Scorpius.
-
-\begin{figure}[t]
-    \includegraphics[width=0.85\linewidth]{Li7_USco_Beq.eps}
-    \caption{Lithium abundance  as a function of effective temperature at 10 Myr.
-Predictions are shown from standard (light-blue dashed line) and magnetic (yellow solid line) stellar evolution isochrones.
-Models were computed using the setup described in Sect.~\ref{sec:models}.
-Lithium abundance is defined as $A(\,^7{\rm Li}) = \log_{10}(N_{\rm Li}/N_{\rm H}) + 12$.}
-    \label{fig:lithium}
-\end{figure}
 
@@
 Ages inferred from standard model isochrones may be systematically too young by a factor of two resulting in a systematic underestimation of giant planet and brown dwarfs masses by roughly 35\% \citep{Baraffe2003}.
-To facilitate their adoption, all models used in this study are available online\footnote{\url{https://github.com/gfeiden/MagneticUpperSco/}}.
-A small grid of solar-metallicity magnetic stellar mass tracks and isochrones is also under construction, as is a web-interface to compute custom magnetic models.
+To facilitate their adoption, all models used in this study are available online.\footnote{\url{https://github.com/gfeiden/MagneticUpperSco/}} A small grid of solar-metallicity magnetic stellar mass tracks and isochrones is also under construction, as is a web-interface to compute custom magnetic models.
 
@@
 thanks Alexis Lavail, Eric Mamajek, James Silvester, and Eric Stempels for reading and commenting on an early version of this manuscript as well as Bengt Gustafsson and Thomas Nordlander for interesting discussions that helped improved the manuscript.
+G.A.F also thanks the anonymous reviewer posing interesting questions that led to significant improvements in the manuscript.
 The magnetic Dartmouth stellar evolution code was originally developed with support of National Science Foundation (NSF) grant AST-0908345.

### 2016-06-23 paper/ms.tex
Edits and responses to report 2

@@
 There are, however, still age discrepancies that must be addressed.
-As noted above, the median age {\bf inferred from} F-type stars appears to be a few million years older than {\bf the median age inferred from} stars of other spectral types.
-This discrepancy is perplexing and deserves further investigation, especially considering that {\bf physics potentially missing from the models} would likely conspire to {\bf increase the age inferred from} F-stars.
-It should be noted that most F-type stars in Upper Scorpius are at a stage of evolution where models predict radii increase and subsequently decrease over a period of roughly 4 -- 8 Myr.
+As noted above, the median age {\bf inferred from models} for F-type stars appears to be a few million years older than {\bf the age inferred from models for} stars of other spectral types.
+This discrepancy is perplexing and deserves further investigation, especially considering that {\bf physics potentially missing from} the models would likely {\bf increase the inferred age for F-stars, widening the age discrepancy.} It should be noted that most F-type stars in Upper Scorpius {\bf appear to be} at a stage of evolution where models predict {\bf stellar} radii increase and subsequently decrease over a period of roughly 4 -- 8 Myr.
 The timescale for this process is similar to the observed age discrepancy (see Fig.~\ref{fig:bump} in Sect.~\ref{sec:radius}) and may be indicative of potential shortcomings in existing model physics such as radiative opacities or nuclear reaction cross-sections.
@@
 
-While the demise of outer convection zones explains the final convergence of magnetic and standard models, it doesn't necessarily explain the beginning of the transition that occurs between $T_{\rm eff} = $4\,500~K and 5\,000~K.
-In the transition region, magnetic models have masses between 1.26 $M_{\odot}$ ($T_{\rm eff} = $ 4\,500~K) and 1.40 $M_{\odot}$ ($T_{\rm eff} = $5\,000~K).
-Magnetic models predict that these stars have radiative core masses between 76\% and 88\% of their total stellar mass, respectively (see Figure~\ref{fig:rad_core}a).
+While the demise of outer convection zones explains the final convergence of magnetic and standard models, it doesn't necessarily explain the beginning of the transition that occurs between $T_{\rm eff} = $ 4\,500~K and 5\,000~K.
+In this transition region, magnetic models have masses between 1.26 $M_{\odot}$ ($T_{\rm eff} = $ 4\,500~K) and 1.40 $M_{\odot}$ ($T_{\rm eff} = $5\,000~K).
+Magnetic models predict that these stars have {\bf convective envelope} masses between 24\% and 12\% of their total stellar mass, respectively (see Figure~\ref{fig:rad_core}a).
 The 1.40 $M_{\odot}$ model is of particular note, as Figure~\ref{fig:mrd} suggests that 1.40 $M_{\odot}$ stars are entering a brief period of radius inflation that accompanies the increasing energy generation from the $p$-$p$ chain and CN-cycle burning prior to the onset of core convection \citep[e.g.,][]{Iben1965,Bodenheimer1965}.
@@
 If the transition region begins around 4\,500~K, as one might expect from the knee in the empirical HR diagram (Fig.~\ref{fig:empirical}), a rapid decrease in surface magnetic field strengths cannot fully explain the start of the transition.
-Note that Fig.~\ref{fig:rad_core}(c) suggests that the difference in size between radiative cores in magnetic and standard stellar models occurs around $T_{\rm eff} \sim 4\,500$~K, suggesting there is something relatively unique occurring at that effective temperature.
+Note that Fig.~\ref{fig:rad_core}(c) suggests that the {\bf mass} difference between convective envelopes in magnetic and standard stellar models occurs around $T_{\rm eff} \sim 4\,500$~K,\footnote{The slope in the convective envelope mass difference below $3\,500$~K is due to the fact that models predict stars are fully convective below that temperature, but cooling of the stellar photosphere by magnetic inhibition of convection means magnetic models have a larger mass at a given $T_{\rm eff}$ than standard models.} suggesting there is something relatively unique occurring at that effective temperature.
 However, Fig.~\ref{fig:ages} shows no noticeable change in morphology at  $T_{\rm eff} \sim 4\,500$~K.
@@
 The sharp knee at \teff~=~4\,500~K in Fig.~\ref{fig:empirical} may be the result of a global change in magnetic field topology.
-Evidence for this comes from \citet{Gregory2012}, who noted that large-scale magnetic field topologies observed on pre-main-sequence stars appear to correlate with their predicted radiative core mass.
-Specifically, they noted a shift from predominantly dipolar axisymmetric magnetic field topologies to multi-polar non-axisymmetric field topologies when the estimated radiative core mass $M_{\rm rad.\ core} > 0.4 M_\star$.
-It was noted above that at \teff~=~4\,500~K, magnetic models predict a star with $M_{\star} = 1.26 M_{\odot}$ and $M_{\rm rad.\ core} \approx 0.76 M_{\star}$, well above the predicted radiative core mass where stars are expected to shift toward multi-polar non-axisymmetric field topologies.
+Evidence for this comes from \citet{Gregory2012}, who noted that large-scale magnetic field topologies observed on pre-main-sequence stars appear to correlate with their predicted \emph{radiative core mass}, {\bf or alternatively, their convective envelope mass}.
+Specifically, \citet{Gregory2012} noted a shift from predominantly dipolar axisymmetric magnetic field topologies to multi-polar non-axisymmetric field topologies when the estimated radiative core mass $M_{\rm rad.\ core} > 0.4\ M_\star$.
+It was noted above that at \teff~=~4\,500~K, magnetic models predict a star with $M_{\star} = 1.26\ M_{\odot}$ and $M_{\rm conv.\ env.} \approx 0.24\ M_{\star}$ ($M_{\rm rad.\ core} \approx 0.76\ M_{\star}$), well below the predicted convective envelope mass where stars are expected to shift toward multi-polar non-axisymmetric field topologies.
 
@@
 
-The observed knee and shallower slope in Fig.~\ref{fig:empirical} appear to be real features.
+The observed knee and shallower slope in Fig.~\ref{fig:empirical} appear to be {\bf genuine} features.
 General agreement between the behavior of the magnetic model isochrone and the observed stellar locus provides evidence that magnetic inhibition of convection is the mechanism that is producing these effects.
@@
 G.A.F.
-thanks Alexis Lavail, Eric Mamajek, James Silvester, and Eric Stempels for reading and commenting on an early version of this manuscript as well as Bengt Gustafsson and Thomas Nordlander for interesting discussions that helped improve the manuscript.
+thanks Alexis Lavail, Eric Mamajek, James Silvester, and Eric Stempels for reading and commenting on an early version of this manuscript as well as Bengt Gustafsson and Thomas Nordlander for interesting discussions that helped improved the manuscript.
+G.A.F also thanks the anonymous reviewer posing interesting questions that led to significant improvements in the manuscript.
 The magnetic Dartmouth stellar evolution code was originally developed with support of National Science Foundation (NSF) grant AST-0908345.

### 2016-06-27 paper/ref/20160509_referee_response_02.txt
accepted version

@@
+Editor Bertout,
+
+Thank you for the opportunity to address the reviewers final comments and to revise the manuscript accordingly.
+
+In their report, the reviewer commented on two aspects of the paper.
+First, the highlighted a couple of confusing sentences at the beginning of Section 5.
+I have added bit of text in each sentence in an effort to better delineate between models and real stars, as requested by the reviewer.
+
+The second comment was with regard to Section 5.1, where Figure 4 and parts of the text referred explicitly to the radiative core mass predicted by stellar models.
+The reviewer correctly points out that this breaks with convention, which is to discuss the mass of the outer convective envelope, not the radiative core.
+I agree with their assertion and have modified Figure 4 and the text to frame the discussion around the convective envelope mass.
+However, the original motivation was for consistency with a previous study, which adopted the radiative core mass as a controlling factor for large-scale magnetic field topology.
+Thus, while re-framing the discussion, I still refer to the radiative core mass to provide direct comparison with results from that previous study.
+
+Finally, I made changes throughout the text where I felt my original word choice was sub-optimal.
+
+All changes are marked in bold font. In my response to the reviewer, their comments are preceded by a '>' and my responses follow.
+
+Sincerely,
+
+Gregory Feiden
+
+=====
+
 > I have reviewed the latest draft of the paper and find it is essentially ready to be accepted. I would encourage the author to consider the following minor comments:

### 2016-06-27 paper/arXiv/ms.tex
accepted version

@@
 
-   \author{Gregory A.~Feiden}
+   \author{Gregory A.~Feiden\inst{1,\,2}}
 
    \institute{Department of Physics \& Astronomy, Uppsala University, Box 516,
-                SE-751 20, Uppsala, Sweden. \\
+                SE-751 20, Uppsala, Sweden.
+                \and
               Department of Physics, University of North Georgia, 82 College Circle, Dahlonega, GA 30597, USA. \\
-                \email{gregory.feiden@physics.uu.se}
+                \email{gregory.a.feiden@gmail.com}
              }
 
-   \date{Version: \today; Submitted: October 21, 2015; Re-submitted: June 23, 2016.}
+   \date{Submitted: 21 October 2015; Accepted: 27 June 2016.}
 
@@
 thanks Alexis Lavail, Eric Mamajek, James Silvester, and Eric Stempels for reading and commenting on an early version of this manuscript as well as Bengt Gustafsson and Thomas Nordlander for interesting discussions that helped improved the manuscript.
-G.A.F also thanks the anonymous reviewer posing interesting questions that led to significant improvements in the manuscript.
+G.A.F also thanks the anonymous reviewer for posing interesting questions that led to significant improvements in the manuscript.
 The magnetic Dartmouth stellar evolution code was originally developed with support of National Science Foundation (NSF) grant AST-0908345.

### 2016-06-27 paper/ms.tex
accepted version

@@
 Cooler (K, M) stars typically yield ages that are systematically younger than warmer (A, F, G) stars by a factor of two.
-I explore the possibility that these age discrepancies are the result of magnetic inhibition of convection in cool young stars by using magnetic stellar evolution isochrones to determine the age of the Upper Scorpius subgroup of the Scorpius-Centaurus OB Association.
+I explore the possibility that these age discrepancies are the result of magnetic inhibition of convection in {\bf cool young} stars by using magnetic stellar evolution isochrones to determine the age of the Upper Scorpius subgroup of the Scorpius-Centaurus OB Association.
 A median age of 10 Myr consistent across spectral types A through M is found, except for a subset of F-type stars that appear significantly older.
@@
 A region in the HR diagram is identified that plausibly connects stars whose structures are weakly influenced by the presence of magnetic fields with those whose structures are strongly influenced by magnetic fields.
-The models suggest this region is characterized by stars with rapidly thinning outer convective envelopes where the radiative core mass is greater than 75\% of the total stellar mass.
+The models suggest this region is characterized by stars with rapidly thinning outer convective envelopes where the radiative core mass is greater than {\bf 75\%} of the total stellar mass.
 Furthermore, depletion of lithium predicted from magnetic models appears in better agreement with observed lithium equivalent widths than predictions from non-magnetic models.
@@
 
+\begin{figure}[t]
+    \includegraphics[width=0.85\linewidth]{Li7_USco_Beq.eps}
+    \caption{Lithium abundance  as a function of effective temperature at 10 Myr.
+Predictions are shown from standard (light-blue dashed line) and magnetic (yellow solid line) stellar evolution isochrones.
+Models were computed using the setup described in Sect.~\ref{sec:models}.
+Lithium abundance is defined as $A(\,^7{\rm Li}) = \log_{10}(N_{\rm Li}/N_{\rm H}) + 12$.}
+    \label{fig:lithium}
+\end{figure}
+
 Figure \ref{fig:lithium} demonstrates the impact that magnetic inhibition of convection has on predicted lithium abundances for stars in Upper Scorpius at 10 Myr.

### 2016-07-12 paper/ms.tex
final copy edited proof

--- 2016-06-23 paper/ms.tex
@@
 
-\titlerunning{A Consistent 10 Myr Age for Upper Scorpius}
+\titlerunning{A consistent 10 Myr age for Upper Scorpius}
 \authorrunning{G.~A. Feiden}
@@
 
-   \title{Magnetic Inhibition of Convection and the Fundamental Properties of Low--Mass Stars}
-   \subtitle{III. A Consistent 10 Myr Age for the Upper Scorpius OB Association}
+   \title{Magnetic inhibition of convection and the fundamental properties of low--mass stars}
+   \subtitle{III. A consistent 10 Myr age for the Upper Scorpius OB association}
 
-   \author{Gregory A.~Feiden}
+   \author{Gregory A.~Feiden\inst{1,\,2}}
 
    \institute{Department of Physics \& Astronomy, Uppsala University, Box 516,
-                SE-751 20, Uppsala, Sweden. \\
+                SE-751 20, Uppsala, Sweden.
+                \and
               Department of Physics, University of North Georgia, 82 College Circle, Dahlonega, GA 30597, USA. \\
-                \email{gregory.feiden@physics.uu.se}
+                \email{gregory.a.feiden@gmail.com}
              }
 
-   \date{Version: \today; Submitted: October 21, 2015; Re-submitted: April 27, 2016.}
+   \date{Submitted: 21 October 2015; Accepted: 27 June 2016.}
 
@@
 Cooler (K, M) stars typically yield ages that are systematically younger than warmer (A, F, G) stars by a factor of two.
-I explore the possibility that these age discrepancies are the result of magnetic inhibition of convection in cool young stars by using magnetic stellar evolution isochrones to determine the age of the Upper Scorpius subgroup of the Scorpius-Centaurus OB Association.
+I explore the possibility that these age discrepancies are the result of magnetic inhibition of convection in cool young stars by using magnetic stellar evolution isochrones to determine the median age of the Upper Scorpius subgroup of the Scorpius-Centaurus OB association.
 A median age of 10 Myr consistent across spectral types A through M is found, except for a subset of F-type stars that appear significantly older.
 Agreement is shown for ages derived from the Hertzsprung-Russell diagram and from the empirical mass-radius relationship defined by eclipsing multiple-star systems.
-Surface magnetic field strengths required to produce agreement are of order 2.5 kG and are predicted from \emph{a priori} estimates of equipartition values.
+Surface magnetic field strengths required to produce agreement are approximately 2.5 kG and are predicted from a priori estimates of thermal equipartition values.
 A region in the HR diagram is identified that plausibly connects stars whose structures are weakly influenced by the presence of magnetic fields with those whose structures are strongly influenced by magnetic fields.
-The models suggest this region is characterized by stars with rapidly thinning outer convective envelopes where the radiative core mass is greater than 75\% of the total stellar mass.
+The models suggest that this region is characterized by stars with rapidly thinning outer convective envelopes where the radiative core mass is greater than 75\% of the total stellar mass.
 Furthermore, depletion of lithium predicted from magnetic models appears in better agreement with observed lithium equivalent widths than predictions from non-magnetic models.
@@
 This problem is not unique to Upper Scorpius and is characteristic of broader issues endemic to age dating young stellar populations with stellar evolution isochrones \citep[e.g.,][]{Naylor2009, Bell2012, Herczeg2015}.
-HR diagram analyses by \citet{Malo2014} and \citet{Herczeg2015} show that age estimates of mid- to late-M stars in nearby young stellar moving groups are typically younger by factor of two as compared to early-M and late-K stars.
+Hertzsprung-Russell diagram analyses by \citet{Malo2014} and \citet{Herczeg2015} show that age estimates of mid- to late-M stars in nearby young stellar moving groups are typically younger by a factor of two than early-M and late-K stars.
 On the other hand, early- to late-K stars appear to have ages that are roughly consistent with each other.
@@
 Slower contraction times for low-mass stars would give them larger radii at a given age, pushing inferred ages to older values \citep[e.g.,][]{MM10, Malo2014}.
-In Sect.~\ref{sec:models}, I describe the model setup and method used to predict stellar surface magnetic field strengths \emph{a priori}.
+In Sect.~\ref{sec:models}, I describe the model setup and method used to predict stellar surface magnetic field strengths a priori.
 Section~\ref{sec:data} presents the data adopted for use in HR and mass-radius diagrams.
@@
 
-\section{Stellar Evolution Models}
+\section{Stellar evolution models}
 \label{sec:models}
@@
 Here, a different approach is used.
-Instead of adjusting models to find suitable magnetic field strengths, equipartition estimates of the maximum allowed average surface magnetic field strengths are adopted.
+Instead of adjusting models to find suitable magnetic field strengths, thermal equipartition estimates of the maximum allowed average surface magnetic field strengths are adopted.
 The aim is to test the predictive abilities of magnetic stellar evolution models.
@@
 This buffer allows models to relax to a stable configuration after the perturbation.
-Typical peak magnetic field strengths in the models are of order 50 kG for models with $\langle Bf \rangle_{\rm eq,\,surf} \sim 2.5$~kG.
+Typical peak magnetic field strengths in the models are approximately 50 kG for models with $\langle Bf \rangle_{\rm eq,\,surf} \sim 2.5$~kG.
 Conversely, magnetic field effects are turned off during a model computation once the outer convective envelope disappears.
@@
 
-Models for this study are computed using solar metallicity, [$m$/H] = 0.
+Models for this study are computed using solar metallicity, [$m$/H] = 0.0 dex.
 Values of the initial helium and heavy element mass fractions ($Y_0$ and $Z_0$, respectively) are taken from a solar-calibrated model.
@@
 
-\section{Properties of Upper Scorpius Members}
+\section{Properties of Upper Scorpius members}
 \label{sec:data}
@@
 
-\subsection{Standard Models}
+\subsection{Standard models}
 An HR diagram for Upper Scorpius is shown in Fig.~\ref{fig:ages}a.
-Empirical data is represented by the median stellar locus (light-gray shaded region) and against three standard stellar evolution isochrones with ages of 5, 10, and 15 Myr (black dashed lines).
-Focusing on temperature regimes corresponding A-, F-, and G-type stars ($5\,750 <$ \teff/K $< 10\,000$), standard stellar isochrones predict ages between 5 and 15 Myr, with a median age estimate of approximately 10 Myr.
+Empirical data are represented by the median stellar locus (light-gray shaded region), which is plotted against three standard stellar evolution isochrones with ages of 5, 10, and 15 Myr (black dashed lines).
+Focusing on temperature regimes corresponding to A-, F-, and G-type stars ($5\,750 <$ \teff/K $< 10\,000$), standard stellar isochrones predict ages between 5 and 15 Myr, with a median age estimate of approximately 10 Myr.
 
@@
 
-\subsection{Magnetic Models}
+\subsection{Magnetic models}
 Introducing a magnetic perturbation as described in Sect.~\ref{sec:models}, a 10 Myr isochrone is computed and overlaid in the HR and mass-radius diagrams in Figs.~\ref{fig:ages} and \ref{fig:mrd} (thick yellow solid line).
@@
 This age spread could be indicative of an intrinsic age spread, but it is also possible to attribute this spread to errors in the mass and radius determinations of the eclipsing binary systems or to the fact that the low-mass stars in UScoCTIO5 may require marginally stronger magnetic field strengths than are predicted from equipartition arguments.
-Nevertheless, it is encouraging that models provide this level of agreement with an age and surface magnetic field strengths determined \emph{a priori}.
+Nevertheless, it is encouraging that models provide this level of agreement with an age and surface magnetic field strengths determined a priori.
 
@@
 There are, however, still age discrepancies that must be addressed.
-As noted above, the median age {\bf inferred from models} for F-type stars appears to be a few million years older than {\bf the age inferred from models for} stars of other spectral types.
-This discrepancy is perplexing and deserves further investigation, especially considering that {\bf physics potentially missing from} the models would likely {\bf increase the inferred age for F-stars, widening the age discrepancy.} It should be noted that most F-type stars in Upper Scorpius {\bf appear to be} at a stage of evolution where models predict {\bf stellar} radii increase and subsequently decrease over a period of roughly 4 -- 8 Myr.
+As noted above, the median age inferred from models for F-type stars appears to be a few million years older than the age inferred from models for stars of other spectral types.
+This discrepancy is perplexing and deserves further investigation, especially considering that physics potentially missing from the models would likely increase the inferred age for F-stars, widening the age discrepancy.
+It should be noted that most F-type stars in Upper Scorpius appear to be at a stage of evolution where models predict stellar radii increase and subsequently decrease over a period of roughly 4 -- 8 Myr.
 The timescale for this process is similar to the observed age discrepancy (see Fig.~\ref{fig:bump} in Sect.~\ref{sec:radius}) and may be indicative of potential shortcomings in existing model physics such as radiative opacities or nuclear reaction cross-sections.
@@
 
-\subsection{Magnetic Field Evolution \& Radiative Core Growth}
+\subsection{Magnetic field evolution \& radiative core growth}
 \label{sec:dynamo}
@@
     \includegraphics[width=0.48\linewidth]{convective_env_mass_difference.eps}
-    \caption{Mass fraction of the stellar convective envelopes as a function of (a) total stellar mass and (b) effective temperature.
+    \caption{Mass fraction of the stellar convective envelope as a function of (a) total stellar mass and (b) effective temperature.
 (c) Difference in convective envelope mass between magnetic and standard stellar evolution models as a function of effective temperature.
@@
 
-While the demise of outer convection zones explains the final convergence of magnetic and standard models, it doesn't necessarily explain the beginning of the transition that occurs between $T_{\rm eff} = $ 4\,500~K and 5\,000~K.
+While the demise of outer convection zones explains the final convergence of magnetic and standard models, it does not necessarily explain the beginning of the transition that occurs between $T_{\rm eff} = $ 4\,500~K and 5\,000~K.
 In this transition region, magnetic models have masses between 1.26 $M_{\odot}$ ($T_{\rm eff} = $ 4\,500~K) and 1.40 $M_{\odot}$ ($T_{\rm eff} = $5\,000~K).
-Magnetic models predict that these stars have {\bf convective envelope} masses between 24\% and 12\% of their total stellar mass, respectively (see Figure~\ref{fig:rad_core}a).
+Magnetic models predict that these stars have convective envelope masses between 24\% and 12\% of their total stellar mass, respectively (see Figure~\ref{fig:rad_core}a).
 The 1.40 $M_{\odot}$ model is of particular note, as Figure~\ref{fig:mrd} suggests that 1.40 $M_{\odot}$ stars are entering a brief period of radius inflation that accompanies the increasing energy generation from the $p$-$p$ chain and CN-cycle burning prior to the onset of core convection \citep[e.g.,][]{Iben1965,Bodenheimer1965}.
@@
 If the transition region begins around 4\,500~K, as one might expect from the knee in the empirical HR diagram (Fig.~\ref{fig:empirical}), a rapid decrease in surface magnetic field strengths cannot fully explain the start of the transition.
-Note that Fig.~\ref{fig:rad_core}(c) suggests that the {\bf mass} difference between convective envelopes in magnetic and standard stellar models occurs around $T_{\rm eff} \sim 4\,500$~K,\footnote{The slope in the convective envelope mass difference below $3\,500$~K is due to the fact that models predict stars are fully convective below that temperature, but cooling of the stellar photosphere by magnetic inhibition of convection means magnetic models have a larger mass at a given $T_{\rm eff}$ than standard models.} suggesting there is something relatively unique occurring at that effective temperature.
+It should be noted that Fig.~\ref{fig:rad_core}(c) suggests that the mass difference between convective envelopes in magnetic and standard stellar models occurs around $T_{\rm eff} \sim 4\,500$~K,\footnote{The slope in the convective envelope mass difference below $3\,500$~K occurs because models predict that stars are fully convective below that temperature, but cooling of the stellar photosphere by magnetic inhibition of convection means magnetic models have a larger mass at a given $T_{\rm eff}$ than standard models.} suggesting there is something relatively unique occurring at that effective temperature.
 However, Fig.~\ref{fig:ages} shows no noticeable change in morphology at  $T_{\rm eff} \sim 4\,500$~K.
@@
 The sharp knee at \teff~=~4\,500~K in Fig.~\ref{fig:empirical} may be the result of a global change in magnetic field topology.
-Evidence for this comes from \citet{Gregory2012}, who noted that large-scale magnetic field topologies observed on pre-main-sequence stars appear to correlate with their predicted \emph{radiative core mass}, {\bf or alternatively, their convective envelope mass}.
+Evidence for this comes from \citet{Gregory2012}, who noted that large-scale magnetic field topologies observed on pre-main-sequence stars appear to correlate with their predicted radiative core mass, or alternatively, their convective envelope mass.
 Specifically, \citet{Gregory2012} noted a shift from predominantly dipolar axisymmetric magnetic field topologies to multi-polar non-axisymmetric field topologies when the estimated radiative core mass $M_{\rm rad.\ core} > 0.4\ M_\star$.
@@
 
-The observed knee and shallower slope in Fig.~\ref{fig:empirical} appear to be {\bf genuine} features.
+The observed knee and shallower slope in Fig.~\ref{fig:empirical} appear to be genuine features.
 General agreement between the behavior of the magnetic model isochrone and the observed stellar locus provides evidence that magnetic inhibition of convection is the mechanism that is producing these effects.
@@
 
-\subsection{Initial Mass Function}
+\subsection{Initial mass function}
 The presence of magnetic and non-magnetic sequences has implications for the (sub)stellar initial mass function of Upper Scorpius \citep{Ardila2000, Preibisch2002}.
@@
 Neglecting magnetic inhibition of convection would produce stellar mass distributions that show a paucity of stars at higher masses compared to standard predictions for field and cluster initial mass function \citep[e.g.,][]{Salpeter1955, Kroupa2002, Chabrier2003}.
-\citet{Preibisch2002} note a possible excess of low-mass stars compared to field initial mass functions \citep{Scalo1998, Kroupa2002}, but it's not immediately clear whether this potential excess of low-mass stars is fully consistent with predictions from magnetic model predictions.
+\citet{Preibisch2002} note a possible excess of low-mass stars compared to field initial mass functions \citep{Scalo1998, Kroupa2002}, but it is not immediately clear whether this potential excess of low-mass stars is fully consistent with predictions from magnetic model predictions.
 Assessing the impact of magnetic inhibition of convection on the (sub)stellar initial mass function of Upper Scorpius is reserved for future work.
@@
 As described in Sect.\ \ref{sec:dynamo}, this radius increase is due to the convective envelope responding to increased energy generation from CN cycle ignition.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.85\linewidth]{radius_bump.eps}
+    \caption{Brief period of radius inflation described in Sect.~\ref{sec:radius} for stars with masses of 1.60\msun\ (blue solid), 1.55\msun\ (green short-dashed), 1.50\msun\ (blue dash-dotted), 1.45\msun\ (yellow long-dashed).
+Mass tracks are computed without a magnetic field (i.e., non-magnetic configuration).
+Effective temperatures at these masses are characteristic of F stars at 10 Myr.}
+    \label{fig:bump}
+\end{figure}
 
@@
 However, the exact role that magnetic fields may play in governing the pre-main-sequence contraction of young A-, F-, and G-type stars remains relatively unexplored.
-While magnetic fields are included in models of these stars, the equipartition magnetic field strength is fixed to the predicted value at 10 Myr.
+While magnetic fields are included in models of these stars, the thermal equipartition magnetic field strength is fixed to the predicted value at 10 Myr.
 Stronger surface magnetic fields may exist at younger ages, which might delay contraction and lead to larger radii at a given age.
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.85\linewidth]{radius_bump.eps}
-    \caption{Brief period of radius inflation described in Sect.~\ref{sec:radius} for stars with masses of 1.60\msun\ (blue solid), 1.55\msun\ (green short-dashed), 1.50\msun\ (blue dash-dotted), 1.45\msun\ (yellow long-dashed).
-Mass tracks are computed without a magnetic field (i.e., non-magnetic configuration).
-Effective temperatures at these masses are characteristic of F stars at 10 Myr.}
-    \label{fig:bump}
-\end{figure}
-
-\subsection{On Starspots}
+\subsection{On starspots}
 Starspots have been suggested as an alternative mechanism to slow the contraction of young low-mass stars \citep{Jackson2009, MM10, Jackson2014a, Somers2015b}.
@@
 
-Agreement between ages and stellar fundamental properties of low-mass stars predicted by magnetic stellar evolution isochrones presented in this work with ages of higher mass stars in Upper Scorpius may indicate that a global inhibition of convection accurately captures relevant physics involved in halting contraction of low-mass stars.
+Agreement between ages and stellar fundamental properties of low-mass stars predicted by magnetic stellar evolution isochrones presented in this work with ages of higher mass stars in Upper Scorpius may indicate that a global inhibition of convection accurately captures relevant physics involved in halting the contraction of low-mass stars.
 If starspots are also to be considered, one might expect to find that young stars in Upper Scorpius have a high coverage fraction of spots ($f \sim 1$).
@@
 
-\subsection{Lithium Depletion}
+\subsection{Lithium depletion}
+
+\begin{figure}[t]
+    \includegraphics[width=0.85\linewidth]{Li7_USco_Beq.eps}
+    \caption{Lithium abundance  as a function of effective temperature at 5 and 10 Myr.
+Predictions are shown from standard (black dashed lines) and magnetic (yellow solid line) stellar evolution isochrones.
+Models were computed using the setup described in Sect.~\ref{sec:models}.
+Lithium abundance is defined as $A(\,^7{\rm Li}) = \log_{10}(N_{\rm Li}/N_{\rm H}) + 12$.}
+    \label{fig:lithium}
+\end{figure}
+
 An approach to validating magnetic stellar models is the determination of lithium abundances \citep{MacDonald2015}, or observation of lithium equivalent widths.
@@
 The lithium depletion boundary at cooler temperatures remains largely unchanged.
-However, lithium depletion is not expected to occur in warmer stars with effective temperatures exceeding about 4500~K, assuming they possess a strong magnetic field.
+However, lithium depletion is not expected to occur in warmer stars with effective temperatures exceeding about 4\,500~K, assuming they possess a strong magnetic field.
 Therefore, K-stars are not expected to exhibit signatures of lithium depletion, in contrast to standard model predictions, which suggest stars with spectral types later than G are expected to show signatures of lithium depletion.
 
-Stars with effective temperatures around 3550~K are predicted to exhibit the greatest amount of lithium depletion, as compared to a prediction of 3750~K for standard models.
-Some depletion is also expected to occur for stars with $3300 <$ \teff/K $< 3500$, which standard models suggest should not be observed.
+Stars with effective temperatures around 3\,550~K are predicted to exhibit the greatest amount of lithium depletion, as compared to a prediction of 3750~K for standard models.
+Some depletion is also expected to occur for stars with $3\,300 <$ \teff/K $< 3\,500$, which standard models suggest should not be observed.
 This prediction shows a strong similarity to trends in lithium equivalent widths for M-stars in Upper Scorpius \citep{Rizzuto2015}.
-The observed lithium equivalent width minimum is located between \teff\ = 3300 -- 3400~K \citep{Rizzuto2015}.
+The observed lithium equivalent width minimum is located between \teff\ = 3\,300 -- 3\,400~K \citep{Rizzuto2015}.
 While comparing lithium equivalent widths and predictions of lithium abundances is not completely correct, within the narrow range of temperatures surrounding the lithium abundance minimum, equivalent widths should accurately reflect trends in overall lithium abundances.
@@
 
-\begin{figure}[t]
-    \includegraphics[width=0.85\linewidth]{Li7_USco_Beq.eps}
-    \caption{Lithium abundance  as a function of effective temperature at 10 Myr.
-Predictions are shown from standard (light-blue dashed line) and magnetic (yellow solid line) stellar evolution isochrones.
-Models were computed using the setup described in Sect.~\ref{sec:models}.
-Lithium abundance is defined as $A(\,^7{\rm Li}) = \log_{10}(N_{\rm Li}/N_{\rm H}) + 12$.}
-    \label{fig:lithium}
-\end{figure}
-
-\section{Summary \& Conclusions}
+\section{Summary \& conclusions}
 \label{sec:tellit}
@@
 Using stellar evolution models that account for magnetic inhibition of convection \citep{FC12b, FC13}, an age of 9 -- 10 Myr is found for K- and M-type stars in Upper Scorpius.
-Magnetic inhibition of convection consistently explains:
+Magnetic inhibition of convection consistently explains
 \begin{enumerate} 
-	\item the age discrepancy between high- and low-mass stars in the HR diagram \citep{Herczeg2015},
-	\item the observed slope of the low-mass stellar mass-radius relationship,
-	\item stellar age differences observed between HR diagram and mass-radius relationship determinations \citep{Kraus2015},
+	\item the age discrepancy between high- and low-mass stars in the HR diagram \citep{Herczeg2015};
+	\item the observed slope of the low-mass stellar mass-radius relationship;
+	\item stellar age differences observed between HR diagram and mass-radius relationship determinations \citep{Kraus2015};
 	\item and the lithium depletion pattern inferred from observed lithium equivalent widths \citep{Rizzuto2015}.
 \end{enumerate}
-Critically, average surface magnetic field strengths are determined \emph{a priori} via equipartition arguments, highlighting the potential predictive power of magnetic stellar models for young stars.
+Critically, average surface magnetic field strengths are determined a priori via equipartition arguments, highlighting the potential predictive power of magnetic stellar models for young stars.
 
@@
 There is no population of stars in the Upper Scorpius that unambiguously supports an age of 5 Myr.
-Nevertheless, additional eclipsing binary systems are needed to better populate the mass-radius relationship to solidify Upper Scorpius as a 10 Myr old stellar association and to verify predictions from magnetic stellar evolution models across the full mass spectrum.
+Nevertheless, additional eclipsing binary systems are needed to better populate the mass-radius relationship to solidly identify Upper Scorpius as a 10 Myr old stellar association and to verify predictions from magnetic stellar evolution models across the full mass spectrum.
 
@@
 G.A.F.
-thanks Alexis Lavail, Eric Mamajek, James Silvester, and Eric Stempels for reading and commenting on an early version of this manuscript as well as Bengt Gustafsson and Thomas Nordlander for interesting discussions that helped improved the manuscript.
-G.A.F also thanks the anonymous reviewer posing interesting questions that led to significant improvements in the manuscript.
+thanks Alexis Lavail, Eric Mamajek, James Silvester, and Eric Stempels for reading and commenting on an early version of this manuscript and also Bengt Gustafsson and Thomas Nordlander for interesting discussions that helped improved the manuscript.
+G.A.F also thanks the anonymous reviewer who posed interesting questions that led to significant improvements in the manuscript.
 The magnetic Dartmouth stellar evolution code was originally developed with support of National Science Foundation (NSF) grant AST-0908345.

### 2016-07-13 paper/ms.tex
integrated new commands from defs

@@
 
-\usepackage{defs}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newcommand{\msun}{$M_{\odot}$}
+\newcommand{\rsun}{$R_{\odot}$}
+\newcommand{\lsun}{$L_{\odot}$}
+\newcommand{\logLsun}{\log(L/L_{\odot})}
+\newcommand{\amlt}{\alpha_{\rm MLT}}
+\newcommand{\teff}{$T_{\rm eff}$}
+\newcommand{\tauf}{\tau_{\rm fit}}
+\newcommand{\lbol}{$L_{\rm bol}$}
+\newcommand{\fbol}{$F_{\rm bol}$}
+\newcommand{\logg}{$\log g$}
+\newcommand{\vsini}{$v \sin i$}
+\newcommand{\ha}{H$\alpha$}
+\newcommand{\lha}{$L_{\rm H\alpha}$}
+\newcommand{\water}{H$_2$O}
+\newcommand{\pgas}{P_{\rm gas}}
+\newcommand{\porb}{$P_{\rm orb}$}
 
@@
 The empirical mass-radius relationship is more reliable than the HR diagram, as masses and radii can be measured directly \citep[e.g.,][]{Andersen1991,Torres2010}.
-Compare this to conversions from spectral types and photometric colors to \teff s and luminosities, which are subject to significant uncertainties, especially for stars with gravities intermediate between dwarf and giant scales \citep[see, e.g.,][]{Pecaut2013}.
+Compare this to conversions from spectral types and photometric colors to $T_{\rm eff}$s and luminosities, which are subject to significant uncertainties, especially for stars with gravities intermediate between dwarf and giant scales \citep[see, e.g.,][]{Pecaut2013}.
 Empirical mass-radius relationships should therefore provide stringent tests of stellar model accuracy.
